---
title: "Compare VAST and survey planktivores"
author: "Sarah Gaichas"
date: "2022-12-07"
output:
  html_document:
    code_fold: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      results='hide')

library(dplyr)
library(ggplot2)
library(stringr)
```


Compare SOE aggregate survey bio indices to VAST forage index. Caveats: may not contain same species, wont be on same scale

## Compare indices scaled to mean for each EPU

Use Kim B's code to extract planktivores from `ecodata::aggregate_biomass`, modify code to calculate time series sd, rescale

```{r SOEplanktivores}
planktivores <- ecodata::aggregate_biomass %>%
  dplyr::filter(Var %in% c("Planktivore Fall Biomass Index",
                           "Planktivore Spring Biomass Index",
                           "Planktivore Fall Biomass Standard Error",
                           "Planktivore Spring Biomass Standard Error"))%>%
  tidyr::separate(Var, c("feeding.guild", "season", "Biomass", "Var1", "Null", "Area"), sep = " ") %>%
  tidyr::unite("Var", feeding.guild:season, sep = " ") %>%
  dplyr::mutate(stat = recode(Var1, Index = "Mean",
                      Standard = "SD")) %>%
  dplyr::select(-Biomass, -Var1, -Null, -Units) %>%
  # dplyr::filter(!Area == "-") %>%
  dplyr::group_by(Var, Time, EPU, Area) %>%
  tidyr::pivot_wider(id_cols = c(Var, Time, EPU, Area),names_from =  stat, values_from =  Value) %>%
  dplyr::filter(!Mean == "NULL") %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Mean = as.numeric(Mean))


agg_bio<-planktivores %>% dplyr::filter(EPU %in% c("MAB", "GB", "GOM"),
         Time >= 1968) %>%
  dplyr::group_by(Var, EPU) %>%
  dplyr::mutate(hline = mean(Mean, na.rm = T), 
                tssd = sd(SD, na.rm = T),
                 upper = Mean + (2*SD),
                lower = Mean - (2*SD)) %>%
  dplyr::ungroup()  

agg_bio_std <- agg_bio %>%
  dplyr::mutate(stdPlank = (Mean-hline)/tssd,
                #cv = SD/Mean,
                stdPlankupper = (upper-hline)/tssd,
                stdPlanklower = (lower-hline)/tssd)

agg_bio_std$Var <- factor(agg_bio_std$Var,levels = c("Planktivore Spring",
                                                    "Planktivore Fall"))
series.col <- rep("black",length(unique(agg_bio_std$Var)))
facet_names <- list("Planktivores" = expression("Planktivores")
                    )

```

### Test plotting

Original SOE plot scale

```{r SOEplot}
#Time series constants
shade.alpha <- 0.3
shade.fill <- "lightgrey"
lwd <- 1
pcex <- 2
trend.alpha <- 0.5
trend.size <- 2
hline.size <- 1
hline.alpha <- 0.35
hline.lty <- "dashed"
label.size <- 5
hjust.label <- 1.5
letter_size <- 4
feeding.guilds <- c("Apex Predator","Piscivore","Planktivore","Benthivore","Benthos")
x.shade.min <- 2011
x.shade.max <- 2021
series.col <- c("indianred","black")
#Function for custom ggplot facet labels
label <- function(variable,value){
  return(facet_names[value])
}

p3<-agg_bio_std %>%
  dplyr::filter(str_detect(Var,"Planktivore")) %>%
  ggplot2::ggplot() +

  #Highlight last ten years
  #ggplot2::annotate("rect", fill = shade.fill, alpha = shade.alpha,
  #    xmin = x.shade.min , xmax = x.shade.max ,
  #    ymin = -Inf, ymax = Inf) +
  #Test for trend and add lines
  ecodata::geom_gls(aes(x = Time, y = Mean,
               color = Var),
             alpha = trend.alpha, size = trend.size) +
  ecodata::geom_lm(aes(x = Time, y = Mean,
               color = Var),
             alpha = trend.alpha, size = trend.size) +
  # #ecodata::geom_lm(aes(x = Time, y = Mean))+

  #Add time series
  ggplot2::geom_ribbon(aes(x = Time, ymin = pmax(lower,0), ymax = upper),
              alpha = 0.5,
              fill = "grey") +
  ggplot2::geom_line(aes(x = Time, y = Mean),size = lwd-0.5) +
  ggplot2::geom_point(aes(x = Time, y = Mean),size = pcex-0.5) +
  ggplot2::scale_color_manual(values = series.col, aesthetics = "color")+
  ggplot2::guides(color = FALSE) +
  ggplot2::geom_hline(aes(yintercept = hline,
                 group = Var),
             size = hline.size,
             alpha = hline.alpha,
             linetype = hline.lty)+
  ggplot2::facet_wrap(EPU ~ Var~.,ncol = 2, scales = "free_y") +
       #Add NEAMAP
  # ggplot2::geom_ribbon(data = neamap.3, aes(ymax = pmax(upper, 0), ymin = lower, x = Time),
  #               fill = "pink", alpha = 0.5) +
  # ggplot2::geom_line(data = neamap.3, aes(x = Time, y = Value),
  #           color = "#ca0020")+
  # ggplot2::geom_point(data = neamap.3, aes(x = Time, y = Value),
  #            size = pcex-0.5,
  #            color = "#ca0020")+

  #Axis and theme
  ggplot2::scale_x_continuous(breaks = seq(1970, 2020, by = 10), expand = c(0.01, 0.01)) +
  #ylim(0, 600)+
  ggplot2::ylab(expression("Biomass (kg tow"^-1*")")) +
  ecodata::theme_facet()+
  ggplot2::theme(strip.text=element_text(hjust=0),
        axis.title.x=element_blank())

p3


```

Rescaled SOE plots

```{r rescaleSOEplot}


p4<-agg_bio_std %>%
  dplyr::filter(str_detect(Var,"Planktivore")) %>%
  ggplot2::ggplot() +

  #Highlight last ten years
  #ggplot2::annotate("rect", fill = shade.fill, alpha = shade.alpha,
  #    xmin = x.shade.min , xmax = x.shade.max ,
  #    ymin = -Inf, ymax = Inf) +
  #Test for trend and add lines
  ecodata::geom_gls(aes(x = Time, y = stdPlank,
               color = Var),
             alpha = trend.alpha, size = trend.size) +
  ecodata::geom_lm(aes(x = Time, y = stdPlank,
               color = Var),
             alpha = trend.alpha, size = trend.size) +
  # #ecodata::geom_lm(aes(x = Time, y = Mean))+

  #Add time series
  ggplot2::geom_ribbon(aes(x = Time, ymin = pmax(stdPlanklower), ymax = stdPlankupper),
              alpha = 0.5,
              fill = "grey") +
  ggplot2::geom_line(aes(x = Time, y = stdPlank),size = lwd-0.5) +
  ggplot2::geom_point(aes(x = Time, y = stdPlank),size = pcex-0.5) +
  ggplot2::scale_color_manual(values = series.col, aesthetics = "color")+
  ggplot2::guides(color = FALSE) +
  ggplot2::geom_hline(aes(yintercept = 0,
                 group = Var),
             size = hline.size,
             alpha = hline.alpha,
             linetype = hline.lty)+
  ggplot2::facet_wrap(EPU ~ Var~.,ncol = 2, scales = "free_y") +
       #Add NEAMAP
  # ggplot2::geom_ribbon(data = neamap.3, aes(ymax = pmax(upper, 0), ymin = lower, x = Time),
  #               fill = "pink", alpha = 0.5) +
  # ggplot2::geom_line(data = neamap.3, aes(x = Time, y = Value),
  #           color = "#ca0020")+
  # ggplot2::geom_point(data = neamap.3, aes(x = Time, y = Value),
  #            size = pcex-0.5,
  #            color = "#ca0020")+

  #Axis and theme
  ggplot2::scale_x_continuous(breaks = seq(1970, 2020, by = 10), expand = c(0.01, 0.01)) +
  #ylim(0, 600)+
  ggplot2::ylab(expression("Standardized Biomass Index")) +
  ecodata::theme_facet()+
  ggplot2::theme(strip.text=element_text(hjust=0),
        axis.title.x=element_blank())

p4


```

Rescale forage indices and add to rescaled SOE plot

```{r VASTrescaleSOE}

forage <- ecodata::forage_index %>%
  dplyr::filter(Var %in% c(#"Annual Forage Fish Biomass Estimate",
                           #"Annual Forage Fish Biomass Estimate SE",
                           "Fall Forage Fish Biomass Estimate",
                           "Fall Forage Fish Biomass Estimate SE",
                           "Spring Forage Fish Biomass Estimate",
                           "Spring Forage Fish Biomass Estimate SE"),
                EPU %in% c("GOM", "GB", "MAB"))%>%
  tidyr::separate(Var, c("season", "feeding.guild", NA,"Biomass", NA, "Var1"), sep = " ", extra = "drop", fill = "right") %>% 
  tidyr::unite("Var", feeding.guild:season, sep = " ") %>%
  dplyr::mutate(stat = recode(Var1, .missing = "Mean",
                      SE = "SD")) %>%
  dplyr::select(-Biomass, -Var1, -Units) %>%
  # dplyr::filter(!Area == "-") %>%
  dplyr::group_by(Var, Time, EPU) %>%
  tidyr::pivot_wider(id_cols = c(Var, Time, EPU),names_from =  stat, values_from =  Value) %>%
  dplyr::filter(!Mean == "NULL") %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Mean = as.numeric(Mean))

forage_std <- forage %>%
  dplyr::group_by(Var, EPU) %>%
  dplyr::mutate(hline = mean(Mean, na.rm = T), 
                tssd = sd(SD, na.rm = T),
                 upper = Mean + (2*SD),
                lower = Mean - (2*SD)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(stdForage = (Mean-hline)/tssd,
                #cv = SD/Mean,
                stdForageupper = (upper-hline)/tssd,
                stdForagelower = (lower-hline)/tssd)

forage_std$Var <- factor(forage_std$Var,levels = c("Forage Spring",
                                                    "Forage Fall"))
series.col <- rep("black",length(unique(forage_std$Var)))
facet_names <- list("Forage" = expression("Forage")
                    )

```

Plot just forage indices

```{r plotVASTrescaled}

p5<-forage_std %>%
  #dplyr::filter(str_detect(Var,"Forage")) %>%
  ggplot2::ggplot() +

  #Highlight last ten years
  #ggplot2::annotate("rect", fill = shade.fill, alpha = shade.alpha,
  #    xmin = x.shade.min , xmax = x.shade.max ,
  #    ymin = -Inf, ymax = Inf) +
  #Test for trend and add lines
  ecodata::geom_gls(aes(x = Time, y = stdForage,
               color = Var),
             alpha = trend.alpha, size = trend.size) +
  ecodata::geom_lm(aes(x = Time, y = stdForage,
               color = Var),
             alpha = trend.alpha, size = trend.size) +
  # #ecodata::geom_lm(aes(x = Time, y = Mean))+

  #Add time series
  ggplot2::geom_ribbon(aes(x = Time, ymin = pmax(stdForagelower), ymax = stdForageupper),
              alpha = 0.5,
              fill = "grey") +
  ggplot2::geom_line(aes(x = Time, y = stdForage),size = lwd-0.5) +
  ggplot2::geom_point(aes(x = Time, y = stdForage),size = pcex-0.5) +
  ggplot2::scale_color_manual(values = series.col, aesthetics = "color")+
  ggplot2::guides(color = FALSE) +
  ggplot2::geom_hline(aes(yintercept = 0,
                 group = Var),
             size = hline.size,
             alpha = hline.alpha,
             linetype = hline.lty)+
  ggplot2::facet_wrap(EPU ~ Var~.,ncol = 2, scales = "free_y") +
       #Add NEAMAP
  # ggplot2::geom_ribbon(data = neamap.3, aes(ymax = pmax(upper, 0), ymin = lower, x = Time),
  #               fill = "pink", alpha = 0.5) +
  # ggplot2::geom_line(data = neamap.3, aes(x = Time, y = Value),
  #           color = "#ca0020")+
  # ggplot2::geom_point(data = neamap.3, aes(x = Time, y = Value),
  #            size = pcex-0.5,
  #            color = "#ca0020")+

  #Axis and theme
  ggplot2::scale_x_continuous(breaks = seq(1970, 2020, by = 10), expand = c(0.01, 0.01)) +
  #ylim(0, 600)+
  ggplot2::ylab(expression("Standardized Biomass Index")) +
  ecodata::theme_facet()+
  ggplot2::theme(strip.text=element_text(hjust=0),
        axis.title.x=element_blank())

p5


```

Same plot standardized SOE planktivores and Forage index

```{r compare}



```

## Compare species lists