---
title: "Bluefish Forage Index: Methods and Progress"
author: "Sarah Gaichas, James Gartland, Elizabeth Ng, and Bluefish WG"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_fold: hide
link-citations: yes
csl: ices-journal-of-marine-science.csl
bibliography: FishDiet_EcoIndicators.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

library(here)
library(sf)
library(rnaturalearth)
library(raster)
library(smoothr)
library(gridExtra)
library(tidyverse)

library(DT)
#library(pdftools)
library(patchwork)
library(ggiraph)

library(ecodata)
#library(VAST)

```

# Does prey drive availability of bluefish?

Objective: create a "prey index" to evaluate changes in bluefish prey over time and in space using VAST [@thorson_comparing_2017; @thorson_guidance_2019].

Pattern on [@ng_predator_2021], which used predator stomach data to create a biomass index for a single prey, herring. Expected biomass of herring per stomach was estimated with 2 linear predictors, n herring per stomach and avg wt of herring in a stomach. 

We adapt this to get an index for "bluefish prey" rather than a single prey species. Further, we include inshore and offshore regions by combining surveys as was done for summer flounder biomass in [@perretti_spatio-temporal_2019]. Finally, since bluefish themselves are somewhat sparsely sampled by the surveys, we aggregate all predators that have a similar diet composition to bluefish to better represent bluefish prey biomass. 

We characterize weight of bluefish prey from all piscivores caught at each location and model that over time/space. Covariates explaining patterns in bluefish prey index include number of predators and size composition of predators at each location. 

# What do bluefish eat?

Bluefish eat small pelagics that are not well sampled by bottom trawl surveys. Bluefish themselves are not well sampled by bottom trawl surveys. Nevertheless, the diet samples collected for bluefish indicate that anchovies, herrings, squids, butterfish, scup, and small hakes are important prey. 

See [here](https://sgaichas.github.io/bluefishdiet/DietSummary.html) for NEFSC survey and [here](https://docs.google.com/presentation/d/1VlP0OsSLnoaoFHHt7kJbrqNTgBJqI6Ru/edit#slide=id.p1) for NEAMAP survey bluefish diet composition summaries.

We first characterize annual food habits data from NEFSC.

```{r}
# object is called `allfh`
load(url("https://github.com/Laurels1/Condition/raw/master/data/allfh.RData"))
```


This is the `get_diet()` function from [ECSA](https://github.com/NOAA-EDAB/ECSA/blob/master/R/get_diet.R), modified to use all available strata:

```{r, get_diet}
#' Get diet composition data for plotting
#'
#' Creates a dataset for plotting annual or seasonal weighted diet composition with sample sizes.
#' Datasets are for a selected species and set of seasonal survey strata.
#' Currently only works for summer flounder with strata pre-selected.
#' Need to clearly define what each data column is, render to tidy data.
#' This is a first draft that will be revised with dplyr functions later.
#' n.b., Original file from Brian Smith, August 23 2018 was allwt_nstoms.R, renamed as get_diet.R
#'
#'
#' @param species_code numeric. Three digit svspp code
#'
#' @return dataframe with variables svspp, year, season, meansw, num_tows, variance, cv, prey, totwt, relmsw, ci, relci, nstom
#'
#' @examples
#' head(get_diet(103))
#'

get_diet <- function(species_code){
  
  #### This part here should be replaced with a file for all NEUS stocks
  # sss <- read.csv("data/seasonal_stock_strata.csv",
  #                 stringsAsFactors = FALSE)
  # 
  # sixcode <- c('acared','alewif','amepla','atlcod','atlhal','atlher','atlmac','atlwol',
  #              'barska','blabas','bluefi','bluher','butter','cleska','haddoc',
  #              'litska','monkfh','ocpout','offhak','polloc','redhak','rosska',
  #              'scupzz','silhak','smodog','smoska','spidog','sumflo','thoska',
  #              'whihak','window','winflo','winska','witflo','yelflo','amlobs','joncra')
  # 
  # svspp_list <- c(155,33,102,73,101,32,121,192,22,141,
  #                 135,34,131,24,74,26,197,193,69,
  #                 75,77,25,143,72,13,27,15,103,
  #                 28,76,108,106,23,107,105,301,312)
  # 
  # 
  # #Get data, manipulate, set constants
  # svspp_df <- data.frame(sp = sixcode,
  #                        svspp = svspp_list, 
  #                        stringsAsFactors = FALSE)
  # 
  # seasonal_strata <- sss %>% 
  #   mutate(season = toupper(season)) %>% 
  #   left_join(svspp_df, by = "sp") %>% 
  #   rename(stratum = strata) %>% 
  #   filter(svspp %in% species_code)


  # seasonal_strata <- read.csv("data/stock_list.csv", stringsAsFactors = FALSE) %>% 
  #   dplyr::select(season,
  #                 sp = species_code,
  #                 stock_area = stock,
  #                 stratum = strat,
  #                 svspp) %>% 
  #   dplyr::filter(svspp == species_code,
  #                 season %in% c("fall", "spring")) %>% 
  #   dplyr::mutate(season = toupper(season))
  
  
  ## Need to figure out how to access via ERDDAP
  #load("data/allfhsg.RData")
  
  #load(here("fhdat", "allfhsg_2016.RData"))
  
  # spring_strata <- seasonal_strata$stratum[seasonal_strata$season == 'SPRING']
  # summer_strata <- seasonal_strata$stratum[seasonal_strata$season == 'SUMMER']
  # fall_strata <-   seasonal_strata$stratum[seasonal_strata$season == 'FALL']
  # winter_strata <- seasonal_strata$stratum[seasonal_strata$season == 'WINTER']
  
  ## Filter out only good stomachs for strata and species
  allsum_raw <- allfh %>%
    filter(pynam != 'BLOWN', 
           pynam != 'PRESERVED',
           pynam != ' ',
           purcode == 10, 
           svspp %in% species_code)#,
           # (season == "SPRING" & stratum %in% spring_strata) |
           #   (season == "SUMMER" & stratum %in% summer_strata) |
           #   (season == "FALL"   & stratum %in% fall_strata)   |
           #   (season == "WINTER" & stratum %in% winter_strata))
  
  ## Number of stomachs by length and weight
  
  ## Sum by length
  allsum_len <- allsum_raw %>%
    group_by(year,
             season,
             svspp,
             cruise,
             station,
             pdid,
             pdsex,
             pdlen) %>%
    summarise(totwt = sum(pyamtw)) %>%
    na.omit() %>%
    group_by(year,
             season,
             svspp) %>%
    summarise(nstom    = n(),
              meanstom = mean(totwt, na.rm = TRUE),
              varstom  = var(totwt, na.rm = TRUE),
              meanlen  = mean(pdlen, na.rm = TRUE),
              numlen   = n(),
              minstom  = min(totwt, na.rm = TRUE),
              maxstom  = max(totwt, na.rm = TRUE),
              minlen   = min(pdlen, na.rm = TRUE),
              maxlen   = max(pdlen, na.rm = TRUE))
  
  ## Sum by weight
  allsum_wgt <- allsum_raw %>%
    group_by(year,
             season,
             svspp,
             cruise,
             station,
             pdid,
             pdsex,
             pdwgt,
             pdlen) %>%
    summarise(totwt = sum(pyamtw, na.rm = TRUE)) %>%
    na.omit() %>%
    group_by(year,
             season,
             svspp) %>%
    summarise(meanwgt = mean(pdwgt, na.rm = TRUE),
              numwgt  = n(),
              minwgt  = min(pdwgt, na.rm = TRUE),
              maxwgt  = max(pdwgt, na.rm = TRUE))
  
  #stomstats2
  nstom_df <- allsum_len %>%
    left_join(allsum_wgt, by = c("year", "season", "svspp")) %>%
    # mutate(std.error = sqrt(varstom/nstom)) %>% 
    select(svspp, year, season, nstom)
  
  #----------------------------------Start weighted diet proportion code-------------------------------------#
  
  ## Select and rename the appropriate columns
  allsum_strat <- allsum_raw %>%
    select(cruise6, stratum, station, 
           year,
           season,
           svspp, pdid, 
           pdsex, pdlen, 
           tax = collsci, 
           pyamt = pyamtw, 
           catnum, numlen, 
           tot_catnum_stratum, tot_catwgt_stratum, tot_tows_spp_stratum, 
           stratum_area)
  
  ## Group into seasonal length-class and remove NAs
  num_strat <- allsum_strat %>%
    group_by(cruise6,
             station,
             year,
             season,
             svspp,
             pdid,
             pdsex,
             pdlen) %>%
    summarise(xxxx = n()) %>%
    group_by(cruise6,
             station, 
             year,
             season, 
             svspp, 
             pdsex, 
             pdlen) %>%
    summarise(numlen2 = n()) %>%
    left_join(allsum_strat,  by = c("cruise6", "station", "year",
                                    "season", "svspp", "pdsex", "pdlen")) %>% 
    mutate(numlen_fin = case_when(numlen < numlen2 ~ numlen2,
                                  numlen >= numlen2 ~ numlen,
                                  TRUE ~ NA_integer_)) %>%
    select(c(cruise6, stratum, station,
             year,
             season, 
             svspp, pdid, pdsex, pdlen, tax, pyamt, 
             catnum, tot_catnum_stratum, tot_catwgt_stratum,
             tot_tows_spp_stratum, stratum_area, numlen, numlen_fin))
  
  
  sum_strat <- num_strat %>%
    group_by(cruise6,
             station, 
             year, 
             season,
             svspp, 
             pdsex,
             pdlen, 
             numlen_fin) %>%
    summarise(dummy_var = sum(numlen, na.rm = TRUE)) %>% 
    na.omit() %>%
    group_by(cruise6,
             station, 
             year, 
             season, 
             svspp, 
             pdlen) %>%
    summarise(rnumlen_fin = sum(numlen_fin, na.rm = TRUE)) %>%
    left_join(num_strat, by = c("cruise6", "station", "year", "season", "svspp", "pdlen")) %>% 
    mutate(rnumlen_fin = ifelse(svspp !=13 | svspp !=15, 
                                numlen_fin, 
                                rnumlen_fin)) %>%
    group_by(cruise6, 
             station,
             year,
             season,
             svspp, 
             pdsex, 
             catnum) %>%
    summarise(dummy_var = sum(numlen)) %>% 
    na.omit()
  
  
  sum_catnum <- sum_strat %>%
    group_by(cruise6,
             station, 
             year,
             season,
             svspp) %>%
    summarise(rcatnum = sum(catnum, na.rm = TRUE)) %>%
    na.omit() %>%
    left_join(num_strat,  by = c("cruise6", "station", "year", "season", "svspp")) %>% 
    mutate(rcatnum = ifelse(svspp != 13 | svspp != 15, 
                            catnum, 
                            rcatnum))
  
  sum_catstratum <- sum_catnum %>%
    group_by(cruise6, stratum, 
             year,
             season, 
             svspp, 
             pdsex, 
             tot_tows_spp_stratum,
             tot_catnum_stratum,
             tot_catwgt_stratum) %>%
    summarise(dum_var = sum(rcatnum, na.rm = TRUE)) %>%
    na.omit()
  
  ####################################################################################################################################
  
  max_tot_tows_spp_stratum <- sum_catstratum %>%
    group_by(cruise6, 
             stratum, 
             year,
             season,
             svspp) %>% 
    summarise(tot_tows_spp_stratum = max(tot_tows_spp_stratum, na.rm = TRUE))
  
  sum_rcatstratum <- sum_catstratum %>%
    group_by(cruise6, 
             stratum, 
             year,
             season,
             svspp) %>%
    summarise(rtot_catnum_stratum = sum(tot_catnum_stratum, na.rm = TRUE),
              rtot_catwgt_stratum = sum(tot_catwgt_stratum, na.rm = TRUE)) %>% 
    na.omit() %>%
    left_join(max_tot_tows_spp_stratum, by = c("cruise6", "stratum", "year", "season", "svspp")) %>%
    rename(rtot_tows_spp_stratum = tot_tows_spp_stratum)
  
  final_strat <- sum_rcatstratum %>%
    left_join(sum_catnum, by = c("cruise6", "stratum", "year", "season", "svspp")) %>% 
    mutate(rtot_catnum_stratum = ifelse(svspp != 13 | svspp != 15, 
                                        tot_catnum_stratum, 
                                        rtot_catnum_stratum),
           rtot_catwgt_stratum = ifelse(svspp != 13 | svspp != 15, 
                                        tot_catwgt_stratum, 
                                        rtot_catwgt_stratum),
           rtot_tows_spp_stratum = ifelse(svspp != 13 | svspp != 15, 
                                          tot_tows_spp_stratum,
                                          rtot_tows_spp_stratum))
  
  ####################################################################################################################################
  py_raw <- final_strat %>%
    group_by(cruise6, 
             station, 
             year,
             season, 
             svspp, pdid, pdlen, tax) %>%
    summarise(pysum = sum(pyamt, na.rm = TRUE)) %>% 
    na.omit() 
  
  py_nostom <- py_raw %>%
    ungroup() %>% 
    arrange(cruise6, station,
            year,
            season,
            svspp,
            pdid) %>%
    group_by(cruise6,
             station, 
             year,
             season, 
             svspp, 
             pdid) %>% 
    top_n(-1, wt = pysum) %>%
    group_by(cruise6, 
             station, 
             year, 
             season, 
             svspp) %>%
    summarise(nostom = n())
  
  py_list <- data.frame(tax = unique(py_raw$tax),
                        pycode = paste0('prey', 1:length(unique(py_raw$tax))))
  
  
  py_all <- py_nostom %>%
    left_join(py_raw, by = c("cruise6", "station", "year", "season", "svspp")) %>% 
    left_join(py_list, by = "tax")
  
  
  pd_strat <- final_strat %>%
    group_by(cruise6, 
             station, 
             year,
             season,
             svspp, 
             pdid, 
             pdlen) %>% 
    top_n(-1, wt = stratum_area) 
  
  
  pd_nas <- pd_strat %>%
    group_by(cruise6, 
             station, 
             year,
             season,
             svspp, 
             pdlen) %>%
    summarise(rnumlen_fin = sum(numlen_fin, na.rm = TRUE)) %>%
    na.omit()
  
  pd_strat <- pd_strat %>%
    left_join(pd_nas, by = c("cruise6", "year", "season", "svspp", "station", "pdlen")) %>% 
    select(cruise6, station, stratum, 
           year,
           season,
           svspp, pdid, pdlen,
           rcatnum, rtot_catnum_stratum,
           tot_catwgt_stratum, rtot_catwgt_stratum,
           rtot_tows_spp_stratum, stratum_area, rnumlen_fin)
  
  #Working with fish data.frame----------------------------------------------------------------------------------#
  fish_ply <- py_all %>%
    select(-tax) %>% 
    left_join(pd_strat, by = c("cruise6", "station", "year", "season", "svspp", "pdid", "pdlen"))
  
  
  ####################################################################################################################################
  ## Take the median value for each prey group
  trans_ply <- fish_ply %>%
    group_by(cruise6, stratum, station,
             year, season, 
             svspp, rcatnum,
             rtot_catnum_stratum, 
             rtot_catwgt_stratum,
             rtot_tows_spp_stratum,
             stratum_area, rnumlen_fin, pycode) %>%
    summarize(pysum = median(pysum, na.rm = FALSE))
  
  ## Weighted mean and mean of pysum
  pysum_wm <- trans_ply %>%
    group_by(cruise6, stratum, station, 
             year, season,
             svspp, rcatnum, 
             rtot_catnum_stratum,
             rtot_tows_spp_stratum,
             stratum_area, pycode) %>% 
    summarize(wmean = weighted.mean(pysum, w = rnumlen_fin))# %>%
  
  ## Mean
  pysum_m <- pysum_wm %>%
    group_by(cruise6, stratum, station,
             year, season,
             svspp, rcatnum,
             rtot_catnum_stratum,
             rtot_tows_spp_stratum,
             stratum_area,
             pycode) %>%
    summarize(musw = mean(wmean, na.rm = TRUE),
              musw2 = wmean * rcatnum)
  
  ## by station
  pysum_wm_s <- pysum_m %>%
    group_by(cruise6, stratum, 
             year, season,
             svspp,
             rtot_catnum_stratum,
             rtot_tows_spp_stratum,
             stratum_area, 
             pycode) %>% 
    summarize(tmsw_strat = sum(musw2, na.rm = TRUE))
  
  musw_strat_ply <- pysum_wm_s %>% 
    group_by(cruise6, stratum, 
             year, season,
             svspp,
             rtot_catnum_stratum,
             rtot_tows_spp_stratum,
             stratum_area, 
             pycode) %>% 
    summarize(musw_strat = tmsw_strat/rtot_tows_spp_stratum) %>%
    ungroup() %>%
    mutate(munfish_strat = rtot_catnum_stratum / rtot_tows_spp_stratum)
  
  
  munfish_stratdat_ply <- musw_strat_ply %>%
    ungroup() %>%
    mutate(munfish_strat = rtot_catnum_stratum / rtot_tows_spp_stratum) %>%
    select(cruise6, stratum,
           year, season,
           svspp, munfish_strat)
  
  
  #weight by stratum area
  pymean_strat <- musw_strat_ply %>% 
    group_by(svspp, year, season,
             pycode) %>% 
    summarize(msw_strat = weighted.mean(musw_strat, stratum_area, na.rm = TRUE),
              m_nfish_strat = weighted.mean(munfish_strat, stratum_area, na.rm = TRUE),
              num_stra = n())
  
  
  meansw_s_ply <- pymean_strat %>% 
    group_by(svspp, year, season, pycode) %>%
    summarize(meansw_s = msw_strat/m_nfish_strat)
  
  meansw_ply <- pysum_m %>% 
    group_by(svspp, year, season, pycode) %>%
    summarize(meansw = weighted.mean(musw, rcatnum, na.rm = TRUE),
              num_tows = n())
  
  master_ply <- pysum_m %>% #musw and musw2
    left_join(pysum_wm_s) %>%  #tmsw_strat
    left_join(musw_strat_ply) %>% # musw_strat
    left_join(meansw_ply) %>% # meansw
    left_join(meansw_s_ply) %>% # meansw_s
    left_join(pymean_strat) %>%     # msw_strat
    select(-munfish_strat) %>% 
    mutate(prod = rcatnum^2 * ((musw - meansw))^2,
           prodf = (rcatnum - m_nfish_strat)^2,
           prodd = (musw2 - musw_strat)^2,
           prod_cov = (rcatnum - m_nfish_strat) * (musw2 - musw_strat))# %>% 
  
  mprod_mnumfish2_ply <- master_ply %>%
    group_by(svspp, year, season, pycode) %>%
    summarize(mprod = mean(prod, na.rm = TRUE),
              mnumfish = mean(rcatnum, na.rm = TRUE))
  
  new4_ply <- master_ply %>% 
    group_by(svspp, year, season, pycode) %>% 
    summarize(sprod = sum(prod, na.rm = TRUE),
              mprod = mean(prod, na.rm = TRUE),
              mnumfish = mean(rcatnum, na.rm = TRUE))
  
  new6_ply <- master_ply %>% 
    group_by(svspp, year, season,
             pycode, cruise6, stratum,
             stratum_area, rtot_tows_spp_stratum,
             m_nfish_strat) %>%
    summarize(sprodf = sum(prodf, na.rm = TRUE),
              sprodd = sum(prodd, na.rm = TRUE),
              sprod_cov = sum(prod_cov, na.rm = TRUE)) %>% 
    ungroup() %>% 
    mutate(dfntows_strat = rtot_tows_spp_stratum - 1,
           varprodf = (stratum_area^2) * ((sprodf/dfntows_strat)/rtot_tows_spp_stratum),
           varprodd = (stratum_area^2) * ((sprodd/dfntows_strat)/rtot_tows_spp_stratum),
           varprod_cov = (stratum_area^2) * ((sprod_cov/dfntows_strat)/rtot_tows_spp_stratum),
           varprodf = if_else(rtot_tows_spp_stratum > 1,
                              varprodf,
                              0),
           varprodd = if_else(rtot_tows_spp_stratum > 1,
                              varprodd,
                              0),
           varprod_cov = if_else(rtot_tows_spp_stratum > 1, 
                                 varprod_cov,
                                 0))
  
  sumvarprod_ply <- new6_ply %>% 
    group_by(svspp, year, season, pycode) %>%
    summarize(svarprodf = sum(varprodf, na.rm = TRUE),
              svarprodd = sum(varprodd, na.rm = TRUE),
              svarprod_cov = sum(varprod_cov, na.rm = TRUE),
              stratum_area = sum(stratum_area, na.rm = TRUE)) %>% 
    ungroup() %>% 
    mutate(varf = svarprodf / stratum_area^2,
           vard = svarprodd/ stratum_area^2,
           var_cov = svarprod_cov/ stratum_area^2) %>% 
    select(-stratum_area)
  
  new4_strat_ply <- new4_ply %>% 
    left_join(sumvarprod_ply) 
  
  
  #merge with  select master columns
  six_ply <- new4_strat_ply %>%
    left_join(master_ply) %>% 
    mutate(variance = ifelse(num_tows > 1 & mnumfish != 0 & meansw!=0 & m_nfish_strat !=0 & meansw_s!=0,
                             1/(num_tows * (mnumfish)^2) * (sprod/(num_tows-1)),
                             0),
           cv = ifelse(num_tows > 1 & mnumfish != 0 & meansw != 0 & m_nfish_strat != 0 & meansw_s != 0,
                       ((variance)^0.5)/meansw,
                       0),
           var_s = ifelse(num_tows > 1 & mnumfish != 0 & meansw != 0 & m_nfish_strat != 0 & meansw_s != 0,
                          (meansw_s^2) * ((varf/(m_nfish_strat^2)) + (vard/(msw_strat^2)) - (2 * var_cov/m_nfish_strat/msw_strat)),
                          0),
           cv_s = ifelse(num_tows > 1 & mnumfish != 0 & meansw != 0 & m_nfish_strat != 0 & meansw_s != 0,
                         ((var_s)^0.5)/meansw_s,0)) %>% 
    select(pycode, svspp, year, season, meansw,
           meansw_s, num_tows, m_nfish_strat, num_stra, 
           variance, cv, var_s, cv_s, pycode) %>% 
    distinct(.keep_all = TRUE)
  
  final_ply <- six_ply %>% 
    mutate(pycode = as.factor(pycode)) %>% 
    left_join(py_list) %>% 
    left_join(nstom_df) %>% 
    group_by(svspp, year, season) %>% 
    mutate(totwt = sum(meansw, na.rm = TRUE),
           totwt_s = sum(meansw_s, na.rm = TRUE),
           relmsw = 100*(meansw/totwt),
           relmsw_s = 100*(meansw_s/totwt_s),
           ci = sqrt(variance/num_tows)*2,
           relci = (ci/totwt)*100,
           ci_s = sqrt(var_s/num_tows)*2,
           relci_s = (ci_s/totwt_s)*100) %>% 
    select(svspp, year, season, meansw, num_tows,
           variance, cv, prey = tax, totwt, 
           relmsw, ci, relci, nstom)
  
  
  # })
  return(final_ply)
  
}

# diet_ply <- final_ply %>%
#   select(year, season, prey, relmsw, num_tows) %>%
#   group_by(season, prey) %>%
#   filter(relmsw>0.01) %>%
#   filter(mean(relmsw)>10.0)
# 
# 
# diet <- final %>%
#   select(year, season, prey, relmsw, num_tows) %>%
#   group_by(season, prey) %>%
#   filter(relmsw>0.01) %>%
#   filter(mean(relmsw)>10.0)
# 
# 
# library(ggplot2)
# compplot <- ggplot(diet, aes(year, relmsw, fill=prey)) +
#   geom_bar(stat = "identity") +
#   ylab("Percent in Diet") +
#   xlab("Year") +
#   facet_wrap("season", nrow=3) +
#   theme_bw() +
#   viridis::scale_fill_viridis(discrete = TRUE) +
#   theme(legend.position="bottom",
#         legend.text=element_text(size=5))
# 
# compplot_ply <- ggplot(diet_ply, aes(year, relmsw, fill=prey)) +
#   geom_bar(stat = "identity") +
#   ylab("Percent in Diet") +
#   xlab("Year") +
#   facet_wrap("season", nrow=3) +
#   theme_bw() +
#   viridis::scale_fill_viridis(discrete = TRUE) +
#   theme(legend.position="bottom",
#         legend.text=element_text(size=5))
# 
# library(patchwork)
# 
# compplot + compplot_ply
# compi <- compplot + geom_bar_interactive(stat = "identity", aes(tooltip = prey, data_id = prey))

# 
# ptm <- proc.time()
# 
# df_diet <- get_diet(103)
# ggiraph(code = print(df_diet), height=14)
# 
# out <- data.frame(t = (proc.time() - ptm)[3],
#                   sys = Sys.time())
# out


# d <- read.csv("~/attempts.csv")
# d <- d %>% arrange(time)
# plot(d$sys, type = "l")
# points(rep(mean(d$sys),nrow(d)))
```

Plot bluefish annual diet

```{r}

bluefish <- get_diet(135) 

p1 <-   ggplot(bluefish, aes(year, relmsw, fill=prey)) +
   geom_bar(stat = "identity") + #
   ylab("Percent in Diet") +
   xlab("Year") +
   facet_wrap("season", nrow=4) +
   theme_bw() +
   viridis::scale_fill_viridis(discrete = TRUE) +
   theme(legend.position = "none"
         #legend.position="bottom",
         #legend.text=element_text(size=5)
         ) +
    geom_bar_interactive(stat = "identity", aes(tooltip = prey, data_id = prey))

ggiraph(code = print(p1), height=14)  

```


## Which predators to include?

Fish feeding guilds based on dietary overlap have been defined for the Northeast US shelf based on NEFSC trawl survey diet data from 1973-1997 [@garrison_dietary_2000]. In this analysis, all size classes of bluefish were classified as piscivores. A reasonable first cut would be to use all predator/size combinations identifed as piscivores in @garrison_dietary_2000. This would include:

```{r}
# code for piscivore table
piscivores <- ecodata::species_groupings %>%
  select(COMNAME, SizeCat, Garrison.Link) %>%
  filter(!is.na(Garrison.Link),
         Garrison.Link == "Piscivores") %>%
  mutate(PiscGuild = case_when(COMNAME == "WINTER SKATE" ~ "c",
                               COMNAME == "WEAKFISH" ~ "b", 
                               COMNAME == "BLUEFISH" & SizeCat == "S" ~ "b",
                               TRUE ~ "a")) %>%
  distinct()

datatable(piscivores, rownames = FALSE,
          caption = "Piscivores feeding guild from Garrison and Link 2000",
          options = list(pageLength = 25))

```


## Building an input prey dataset

### NEFSC data

Following data prep in @ng_predator_2021, we first select data for all piscivores, then collapsed to first and second half of year, combining winter and summer surveys with spring and fall to expand datasets. 

```{r}
# code for piscivore table
piscivores <- ecodata::species_groupings %>%
  select(COMNAME, SizeCat, Garrison.Link) %>%
  filter(!is.na(Garrison.Link),
         Garrison.Link == "Piscivores") %>%
  mutate(PiscGuild = case_when(COMNAME == "WINTER SKATE" ~ "c",
                               COMNAME == "WEAKFISH" ~ "b", 
                               COMNAME == "BLUEFISH" & SizeCat == "S" ~ "b",
                               TRUE ~ "a")) %>%
  distinct()

# food habits 1973-2020 piscivores only; include empties

fh.nefsc.pisc <- allfh %>%
  #filter(pynam != "EMPTY") %>%
  left_join(piscivores, by = c("pdcomnam" = "COMNAME",
                               "sizecat" = "SizeCat")) %>%
  filter(!is.na(Garrison.Link))

 preycount <- fh.nefsc.pisc %>%
   #group_by(year, season, pdcomnam, pynam) %>%
   group_by(pdcomnam, pynam) %>%
   summarise(count = n()) %>%
   #arrange(desc(count))
   pivot_wider(names_from = pdcomnam, values_from = count)

```

How many times in the full dataset was each prey name observed per predator?

```{r}
datatable(preycount, rownames = FALSE,
          extensions = c("FixedColumns"),
          #caption = "Prey observed in piscivores guild (Garrison and Link 2000) 1973-2020",
          options = list(pageLength = 25,
                         scrollX = TRUE,
                         fixedColumns = list(leftColumns = 1)))
```

Start by aggregating all pelagic nekton prey that have at least 10 observations for bluefish (leaving out empty, fish, osteichthes, AR, blown):

```{r}

gencomlist <- fh.nefsc.pisc %>%
  select(pynam, gencom2) %>%
  distinct()

blueprey <- preycount %>%
  filter(BLUEFISH > 9) %>%
  filter(!pynam %in% c("EMPTY", "BLOWN",
                       "FISH", "OSTEICHTHYES",
                       "ANIMAL REMAINS",
                       "FISH SCALES")) %>%
  #filter(!str_detect(pynam, "SHRIMP|CRAB")) %>%
  left_join(gencomlist) %>%
  filter(!gencom2 %in% c("ARTHROPODA", "ANNELIDA",
                         "CNIDARIA", "UROCHORDATA",
                         "ECHINODERMATA", "WORMS",
                         "BRACHIOPODA", "COMB JELLIES",
                         "BRYOZOA", "SPONGES",
                         "MISCELLANEOUS", "OTHER"))
```

```{r}
datatable(blueprey, rownames = FALSE,
          extensions = c("FixedColumns"),
          #caption = "Bluefish prey in all piscivores 1973-2020",
          options = list(pageLength = 25,
                         scrollX = TRUE,
                         fixedColumns = list(leftColumns = 1)))
```

This gives us 20 individual prey names. 

How many tows with piscivore diets had these preynames? 

```{r}
fh.nefsc.pisc.blueprey <- fh.nefsc.pisc %>%
  mutate(blueprey = case_when(pynam %in% blueprey$pynam ~ "blueprey",
                              TRUE ~ "othprey"))

preystn <- fh.nefsc.pisc.blueprey %>%
  group_by(year, season, station) %>%
  count(blueprey) %>%
  pivot_wider(names_from = blueprey, values_from = n) 

#dim(preystn)[1]

bluepreystn <- preystn %>% 
  arrange(desc(blueprey)) %>%
  filter(!is.na(blueprey))

#dim(bluepreystn)[1]

```

Between 1973 and 2020 we have `r dim(preystn)[1]` individual tows where piscivores were collected and `r dim(bluepreystn)[1]` of those tows had bluefish prey. Therefore, `r dim(bluepreystn)[1]/dim(preystn)[1]*100` percent of piscivore tows will be used to get the aggregate prey index. 

Which years and seasons have bluefish prey observed? How many tows each?

```{r}
# coverage <- bluepreystn %>%
#   ungroup() %>%
#   select(year, season) %>%
#   distinct() %>%
#   arrange(year, desc(season))

coverage <- bluepreystn %>%
  group_by(year, season) %>%
  count(station) %>%
  summarize(nstation = sum(n))

datatable(coverage, rownames = FALSE,
          #extensions = c("FixedColumns"),
          caption = "Piscivore stations with bluefish prey 1973-2020",
          options = list(pageLength = 10,
                         autoWidth = TRUE,
                         columnDefs = list(list(width = '200px'))
                         )
          )
```

(Note that the fall 2020 surveys were cancelled, and spring 2020 was partial due to pandemic restrictions.)

No year/season combinations have 0 stations with aggregated bluefish prey. Summarizing the number of stations per year/season with bluefish prey, 1973-2020:

```{r}
summary(coverage$nstation)
```

So we can aggregate over all these prey in all predator stomachs at a particular station to get mean bluefish prey weight per predator stomach. Calculate variance in prey weight too, n prey species, prey diversity index? The catchability covariates at each station could be number of predators, number of predator species, diversity/evenness of predator species, mean predator length, variance predator length. The habitat covariates at each station could be temperature, bottom depth?

```{r}

bluepyall_stn <- fh.nefsc.pisc.blueprey %>%
  #create id linking cruise6_station
  #create season_ng spring and fall Spring=Jan-May, Fall=June-Dec
  mutate(id = paste0(cruise6, "_", station),
         year = as.numeric(year),
         month = as.numeric(month),
         season_ng = case_when(month <= 5 ~ "SPRING",
                               month >= 6 ~ "FALL",
                               TRUE ~ as.character(NA))
         ) %>%
  select(year, season_ng, id, 
         pynam, pyamtw, pywgti, pyvoli, blueprey, 
         pdcomnam, pdid, PiscGuild, pdlen, pdsvol, pdswgt, 
         beglat, beglon, declat, declon, 
         bottemp, surftemp, setdepth) %>%
  group_by(id) %>%
  #mean blueprey g per stomach per tow: sum all blueprey g/n stomachs in tow
  mutate(bluepywt = case_when(blueprey == "blueprey" ~ pyamtw,
                               TRUE ~ 0.0),
         bluepynam = case_when(blueprey == "blueprey" ~ pynam,
                               TRUE ~ NA_character_)) 

stndat <- bluepyall_stn %>%
  select(year, season_ng, id, 
         beglat, beglon, declat, declon, 
         bottemp, surftemp, setdepth) %>%
  distinct()

#pisc stomachs in tow count pdid for each pred and sum
piscstom <- bluepyall_stn %>%
  group_by(id, pdcomnam) %>%
  summarise(nstompd = n_distinct(pdid)) %>%
  group_by(id) %>%
  summarise(nstomtot = sum(nstompd))

#mean and var pred length per tow
pisclen <- bluepyall_stn %>%
  summarise(meanpisclen = mean(pdlen),
            varpisclen = var(pdlen))

bluepyagg_stn <- bluepyall_stn %>%
  summarise(sumbluepywt = sum(bluepywt),
            nbluepysp = n_distinct(bluepynam, na.rm = T),
            npreysp = n_distinct(pynam),
            npiscsp = n_distinct(pdcomnam)) %>%
  left_join(piscstom) %>%
  mutate(meanbluepywt = sumbluepywt/nstomtot) %>%
  left_join(pisclen) %>%
  left_join(stndat)
  
```

### Add NEAMAP

Ensure NEAMAP data colums align with current dataset. Also, add vessel column and fix declon to be negative in nefsc.

```{r}
# current dataset, fix declon, add vessel
nefsc_bluepyagg_stn <- readRDS(here("fhdat/bluepyagg_stn.rds")) %>%
  mutate(declon = -declon,
         vessel = case_when(year<2009 ~ "AL",
                            year>=2009 ~ "HB", 
                            TRUE ~ as.character(NA)))


# NEAMAP add vessel and rename
neamap_bluepreyagg_stn <- read_csv(here("fhdat/NEAMAP_Mean stomach weights_Bluefish Prey.csv")) %>%
  mutate(vessel = "NEAMAP") %>%
  rename(id = station,
         sumbluepywt = sumbluepreywt,
         nbluepysp = nbfpreyspp,
         #npreysp = ,
         npiscsp = npiscspp,
         nstomtot = nstomtot, 
         meanbluepywt = meanbluepreywt,
         meanpisclen = meanpisclen.simple, 
         #varpisclen = ,
         season_ng = season,
         declat  = lat,
         declon = lon,
         bottemp = bWT,
         #surftemp = , 
         setdepth = depthm) 
  
  
# combine  
bluepyagg_stn <-  nefsc_bluepyagg_stn %>%
  bind_rows(neamap_bluepreyagg_stn) 

saveRDS(bluepyagg_stn, here("fhdat/bluepyagg_stn_all.rds"))

```

## Questions for the WG on input data

1.  We truncate the input data to start in 1985 similar to the assessment model. Still Ok?
1.  Should we keep 2020 or leave it out? Incomplete survey for NEFSC, one survey for NEAMAP.
1.  Should we add 2021 data when it becomes available?
1.  Should we use the full spatial domain or reduce the footprint to match bluefish occurrence? How much of the Gulf of Maine and Scotian Shelf should we include?
1.  Should we consider leaving out more dissimilar predators, especially really different life history types and habitat/foraging mode. First to go may be the winter skate which was in a different subgroup from bluefish. Second could be split out small bluefish and weakfish group from @garrison_dietary_2000.
1.  If we consider a multivarite model, what prey categories make the most sense? 


## References