---
title: "Bluefish Diet Summaries for 2022 RTA"
author: "Sarah Gaichas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_fold: hide
link-citations: yes
csl: plos.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

library(tidyverse)
library(here)
library(DT)
library(pdftools)
library(patchwork)
library(ggiraph)


```

## Data sources

For the 13 October 2021 Bluefish WG meeting, we pulled summary diet information from the [NEFSC Diet Data shiny app, Fish Trophic Ecology of the Northeast U.S. Continental Shelf, by Smith B.E. & Rowe S., dated 9/20/2021](https://fwdp.shinyapps.io/tm2020/). These data were pulled 7 October 2021 and were saved in the `datfromshiny` folder in this repository.

NEAMAP diets were queried using the [VIMS food habits data summary web interface](https://www.vims.edu/research/departments/fisheries/programs/mrg_oldwebsite/interaction/fish_food_habits/index.php) on 14 July 2021. Using the VIMS "prey centered data report" The file `bluefishaspreyVIMS.pdf`was retrieved.

Need to investigate whether any other state or inshore surveys collect diet data and add.

## Bluefish as prey

### Who eats bluefish? NEFSC bottom trawl survey

```{r}

bluefishpreds <- read_csv(here("datfromshiny","WEW.Bluefish (Pomatomus saltatrix).2021-10-07.csv"))

totobs <- sum(bluefishpreds$Frequency)
dompred <- bluefishpreds$Predator[which.max(bluefishpreds$Frequency)]
pctdompred <- max(bluefishpreds$Frequency)/totobs*100

```
The NEFSC bottom trawl survey has relatively few records of bluefish as prey.  From 1973-2020, `r totobs` bluefish were identified as prey in fish sampled for diet. Of these, `r dompred` had the most bluefish in stomachs; `r pctdompred`% of all observed.

```{r}
datatable(bluefishpreds[,-c(1:2)], rownames = FALSE,
          caption = 'Table 1: Who eats bluefish on the NEFSC bottom trawl survey. Nstom is total stomachs sampled for the predator, 1973-2020.')
```

### NEAMAP survey

Quick outputs of NEFSC and NEAMAP surveys are not direcly comparable (NEAMAP doesn't say how many times bluefish were observed). However, NEAMAP but does give a % of predator diet for all predators where bluefish were observed in stomachs. Looks like sandbar sharks and striped bass eat them inshore (likely as juveniles).

```{r}
bluefishpredsNEAMAP <- pdf_text(here("datfromVIMS","bluefishaspreyVIMS.pdf")) %>%
  stringr::str_split('\n', simplify = T) %>%
  matrix(ncol = 1)

# tab_start <- stringr::str_which(bluefishpredsNEAMAP, "                                         bluefish")
# tab_end <- stringr::str_which(bluefishpredsNEAMAP, "                       striped bass                     8.8          352         195" )
# tab <- bluefishpredsNEAMAP[(tab_start+1):(tab_end-1), 1] %>%
#   str_replace_all('\\s{2,}', '\t')
# text_conn <- textConnection(tab)
# df <- read.csv(text_conn, sep = '\t', skip = 1)

#wont work but placeholder
bluefishpredsNEAMAP
```


Full striped bass NEAMAP diet data as well as full diet data for sandbar sharks in either numbers or weight are available in the `datfromVIMS` folder. Jim Gartland is showing a much better summary for NEAMAP and ChesMMAP data.

### Literature search (to be expanded)  

Quick research found the following links showing that (adult) bluefish are eaten by [mako sharks](https://web.uri.edu/wetherbee/predator-prey-interactions-between-mako-sharks-isurus-oxyrinchus-and-bluefish-pomatomus-saltatrix/) (Tony Wood, primary author) and have been found in [swordfish](http://www.int-res.com/articles/meps/22/m022p239.pdf) diets.

I found one paper looking at [bluefish cannibalism on juveniles](https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1095-8649.1999.tb00734.x); but nothing else on consumption of juvenile bluefish by predators. There may be more info. We looked at bluefish diets for a previous benchmark assessment and did see some cannibalism; see Fig B5.7, p.522 of [this doc](https://repository.library.noaa.gov/view/noaa/4975)).

## Bluefish as predators

### NEFSC bottom trawl survey diet summaries

Diet summaries from the shiny app use different prey categories depending on the summary. We'll read them all in here to get a list of unique prey across all summaries. 
```{r, readdiets}
bluefishaggdiet <- read_csv(here("datfromshiny","DC.Bluefish (Pomatomus saltatrix).All.2021-10-07.csv"))

# decadal diet
diet70 <- read_csv(here("datfromshiny","DC.Bluefish (Pomatomus saltatrix).1970s.2021-10-07.csv")) %>%
  mutate(Decade = 1970)
diet80 <- read_csv(here("datfromshiny","DC.Bluefish (Pomatomus saltatrix).1980s.2021-10-07.csv"))%>%
  mutate(Decade = 1980)
diet90 <- read_csv(here("datfromshiny","DC.Bluefish (Pomatomus saltatrix).1990s.2021-10-07.csv"))%>%
  mutate(Decade = 1990)
diet00 <- read_csv(here("datfromshiny","DC.Bluefish (Pomatomus saltatrix).2000s.2021-10-07.csv"))%>%
  mutate(Decade = 2000)
diet10 <- read_csv(here("datfromshiny","DC.Bluefish (Pomatomus saltatrix).2010s.2021-10-07.csv"))%>%
  mutate(Decade = 2010)

bluefishdecadediet <- bind_rows(diet70, diet80, diet90, diet00, diet10)

# seasonal diet
dietspring <- read_csv(here("datfromshiny","DC.Bluefish (Pomatomus saltatrix).SPRING.2021-10-07.csv"))%>%
  mutate(Season = "Spring")
dietfall <- read_csv(here("datfromshiny","DC.Bluefish (Pomatomus saltatrix).FALL.2021-10-07.csv"))%>%
  mutate(Season = "Fall")

bluefishseasondiet <- bind_rows(dietspring, dietfall)

# regional diet
dietMAB <- read_csv(here("datfromshiny","DC.Bluefish (Pomatomus saltatrix).MID-ATLANTIC BIGHT.2021-10-07.csv")) %>%
  mutate(Region = "MAB")
dietSNE <- read_csv(here("datfromshiny","DC.Bluefish (Pomatomus saltatrix).SOUTHERN NEW ENGLAND.2021-10-07.csv"))%>%
  mutate(Region = "SNE")
dietGB <- read_csv(here("datfromshiny","DC.Bluefish (Pomatomus saltatrix).GEORGES BANK.2021-10-07.csv"))%>%
  mutate(Region = "GB")

bluefishregiondiet <- bind_rows(dietMAB, dietSNE, dietGB)

# bluefish size diet
dietSM <- read_csv(here("datfromshiny","DC.Bluefish (Pomatomus saltatrix).S.2021-10-07.csv")) %>%
  mutate(Size = "Small")
dietMED <- read_csv(here("datfromshiny","DC.Bluefish (Pomatomus saltatrix).M.2021-10-07.csv"))%>%
  mutate(Size = "Medium")
dietLG <- read_csv(here("datfromshiny","DC.Bluefish (Pomatomus saltatrix).L.2021-10-07.csv"))%>%
  mutate(Size = "Large")

bluefishsizediet <- bind_rows(dietSM, dietMED, dietLG)

preylist <- unique(c(bluefishaggdiet$Prey, bluefishdecadediet$Prey, bluefishregiondiet$Prey, bluefishseasondiet$Prey, bluefishsizediet$Prey))

```

We will define the colors used for the prey categories and use them consistently throughout the analyses. These can be changed here and carried through all subsequent plots. There is no way to really keep track of these in the plots below, so click a bar to get that bar highlighted with a prey name.

```{r}
#from http://medialab.github.io/iwanthue/ using 35 categories, colorblind friendly
# again from http://medialab.github.io/iwanthue/ All colors colorspace, colorblind friendly, hard
preycol <- c("#00495d",
"#3ac100",
"#a646f7",
"#72ff75",
"#8d00a6",
"#c6ff90",
"#0268f1",
"#ff8d23",
"#0144a6",
"#01a249",
"#e1009e",
"#abffe1",
"#7e0082",
"#fffdd4",
"#24001c",
"#bbf6ff",
"#a60029",
"#0176c8",
"#8a4700",
"#a083ff",
"#454400",
"#ff7fff",
"#005d35",
"#c9005e",
"#00483e",
"#ff96e4",
"#291d00",
"#d5a5ff",
"#2e0400",
"#ffc5d6",
"#00285f",
"#ffbb88",
"#4a002e",
"#ff8092",
"#68001a")
names(preycol) <- as.factor(preylist)

```

```{r}
dfpreycol <- as.data.frame(preycol) %>%
  rownames_to_column(var = "preyname")

preycolplot <- ggplot(dfpreycol, aes(x=preyname, weight=1, fill=preycol)) + 
  geom_bar() +
  scale_fill_manual(values=preycol) 

# see https://stackoverflow.com/questions/43366616/ggplot2-legend-only-in-a-plot
library(gridExtra)
library(grid)
g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

preykey <- g_legend(preycolplot)
grid.draw(preykey)

```

#### Bluefish diet in aggregate (all years, regions, and bluefish sizes), 1973-2020 {.tabset}

##### Plot
```{r}
p <- ggplot(bluefishaggdiet, aes(x=as.factor("Aggregate"), y=Pct.m, fill=Prey)) +
  geom_bar_interactive(width = 0.95, stat = "identity", show.legend = FALSE,
                       aes(tooltip = Prey, data_id = Prey))+
  scale_fill_manual(values=preycol) +         #custom colors
  ggthemes::theme_tufte()
ggiraph(code=print(p))
```

##### Table
```{r}
datatable(bluefishaggdiet[,-c(1:2, 10)], rownames = FALSE,
          caption = 'Table 3: Bluefish prey from all samples combined.')
```

#### {-}

#### Bluefish diet by season (all years, regions, and bluefish sizes) {.tabset}

##### Plot
```{r}
p <- ggplot(bluefishseasondiet, aes(x=as.factor(Season), y=Pct.m, fill=Prey)) +
  geom_bar_interactive(width = 0.95, stat = "identity", show.legend = FALSE,
                       aes(tooltip = Prey, data_id = Prey))+
  scale_fill_manual(values=preycol) +         #custom colors
  ggthemes::theme_tufte()
ggiraph(code=print(p))
```

##### Table
```{r}
datatable(bluefishseasondiet[,-c(1:2, 10)], rownames = FALSE,
          caption = 'Table 4: Bluefish prey by season, 1973-2020.')
```

#### {-}

#### Bluefish diet by decade (all regions and bluefish sizes) {.tabset} 

##### Plot
```{r}
p <- ggplot(bluefishdecadediet, aes(x=as.factor(Decade), y=Pct.m, fill=Prey)) +
  geom_bar_interactive(width = 0.95, stat = "identity", show.legend = FALSE,
                       aes(tooltip = Prey, data_id = Prey))+
  scale_fill_manual(values=preycol) +         #custom colors
  ggthemes::theme_tufte()
ggiraph(code=print(p))
```

##### Table
```{r}
datatable(bluefishdecadediet[,-c(1:2, 10)], rownames = FALSE,
          caption = 'Table 5: Bluefish prey by decade, 1973-2020.')
```

#### {-}

#### Bluefish diet by region (all years and bluefish sizes) {.tabset}  

##### Plot
```{r}
p <- ggplot(bluefishregiondiet, aes(x=as.factor(Region), y=Pct.m, fill=Prey)) +
  geom_bar_interactive(width = 0.95, stat = "identity", show.legend = FALSE,
                       aes(tooltip = Prey, data_id = Prey))+
  scale_fill_manual(values=preycol) +         #custom colors
  ggthemes::theme_tufte()
ggiraph(code=print(p))
```

##### Table
```{r}
datatable(bluefishregiondiet[,-c(1:2, 10)], rownames = FALSE,
          caption = 'Table 6: Bluefish prey by region, 1973-2020.')
```

#### {-}

#### Bluefish diet by bluefish size (all years and regions) {.tabset}

Bluefish size categories: Small = 10-30 cm; Medium = 31-70 cm; Large = >70 cm

##### Plot
```{r}
p <- ggplot(bluefishsizediet, aes(x=as.factor(Size), y=Pct.m, fill=Prey)) +
  geom_bar_interactive(width = 0.95, stat = "identity", show.legend = FALSE,
                       aes(tooltip = Prey, data_id = Prey))+
  scale_fill_manual(values=preycol) +         #custom colors
  ggthemes::theme_tufte()
ggiraph(code=print(p))

```

##### Table
```{r}
datatable(bluefishsizediet[,-c(1:2, 10)], rownames = FALSE,
          caption = 'Table 7: Bluefish prey by bluefish size, 1973-2020.')
```

#### {-}

### Bluefish annual diet by season (1973-2016)

Initial test food habits dataset from [2018 ECSA](https://github.com/NOAA-EDAB/ECSA/blob/master/data/allfhsg.RData) has food habits 1973 to 2016. Will get fuller up to date info from Brian Smith shortly.

This is the `get_diet()` function from [ECSA](https://github.com/NOAA-EDAB/ECSA/blob/master/R/get_diet.R), modified to use all available strata:

```{r, get_diet}
#' Get diet composition data for plotting
#'
#' Creates a dataset for plotting annual or seasonal weighted diet composition with sample sizes.
#' Datasets are for a selected species and set of seasonal survey strata.
#' Currently only works for summer flounder with strata pre-selected.
#' Need to clearly define what each data column is, render to tidy data.
#' This is a first draft that will be revised with dplyr functions later.
#' n.b., Original file from Brian Smith, August 23 2018 was allwt_nstoms.R, renamed as get_diet.R
#'
#'
#' @param species_code numeric. Three digit svspp code
#'
#' @return dataframe with variables svspp, year, season, meansw, num_tows, variance, cv, prey, totwt, relmsw, ci, relci, nstom
#'
#' @examples
#' head(get_diet(103))
#'

get_diet <- function(species_code){
  
  #### This part here should be replaced with a file for all NEUS stocks
  # sss <- read.csv("data/seasonal_stock_strata.csv",
  #                 stringsAsFactors = FALSE)
  # 
  # sixcode <- c('acared','alewif','amepla','atlcod','atlhal','atlher','atlmac','atlwol',
  #              'barska','blabas','bluefi','bluher','butter','cleska','haddoc',
  #              'litska','monkfh','ocpout','offhak','polloc','redhak','rosska',
  #              'scupzz','silhak','smodog','smoska','spidog','sumflo','thoska',
  #              'whihak','window','winflo','winska','witflo','yelflo','amlobs','joncra')
  # 
  # svspp_list <- c(155,33,102,73,101,32,121,192,22,141,
  #                 135,34,131,24,74,26,197,193,69,
  #                 75,77,25,143,72,13,27,15,103,
  #                 28,76,108,106,23,107,105,301,312)
  # 
  # 
  # #Get data, manipulate, set constants
  # svspp_df <- data.frame(sp = sixcode,
  #                        svspp = svspp_list, 
  #                        stringsAsFactors = FALSE)
  # 
  # seasonal_strata <- sss %>% 
  #   mutate(season = toupper(season)) %>% 
  #   left_join(svspp_df, by = "sp") %>% 
  #   rename(stratum = strata) %>% 
  #   filter(svspp %in% species_code)


  # seasonal_strata <- read.csv("data/stock_list.csv", stringsAsFactors = FALSE) %>% 
  #   dplyr::select(season,
  #                 sp = species_code,
  #                 stock_area = stock,
  #                 stratum = strat,
  #                 svspp) %>% 
  #   dplyr::filter(svspp == species_code,
  #                 season %in% c("fall", "spring")) %>% 
  #   dplyr::mutate(season = toupper(season))
  
  
  ## Need to figure out how to access via ERDDAP
  #load("data/allfhsg.RData")
  
  load(here("fhdat", "allfhsg_2016.RData"))
  
  # spring_strata <- seasonal_strata$stratum[seasonal_strata$season == 'SPRING']
  # summer_strata <- seasonal_strata$stratum[seasonal_strata$season == 'SUMMER']
  # fall_strata <-   seasonal_strata$stratum[seasonal_strata$season == 'FALL']
  # winter_strata <- seasonal_strata$stratum[seasonal_strata$season == 'WINTER']
  
  ## Filter out only good stomachs for strata and species
  allsum_raw <- allfhsg %>%
    filter(pynam != 'BLOWN', 
           pynam != 'PRESERVED',
           pynam != ' ',
           purcode == 10, 
           svspp %in% species_code)#,
           # (season == "SPRING" & stratum %in% spring_strata) |
           #   (season == "SUMMER" & stratum %in% summer_strata) |
           #   (season == "FALL"   & stratum %in% fall_strata)   |
           #   (season == "WINTER" & stratum %in% winter_strata))
  
  ## Number of stomachs by length and weight
  
  ## Sum by length
  allsum_len <- allsum_raw %>%
    group_by(year,
             season,
             svspp,
             cruise,
             station,
             pdid,
             pdsex,
             pdlen) %>%
    summarise(totwt = sum(pyamtw)) %>%
    na.omit() %>%
    group_by(year,
             season,
             svspp) %>%
    summarise(nstom    = n(),
              meanstom = mean(totwt, na.rm = TRUE),
              varstom  = var(totwt, na.rm = TRUE),
              meanlen  = mean(pdlen, na.rm = TRUE),
              numlen   = n(),
              minstom  = min(totwt, na.rm = TRUE),
              maxstom  = max(totwt, na.rm = TRUE),
              minlen   = min(pdlen, na.rm = TRUE),
              maxlen   = max(pdlen, na.rm = TRUE))
  
  ## Sum by weight
  allsum_wgt <- allsum_raw %>%
    group_by(year,
             season,
             svspp,
             cruise,
             station,
             pdid,
             pdsex,
             pdwgt,
             pdlen) %>%
    summarise(totwt = sum(pyamtw, na.rm = TRUE)) %>%
    na.omit() %>%
    group_by(year,
             season,
             svspp) %>%
    summarise(meanwgt = mean(pdwgt, na.rm = TRUE),
              numwgt  = n(),
              minwgt  = min(pdwgt, na.rm = TRUE),
              maxwgt  = max(pdwgt, na.rm = TRUE))
  
  #stomstats2
  nstom_df <- allsum_len %>%
    left_join(allsum_wgt, by = c("year", "season", "svspp")) %>%
    # mutate(std.error = sqrt(varstom/nstom)) %>% 
    select(svspp, year, season, nstom)
  
  #----------------------------------Start weighted diet proportion code-------------------------------------#
  
  ## Select and rename the appropriate columns
  allsum_strat <- allsum_raw %>%
    select(cruise6, stratum, station, 
           year,
           season,
           svspp, pdid, 
           pdsex, pdlen, 
           tax = collsci, 
           pyamt = pyamtw, 
           catnum, numlen, 
           tot_catnum_stratum, tot_catwgt_stratum, tot_tows_spp_stratum, 
           stratum_area)
  
  ## Group into seasonal length-class and remove NAs
  num_strat <- allsum_strat %>%
    group_by(cruise6,
             station,
             year,
             season,
             svspp,
             pdid,
             pdsex,
             pdlen) %>%
    summarise(xxxx = n()) %>%
    group_by(cruise6,
             station, 
             year,
             season, 
             svspp, 
             pdsex, 
             pdlen) %>%
    summarise(numlen2 = n()) %>%
    left_join(allsum_strat,  by = c("cruise6", "station", "year",
                                    "season", "svspp", "pdsex", "pdlen")) %>% 
    mutate(numlen_fin = case_when(numlen < numlen2 ~ numlen2,
                                  numlen >= numlen2 ~ numlen,
                                  TRUE ~ NA_integer_)) %>%
    select(c(cruise6, stratum, station,
             year,
             season, 
             svspp, pdid, pdsex, pdlen, tax, pyamt, 
             catnum, tot_catnum_stratum, tot_catwgt_stratum,
             tot_tows_spp_stratum, stratum_area, numlen, numlen_fin))
  
  
  sum_strat <- num_strat %>%
    group_by(cruise6,
             station, 
             year, 
             season,
             svspp, 
             pdsex,
             pdlen, 
             numlen_fin) %>%
    summarise(dummy_var = sum(numlen, na.rm = TRUE)) %>% 
    na.omit() %>%
    group_by(cruise6,
             station, 
             year, 
             season, 
             svspp, 
             pdlen) %>%
    summarise(rnumlen_fin = sum(numlen_fin, na.rm = TRUE)) %>%
    left_join(num_strat, by = c("cruise6", "station", "year", "season", "svspp", "pdlen")) %>% 
    mutate(rnumlen_fin = ifelse(svspp !=13 | svspp !=15, 
                                numlen_fin, 
                                rnumlen_fin)) %>%
    group_by(cruise6, 
             station,
             year,
             season,
             svspp, 
             pdsex, 
             catnum) %>%
    summarise(dummy_var = sum(numlen)) %>% 
    na.omit()
  
  
  sum_catnum <- sum_strat %>%
    group_by(cruise6,
             station, 
             year,
             season,
             svspp) %>%
    summarise(rcatnum = sum(catnum, na.rm = TRUE)) %>%
    na.omit() %>%
    left_join(num_strat,  by = c("cruise6", "station", "year", "season", "svspp")) %>% 
    mutate(rcatnum = ifelse(svspp != 13 | svspp != 15, 
                            catnum, 
                            rcatnum))
  
  sum_catstratum <- sum_catnum %>%
    group_by(cruise6, stratum, 
             year,
             season, 
             svspp, 
             pdsex, 
             tot_tows_spp_stratum,
             tot_catnum_stratum,
             tot_catwgt_stratum) %>%
    summarise(dum_var = sum(rcatnum, na.rm = TRUE)) %>%
    na.omit()
  
  ####################################################################################################################################
  
  max_tot_tows_spp_stratum <- sum_catstratum %>%
    group_by(cruise6, 
             stratum, 
             year,
             season,
             svspp) %>% 
    summarise(tot_tows_spp_stratum = max(tot_tows_spp_stratum, na.rm = TRUE))
  
  sum_rcatstratum <- sum_catstratum %>%
    group_by(cruise6, 
             stratum, 
             year,
             season,
             svspp) %>%
    summarise(rtot_catnum_stratum = sum(tot_catnum_stratum, na.rm = TRUE),
              rtot_catwgt_stratum = sum(tot_catwgt_stratum, na.rm = TRUE)) %>% 
    na.omit() %>%
    left_join(max_tot_tows_spp_stratum, by = c("cruise6", "stratum", "year", "season", "svspp")) %>%
    rename(rtot_tows_spp_stratum = tot_tows_spp_stratum)
  
  final_strat <- sum_rcatstratum %>%
    left_join(sum_catnum, by = c("cruise6", "stratum", "year", "season", "svspp")) %>% 
    mutate(rtot_catnum_stratum = ifelse(svspp != 13 | svspp != 15, 
                                        tot_catnum_stratum, 
                                        rtot_catnum_stratum),
           rtot_catwgt_stratum = ifelse(svspp != 13 | svspp != 15, 
                                        tot_catwgt_stratum, 
                                        rtot_catwgt_stratum),
           rtot_tows_spp_stratum = ifelse(svspp != 13 | svspp != 15, 
                                          tot_tows_spp_stratum,
                                          rtot_tows_spp_stratum))
  
  ####################################################################################################################################
  py_raw <- final_strat %>%
    group_by(cruise6, 
             station, 
             year,
             season, 
             svspp, pdid, pdlen, tax) %>%
    summarise(pysum = sum(pyamt, na.rm = TRUE)) %>% 
    na.omit() 
  
  py_nostom <- py_raw %>%
    ungroup() %>% 
    arrange(cruise6, station,
            year,
            season,
            svspp,
            pdid) %>%
    group_by(cruise6,
             station, 
             year,
             season, 
             svspp, 
             pdid) %>% 
    top_n(-1, wt = pysum) %>%
    group_by(cruise6, 
             station, 
             year, 
             season, 
             svspp) %>%
    summarise(nostom = n())
  
  py_list <- data.frame(tax = unique(py_raw$tax),
                        pycode = paste0('prey', 1:length(unique(py_raw$tax))))
  
  
  py_all <- py_nostom %>%
    left_join(py_raw, by = c("cruise6", "station", "year", "season", "svspp")) %>% 
    left_join(py_list, by = "tax")
  
  
  pd_strat <- final_strat %>%
    group_by(cruise6, 
             station, 
             year,
             season,
             svspp, 
             pdid, 
             pdlen) %>% 
    top_n(-1, wt = stratum_area) 
  
  
  pd_nas <- pd_strat %>%
    group_by(cruise6, 
             station, 
             year,
             season,
             svspp, 
             pdlen) %>%
    summarise(rnumlen_fin = sum(numlen_fin, na.rm = TRUE)) %>%
    na.omit()
  
  pd_strat <- pd_strat %>%
    left_join(pd_nas, by = c("cruise6", "year", "season", "svspp", "station", "pdlen")) %>% 
    select(cruise6, station, stratum, 
           year,
           season,
           svspp, pdid, pdlen,
           rcatnum, rtot_catnum_stratum,
           tot_catwgt_stratum, rtot_catwgt_stratum,
           rtot_tows_spp_stratum, stratum_area, rnumlen_fin)
  
  #Working with fish data.frame----------------------------------------------------------------------------------#
  fish_ply <- py_all %>%
    select(-tax) %>% 
    left_join(pd_strat, by = c("cruise6", "station", "year", "season", "svspp", "pdid", "pdlen"))
  
  
  ####################################################################################################################################
  ## Take the median value for each prey group
  trans_ply <- fish_ply %>%
    group_by(cruise6, stratum, station,
             year, season, 
             svspp, rcatnum,
             rtot_catnum_stratum, 
             rtot_catwgt_stratum,
             rtot_tows_spp_stratum,
             stratum_area, rnumlen_fin, pycode) %>%
    summarize(pysum = median(pysum, na.rm = FALSE))
  
  ## Weighted mean and mean of pysum
  pysum_wm <- trans_ply %>%
    group_by(cruise6, stratum, station, 
             year, season,
             svspp, rcatnum, 
             rtot_catnum_stratum,
             rtot_tows_spp_stratum,
             stratum_area, pycode) %>% 
    summarize(wmean = weighted.mean(pysum, w = rnumlen_fin))# %>%
  
  ## Mean
  pysum_m <- pysum_wm %>%
    group_by(cruise6, stratum, station,
             year, season,
             svspp, rcatnum,
             rtot_catnum_stratum,
             rtot_tows_spp_stratum,
             stratum_area,
             pycode) %>%
    summarize(musw = mean(wmean, na.rm = TRUE),
              musw2 = wmean * rcatnum)
  
  ## by station
  pysum_wm_s <- pysum_m %>%
    group_by(cruise6, stratum, 
             year, season,
             svspp,
             rtot_catnum_stratum,
             rtot_tows_spp_stratum,
             stratum_area, 
             pycode) %>% 
    summarize(tmsw_strat = sum(musw2, na.rm = TRUE))
  
  musw_strat_ply <- pysum_wm_s %>% 
    group_by(cruise6, stratum, 
             year, season,
             svspp,
             rtot_catnum_stratum,
             rtot_tows_spp_stratum,
             stratum_area, 
             pycode) %>% 
    summarize(musw_strat = tmsw_strat/rtot_tows_spp_stratum) %>%
    ungroup() %>%
    mutate(munfish_strat = rtot_catnum_stratum / rtot_tows_spp_stratum)
  
  
  munfish_stratdat_ply <- musw_strat_ply %>%
    ungroup() %>%
    mutate(munfish_strat = rtot_catnum_stratum / rtot_tows_spp_stratum) %>%
    select(cruise6, stratum,
           year, season,
           svspp, munfish_strat)
  
  
  #weight by stratum area
  pymean_strat <- musw_strat_ply %>% 
    group_by(svspp, year, season,
             pycode) %>% 
    summarize(msw_strat = weighted.mean(musw_strat, stratum_area, na.rm = TRUE),
              m_nfish_strat = weighted.mean(munfish_strat, stratum_area, na.rm = TRUE),
              num_stra = n())
  
  
  meansw_s_ply <- pymean_strat %>% 
    group_by(svspp, year, season, pycode) %>%
    summarize(meansw_s = msw_strat/m_nfish_strat)
  
  meansw_ply <- pysum_m %>% 
    group_by(svspp, year, season, pycode) %>%
    summarize(meansw = weighted.mean(musw, rcatnum, na.rm = TRUE),
              num_tows = n())
  
  master_ply <- pysum_m %>% #musw and musw2
    left_join(pysum_wm_s) %>%  #tmsw_strat
    left_join(musw_strat_ply) %>% # musw_strat
    left_join(meansw_ply) %>% # meansw
    left_join(meansw_s_ply) %>% # meansw_s
    left_join(pymean_strat) %>%     # msw_strat
    select(-munfish_strat) %>% 
    mutate(prod = rcatnum^2 * ((musw - meansw))^2,
           prodf = (rcatnum - m_nfish_strat)^2,
           prodd = (musw2 - musw_strat)^2,
           prod_cov = (rcatnum - m_nfish_strat) * (musw2 - musw_strat))# %>% 
  
  mprod_mnumfish2_ply <- master_ply %>%
    group_by(svspp, year, season, pycode) %>%
    summarize(mprod = mean(prod, na.rm = TRUE),
              mnumfish = mean(rcatnum, na.rm = TRUE))
  
  new4_ply <- master_ply %>% 
    group_by(svspp, year, season, pycode) %>% 
    summarize(sprod = sum(prod, na.rm = TRUE),
              mprod = mean(prod, na.rm = TRUE),
              mnumfish = mean(rcatnum, na.rm = TRUE))
  
  new6_ply <- master_ply %>% 
    group_by(svspp, year, season,
             pycode, cruise6, stratum,
             stratum_area, rtot_tows_spp_stratum,
             m_nfish_strat) %>%
    summarize(sprodf = sum(prodf, na.rm = TRUE),
              sprodd = sum(prodd, na.rm = TRUE),
              sprod_cov = sum(prod_cov, na.rm = TRUE)) %>% 
    ungroup() %>% 
    mutate(dfntows_strat = rtot_tows_spp_stratum - 1,
           varprodf = (stratum_area^2) * ((sprodf/dfntows_strat)/rtot_tows_spp_stratum),
           varprodd = (stratum_area^2) * ((sprodd/dfntows_strat)/rtot_tows_spp_stratum),
           varprod_cov = (stratum_area^2) * ((sprod_cov/dfntows_strat)/rtot_tows_spp_stratum),
           varprodf = if_else(rtot_tows_spp_stratum > 1,
                              varprodf,
                              0),
           varprodd = if_else(rtot_tows_spp_stratum > 1,
                              varprodd,
                              0),
           varprod_cov = if_else(rtot_tows_spp_stratum > 1, 
                                 varprod_cov,
                                 0))
  
  sumvarprod_ply <- new6_ply %>% 
    group_by(svspp, year, season, pycode) %>%
    summarize(svarprodf = sum(varprodf, na.rm = TRUE),
              svarprodd = sum(varprodd, na.rm = TRUE),
              svarprod_cov = sum(varprod_cov, na.rm = TRUE),
              stratum_area = sum(stratum_area, na.rm = TRUE)) %>% 
    ungroup() %>% 
    mutate(varf = svarprodf / stratum_area^2,
           vard = svarprodd/ stratum_area^2,
           var_cov = svarprod_cov/ stratum_area^2) %>% 
    select(-stratum_area)
  
  new4_strat_ply <- new4_ply %>% 
    left_join(sumvarprod_ply) 
  
  
  #merge with  select master columns
  six_ply <- new4_strat_ply %>%
    left_join(master_ply) %>% 
    mutate(variance = ifelse(num_tows > 1 & mnumfish != 0 & meansw!=0 & m_nfish_strat !=0 & meansw_s!=0,
                             1/(num_tows * (mnumfish)^2) * (sprod/(num_tows-1)),
                             0),
           cv = ifelse(num_tows > 1 & mnumfish != 0 & meansw != 0 & m_nfish_strat != 0 & meansw_s != 0,
                       ((variance)^0.5)/meansw,
                       0),
           var_s = ifelse(num_tows > 1 & mnumfish != 0 & meansw != 0 & m_nfish_strat != 0 & meansw_s != 0,
                          (meansw_s^2) * ((varf/(m_nfish_strat^2)) + (vard/(msw_strat^2)) - (2 * var_cov/m_nfish_strat/msw_strat)),
                          0),
           cv_s = ifelse(num_tows > 1 & mnumfish != 0 & meansw != 0 & m_nfish_strat != 0 & meansw_s != 0,
                         ((var_s)^0.5)/meansw_s,0)) %>% 
    select(pycode, svspp, year, season, meansw,
           meansw_s, num_tows, m_nfish_strat, num_stra, 
           variance, cv, var_s, cv_s, pycode) %>% 
    distinct(.keep_all = TRUE)
  
  final_ply <- six_ply %>% 
    mutate(pycode = as.factor(pycode)) %>% 
    left_join(py_list) %>% 
    left_join(nstom_df) %>% 
    group_by(svspp, year, season) %>% 
    mutate(totwt = sum(meansw, na.rm = TRUE),
           totwt_s = sum(meansw_s, na.rm = TRUE),
           relmsw = 100*(meansw/totwt),
           relmsw_s = 100*(meansw_s/totwt_s),
           ci = sqrt(variance/num_tows)*2,
           relci = (ci/totwt)*100,
           ci_s = sqrt(var_s/num_tows)*2,
           relci_s = (ci_s/totwt_s)*100) %>% 
    select(svspp, year, season, meansw, num_tows,
           variance, cv, prey = tax, totwt, 
           relmsw, ci, relci, nstom)
  
  
  # })
  return(final_ply)
  
}

# diet_ply <- final_ply %>%
#   select(year, season, prey, relmsw, num_tows) %>%
#   group_by(season, prey) %>%
#   filter(relmsw>0.01) %>%
#   filter(mean(relmsw)>10.0)
# 
# 
# diet <- final %>%
#   select(year, season, prey, relmsw, num_tows) %>%
#   group_by(season, prey) %>%
#   filter(relmsw>0.01) %>%
#   filter(mean(relmsw)>10.0)
# 
# 
# library(ggplot2)
# compplot <- ggplot(diet, aes(year, relmsw, fill=prey)) +
#   geom_bar(stat = "identity") +
#   ylab("Percent in Diet") +
#   xlab("Year") +
#   facet_wrap("season", nrow=3) +
#   theme_bw() +
#   viridis::scale_fill_viridis(discrete = TRUE) +
#   theme(legend.position="bottom",
#         legend.text=element_text(size=5))
# 
# compplot_ply <- ggplot(diet_ply, aes(year, relmsw, fill=prey)) +
#   geom_bar(stat = "identity") +
#   ylab("Percent in Diet") +
#   xlab("Year") +
#   facet_wrap("season", nrow=3) +
#   theme_bw() +
#   viridis::scale_fill_viridis(discrete = TRUE) +
#   theme(legend.position="bottom",
#         legend.text=element_text(size=5))
# 
# library(patchwork)
# 
# compplot + compplot_ply
# compi <- compplot + geom_bar_interactive(stat = "identity", aes(tooltip = prey, data_id = prey))

# 
# ptm <- proc.time()
# 
# df_diet <- get_diet(103)
# ggiraph(code = print(df_diet), height=14)
# 
# out <- data.frame(t = (proc.time() - ptm)[3],
#                   sys = Sys.time())
# out


# d <- read.csv("~/attempts.csv")
# d <- d %>% arrange(time)
# plot(d$sys, type = "l")
# points(rep(mean(d$sys),nrow(d)))
```

Plot bluefish annual diet

```{r}

bluefish <- get_diet(135) 

p1 <-   ggplot(bluefish, aes(year, relmsw, fill=prey)) +
   geom_bar(stat = "identity") + #
   ylab("Percent in Diet") +
   xlab("Year") +
   facet_wrap("season", nrow=4) +
   theme_bw() +
   viridis::scale_fill_viridis(discrete = TRUE) +
   theme(legend.position = "none"
         #legend.position="bottom",
         #legend.text=element_text(size=5)
         ) +
    geom_bar_interactive(stat = "identity", aes(tooltip = prey, data_id = prey))

ggiraph(code = print(p1), height=14)  

```


### Bluefish consumption estimates (preliminary based on NEFSC diet only)

Consumption estimates from the shiny app 
```{r, readcons}

totcons <- read_csv(here("datfromshiny", "C.Bluefish (Pomatomus saltatrix).All prey.2021-10-07.csv"))

preycons <- read_csv(here("datfromshiny", "C.Bluefish (Pomatomus saltatrix).Atlantic herring (Clupea harengus).2021-10-07.csv"))

preycons1 <-read_csv(here("datfromshiny", "C.Bluefish (Pomatomus saltatrix).Atlantic mackerel (Scomber scombrus).2021-10-07.csv"))
preycons2 <- read_csv(here("datfromshiny", "C.Bluefish (Pomatomus saltatrix).Butterfish (Peprilus triacanthus).2021-10-07.csv"))
preycons3 <- read_csv(here("datfromshiny", "C.Bluefish (Pomatomus saltatrix).Loligo squid (Loligo sp.).2021-10-07.csv"))
preycons4 <-  read_csv(here("datfromshiny", "C.Bluefish (Pomatomus saltatrix).Other prey.2021-10-07.csv"))
preycons5 <-  read_csv(here("datfromshiny", "C.Bluefish (Pomatomus saltatrix).Sand lance (Ammodytes sp.).2021-10-07.csv"))
preycons6 <- read_csv(here("datfromshiny", "C.Bluefish (Pomatomus saltatrix).Silver hake (Merluccius bilinearis).2021-10-07.csv"))



```

