---
title: "Bluefish Diet Summaries for 2022 Research Track"
author: "Sarah Gaichas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_fold: hide
link-citations: yes
csl: plos.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

library(tidyverse)
library(here)
library(DT)
library(pdftools)

```

## Data sources

For the 13 October 2021 Bluefish WG meeting, we pulled summary diet information from the [NEFSC Diet Data shiny app, Fish Trophic Ecology of the Northeast U.S. Continental Shelf, by Smith B.E. & Rowe S., dated 9/20/2021](https://fwdp.shinyapps.io/tm2020/). These data were pulled 7 October 2021 and were saved in the `datfromshiny` folder in this repository.

NEAMAP diets were queried using the [VIMS food habits data summary web interface](https://www.vims.edu/research/departments/fisheries/programs/mrg_oldwebsite/interaction/fish_food_habits/index.php) on 14 July 2021. Using the VIMS "prey centered data report" The file `bluefishaspreyVIMS.pdf`was retrieved.

Need to investigate whether any other state or inshore surveys collect diet data and add.

## Bluefish as prey

### Who eats bluefish? NEFSC bottom trawl survey

```{r}

bluefishpreds <- read_csv(here("datfromshiny","WEW.Bluefish (Pomatomus saltatrix).2021-10-07.csv"))

totobs <- sum(bluefishpreds$Frequency)
dompred <- bluefishpreds$Predator[which.max(bluefishpreds$Frequency)]
pctdompred <- max(bluefishpreds$Frequency)/totobs*100

```
The NEFSC bottom trawl survey has relatively few records of bluefish as prey.  From 1973-2020, `r totobs` bluefish were identified as prey in fish sampled for diet. Of these, `r dompred` had the most bluefish in stomachs; `r pctdompred`% of all observed.

```{r}
datatable(bluefishpreds[,-c(1:2)], rownames = FALSE,
          caption = 'Table 1: Who eats bluefish on the NEFSC bottom trawl survey. Nstom is total stomachs sampled for the predator, 1973-2020.')
```

### NEAMAP survey

Quick outputs of NEFSC and NEAMAP surveys are not direcly comparable (NEAMAP doesn't say how many times bluefish were observed). However, NEAMAP but does give a % of predator diet for all predators where bluefish were observed in stomachs. Looks like sandbar sharks and striped bass eat them inshore (likely as juveniles).

```{r}
bluefishpredsNEAMAP <- pdf_text(here("datfromVIMS","bluefishaspreyVIMS.pdf")) %>%
  stringr::str_split('\n', simplify = T) %>%
  matrix(ncol = 1)

#wont work but placeholder
datatable(bluefishpredsNEAMAP)
```


You can see the full striped bass NEAMAP diet data in another attached pdf. I'm having trouble understanding the full diet data for sandbar sharks in either numbers or weight (both attached); they don't seem to add up to the number of predators in the bluefish as prey pdf so I will ask the VIMS folks about this.

### Literature search (to be expanded)  

Quick research found the following links showing that (adult) bluefish are eaten by [mako sharks](https://web.uri.edu/wetherbee/predator-prey-interactions-between-mako-sharks-isurus-oxyrinchus-and-bluefish-pomatomus-saltatrix/) (Tony Wood, primary author) and have been found in [swordfish](http://www.int-res.com/articles/meps/22/m022p239.pdf) diets.

I found one paper looking at [bluefish cannibalism on juveniles](https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1095-8649.1999.tb00734.x); but nothing else on consumption of juvenile bluefish by predators. There may be more info. We looked at bluefish diets for a previous benchmark assessment and did see some cannibalism; see Fig B5.7, p.522 of [this doc](https://repository.library.noaa.gov/view/noaa/4975)).

## Bluefish as predators




