---
title: "Density by stratum"
format: html
editor: visual
---

## VAST estimated density in each strata

Looks like mean density by stratum it should be in \`fit\$Report\$mean_D\_ctl\` in the fit output of each model. The currently loaded model is the bias corrected annual model.

Stealing code from the `FishStatsUtils` plotting functions at https://github.com/James-Thorson-NOAA/FishStatsUtils/blob/dev/R/plot_index.R

```{r}
# currently loaded model is the bias corrected annual
# can read in fit.rds from ~/Documents/0_Data/bluefishdiet/pyindex/allagg_annual_500_lennosst_ALLsplit_biascorrect

n_categories = dim(fit$Report$mean_D_ctl)[1]
n_years = dim(fit$Report$mean_D_ctl)[2]
n_strata = dim(fit$Report$mean_D_ctl)[3]

strata_names <- c("AllEPU", 
                  "MABGB", 
                  "MABGBstate", 
                  "MABGBfed", 
                  "MAB",
                  "GB",
                  "GOM",
                  "bfall",
                  "bfin",
                  "bfoff",
                  "MABGBalbinshore",
                  "MABGBothoffshore",
                  "allother")

year_labels <- fit$year_labels
years_to_plot <- fit$years_to_plot
category_names <- fit$category_names
plot_legend <- ifelse(n_strata>1, TRUE, FALSE)

# reference the data using fit$Report$mean_D_ctl[category, years_to_plot, stratum]
dens_strat1 <- fit$Report$mean_D_ctl[1,years_to_plot,1]

```

Huge density estimates in year 23 (2007) in any strata containing nearshore Long Island. The relevant comparison for this model is combined MABGB state and federal waters density for comparison with MRIP CPUE.

```{r}
plot(year_labels, fit$Report$mean_D_ctl[1,years_to_plot,4], ylim=c(0,0.5)) #fedwaters
lines(year_labels, fit$Report$mean_D_ctl[1,years_to_plot,3], ylim=c(0,0.5)) #statewaters

```

To my eye, state waters forage density was higher pre 1991, was even with federal waters forage density through about 2006, and has been mainly higher than federal waters density again since 2008.

AND the 2007 density estimate is due to a data error. Re running everything now...

It would be nice to get error bars on these.
