---
title: "Prey data and aggregation"
author: "Sarah Gaichas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_fold: hide
link-citations: yes
csl: ices-journal-of-marine-science.csl
bibliography: FishDiet_EcoIndicators.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

library(tidyverse)
library(here)
library(DT)
library(pdftools)
library(patchwork)
library(ggiraph)

library(ecodata)
library(VAST)
```

Use food habits data from Laurel's condition repository, object is called `allfh`

```{r}
load(url("https://github.com/Laurels1/Condition/raw/master/data/allfh.RData"))
```

Range of years in `allfh` :

`r unique(allfh$year)`

Following data prep in @ng_predator_2021. First collapsed to first and second half of year, combining winter and summer surveys with spring and fall to expand datasets. 

Want to compute the average mass of each prey category for combined predators per tow. Predator-specific covariates need to also be averaged by tow (size, Nspecies, evenness?).

First explore, how many predators per tow, how many stomachs each, how many prey in each predator?



The first aggregation was to season in 