---
title: "Prey data and aggregation"
author: "Sarah Gaichas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_fold: hide
link-citations: yes
csl: ices-journal-of-marine-science.csl
bibliography: FishDiet_EcoIndicators.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

library(tidyverse)
library(here)
library(DT)
library(pdftools)
library(patchwork)
library(ggiraph)

library(ecodata)
#library(VAST)
```

Use food habits data from Laurel's condition repository, object is called `allfh`

```{r}
load(url("https://github.com/Laurels1/Condition/raw/master/data/allfh.RData"))
```

Range of years in `allfh` :

`r unique(allfh$year)`

Following data prep in @ng_predator_2021. First collapsed to first and second half of year, combining winter and summer surveys with spring and fall to expand datasets. 

Want to compute the average mass of each prey category for combined predators per tow. Predator-specific covariates need to also be averaged by tow (size, Nspecies, evenness?).

First explore, how many predators per tow, how many stomachs each, how many prey in each predator? Filter to piscivores first. 

```{r}
# code for piscivore table
piscivores <- ecodata::species_groupings %>%
  select(COMNAME, SizeCat, Garrison.Link) %>%
  filter(!is.na(Garrison.Link),
         Garrison.Link == "Piscivores") %>%
  mutate(PiscGuild = case_when(COMNAME == "WINTER SKATE" ~ "c",
                               COMNAME == "WEAKFISH" ~ "b", 
                               COMNAME == "BLUEFISH" & SizeCat == "S" ~ "b",
                               TRUE ~ "a")) %>%
  distinct()

# same as Scott's?
guild_dat <- read.csv("fhdat/predator_guilds.csv", stringsAsFactors = FALSE)

pisc2 <- guild_dat %>%
  filter(guild %in% "piscivore")

# no, typo in Scott's BSB should not be a piscivore and bluefish S and M missing

rm(pisc2, guild_dat)

# food habits 1973-2020 piscivores only; include empties

fh.nefsc.pisc <- allfh %>%
  #filter(pynam != "EMPTY") %>%
  left_join(piscivores, by = c("pdcomnam" = "COMNAME",
                               "sizecat" = "SizeCat")) %>%
  filter(!is.na(Garrison.Link))

 preycount <- fh.nefsc.pisc %>%
   #group_by(year, season, pdcomnam, pynam) %>%
   group_by(pdcomnam, pynam) %>%
   summarise(count = n()) %>%
   #arrange(desc(count))
   pivot_wider(names_from = pdcomnam, values_from = count)

```

How many times in the full dataset was each prey name observed per predator?

```{r}
datatable(preycount, rownames = FALSE,
          extensions = c("FixedColumns"),
          #caption = "Prey observed in piscivores guild (Garrison and Link 2000) 1973-2020",
          options = list(pageLength = 25,
                         scrollX = TRUE,
                         fixedColumns = list(leftColumns = 1)))
```

Start by aggregating all pelagic nekton prey that have at least 10 observations for bluefish (leaving out empty, fish, osteichthes, AR, blown):

```{r}

gencomlist <- fh.nefsc.pisc %>%
  select(pynam, gencom2) %>%
  distinct()

blueprey <- preycount %>%
  filter(BLUEFISH > 9) %>%
  filter(!pynam %in% c("EMPTY", "BLOWN",
                       "FISH", "OSTEICHTHYES",
                       "ANIMAL REMAINS",
                       "FISH SCALES")) %>%
  #filter(!str_detect(pynam, "SHRIMP|CRAB")) %>%
  left_join(gencomlist) %>%
  filter(!gencom2 %in% c("ARTHROPODA", "ANNELIDA",
                         "CNIDARIA", "UROCHORDATA",
                         "ECHINODERMATA", "WORMS",
                         "BRACHIOPODA", "COMB JELLIES",
                         "BRYOZOA", "SPONGES",
                         "MISCELLANEOUS", "OTHER"))
```

```{r}
datatable(blueprey, rownames = FALSE,
          extensions = c("FixedColumns"),
          #caption = "Bluefish prey in all piscivores 1973-2020",
          options = list(pageLength = 25,
                         scrollX = TRUE,
                         fixedColumns = list(leftColumns = 1)))
```

This gives us 20 individual prey names. 

We should compare this list with NEAMAP bluefish prey to see if any are missing.

How many tows with piscivore diets had these preynames? 

```{r}
fh.nefsc.pisc.blueprey <- fh.nefsc.pisc %>%
  mutate(blueprey = case_when(pynam %in% blueprey$pynam ~ "blueprey",
                              TRUE ~ "othprey"))

preystn <- fh.nefsc.pisc.blueprey %>%
  group_by(year, season, station) %>%
  count(blueprey) %>%
  pivot_wider(names_from = blueprey, values_from = n) 

#dim(preystn)[1]

bluepreystn <- preystn %>% 
  arrange(desc(blueprey)) %>%
  filter(!is.na(blueprey))

#dim(bluepreystn)[1]

```

Between 1973 and 2020 we have `r dim(preystn)[1]` individual tows where piscivores were collected and `r dim(bluepreystn)[1]` of those tows had bluefish prey. Therefore, `r dim(bluepreystn)[1]/dim(preystn)[1]*100` percent of piscivore tows will be used to get the aggregate prey index. 

Which years and seasons have bluefish prey observed? How many tows each?

```{r}
# coverage <- bluepreystn %>%
#   ungroup() %>%
#   select(year, season) %>%
#   distinct() %>%
#   arrange(year, desc(season))

coverage <- bluepreystn %>%
  group_by(year, season) %>%
  count(station) %>%
  summarize(nstation = sum(n))

datatable(coverage, rownames = FALSE,
          #extensions = c("FixedColumns"),
          caption = "Piscivore stations with bluefish prey 1973-2020",
          options = list(pageLength = 10,
                         autoWidth = TRUE,
                         columnDefs = list(list(width = '200px'))
                         )
          )
```

(Note that the fall 2020 surveys were cancelled, and spring 2020 was partial due to pandemic restrictions.)

No year/season combinations have 0 stations with aggregated bluefish prey. Summarizing the number of stations per year/season with bluefish prey, 1973-2020:

```{r}
summary(coverage$nstation)
```

So we can aggregate over all these prey in all predator stomachs at a particular station to get mean bluefish prey weight per predator stomach. Calculate variance in prey weight too, n prey species, prey diversity index? The catchability covariates at each station could be number of predators, number of predator species, diversity/evenness of predator species, mean predator length, variance predator length. The habitat covariates at each station could be temperature, bottom depth?

```{r}

bluepyall_stn <- fh.nefsc.pisc.blueprey %>%
  #create id linking cruise6_station
  #create season_ng spring and fall Spring=Jan-May, Fall=June-Dec
  mutate(id = paste0(cruise6, "_", station),
         year = as.numeric(year),
         month = as.numeric(month),
         season_ng = case_when(month <= 5 ~ "SPRING",
                               month >= 6 ~ "FALL",
                               TRUE ~ as.character(NA))
         ) %>%
  select(year, season_ng, id, 
         pynam, pyamtw, pywgti, pyvoli, blueprey, 
         pdcomnam, pdid, PiscGuild, pdlen, pdsvol, pdswgt, 
         beglat, beglon, declat, declon, 
         bottemp, surftemp, setdepth) %>%
  group_by(id) %>%
  #mean blueprey g per stomach per tow: sum all blueprey g/n stomachs in tow
  mutate(bluepywt = case_when(blueprey == "blueprey" ~ pywgti,
                               TRUE ~ 0.0),
         bluepynam = case_when(blueprey == "blueprey" ~ pynam,
                               TRUE ~ NA_character_)) 

stndat <- bluepyall_stn %>%
  select(year, season_ng, id, 
         beglat, beglon, declat, declon, 
         bottemp, surftemp, setdepth) %>%
  distinct()

#pisc stomachs in tow count pdid for each pred and sum
piscstom <- bluepyall_stn %>%
  group_by(id, pdcomnam) %>%
  summarise(nstompd = n_distinct(pdid)) %>%
  group_by(id) %>%
  summarise(nstomtot = sum(nstompd))

#mean and var pred length per tow
pisclen <- bluepyall_stn %>%
  summarise(meanpisclen = mean(pdlen),
            varpisclen = var(pdlen))

bluepyagg_stn <- bluepyall_stn %>%
  summarise(sumbluepywt = sum(bluepywt),
            nbluepysp = n_distinct(bluepynam, na.rm = T),
            npreysp = n_distinct(pynam),
            npiscsp = n_distinct(pdcomnam)) %>%
  left_join(piscstom) %>%
  mutate(meanbluepywt = sumbluepywt/nstomtot) %>%
  left_join(pisclen) %>%
  left_join(stndat)
  
```

Some tests to ensure calcs look right, station data and summary:

```{r}
datatable(bluepyall_stn %>% filter(id=="197303_134"),
          options= list(pageLength = 25,
                         scrollX = TRUE))

datatable(bluepyagg_stn %>% filter(id=="197303_134"),
          options= list(pageLength = 25,
                         scrollX = TRUE))

datatable(bluepyall_stn %>% filter(id=="197303_140"),
          options= list(pageLength = 25,
                         scrollX = TRUE))

datatable(bluepyagg_stn %>% filter(id=="197303_140"),
          options= list(pageLength = 25,
                         scrollX = TRUE))
```


Then look at summary stats of prey per tow, predators per tow by season each year.

```{r}
sumstats <- bluepyagg_stn %>%
  group_by(year, season_ng) %>%
  summarise(nstn = n(),
            meanpreyn = mean(npreysp),
            meanbluepreyn = mean(nbluepysp),
            meanpiscn = mean(npiscsp),
            meanstomn = mean(nstomtot))

datatable(sumstats)
```

Save the input data for the initial aggregated prey index VAST:

```{r}

saveRDS(bluepyagg_stn, here("fhdat/bluepyagg_stn.rds"))
```

After the first run with all prey aggregated we can explore possible prey categories:  

+  Inshore fish (menhaden, bay anchovy, engraulidae?, sandlance, spot?)
+  Offshore fish (Atl herring/clupeidae, Atl mackerel/scomber, butterfish, hakes)
+  Inshore squid (Loligo)
+  Offshore squid (Illex)
+  Other (AR, misc, inverts other than squid) No, skip this.

Presence of family level categories (Cephalopoda, Engraulidae) makes habitat splitting difficult.
Do some dynamic mapping if engraulidae mostly with anchoa make inshore? 
If cephalapods with loligo make inshore; Illex offshore?
Circular though.