---
title: "Index By Region"
subtitle: "NEFSC and NEAMAP surveys, new predator list"
author: "Sarah Gaichas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_fold: hide
link-citations: yes
csl: ices-journal-of-marine-science.csl
bibliography: FishDiet_EcoIndicators.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(purrr)
library(ggplot2)
theme_set(theme_bw())

library(sf)
library(ecodata)
library(FishStatsUtils)
```

Now splitting the index into many parts.

Make a lookup table:

```{r}
# strata.limits <- as.list(c("AllEPU" = AllEPU, 
#                          "MABGB" = MABGB, 
#                          "MABGBinshore" = MABGBinshore, 
#                          "MABGBoffshore" = MABGBoffshore, 
#                          "bfall" = bfall,
#                          "bfallnot" = bfallnot,
#                          "bfin" = bfin,
#                          "bfinnot" = bfinnot,
#                          "bfoff" = bfoff,
#                          "bfoffnot" = bfoffnot,
#                          "MABGBalbinshore" = MABGBalbinshore,
#                          "MABGBoffshorebigin" = MABGBoffshorebigin))

stratlook <- data.frame(Stratum = c("Stratum_1",
                                      "Stratum_2",
                                      "Stratum_3",
                                      "Stratum_4",
                                      "Stratum_5",
                                      "Stratum_6",
                                      "Stratum_7",
                                      "Stratum_8",
                                      "Stratum_9",
                                      "Stratum_10",
                                      "Stratum_11",
                                      "Stratum_12"),
                           Region  = c("AllEPU", 
                                       "MABGB", 
                                       "MABGBinshore", 
                                       "MABGBoffshore", 
                                       "bfall",
                                       "bfallnot",
                                       "bfin",
                                       "bfinnot",
                                       "bfoff",
                                       "bfoffnot",
                                       "MABGBalbinshore",
                                       "MABGBoffshorebigin"))


```

## Fall

Plot individual time series

```{r}
splitoutput <- read.csv("pyindex/allagg_fall_500_lenno_split/Index.csv")

splitoutput <- splitoutput %>%
  left_join(stratlook)

ggplot(splitoutput, aes(x=Time, y=Estimate, colour=Region)) +
  geom_errorbar(aes(ymin=Estimate+Std..Error.for.Estimate, ymax=Estimate-Std..Error.for.Estimate))+
  geom_point()+
  geom_line()+
  facet_wrap(~Region, scales = "free_y") +
  guides(colour = guide_legend(ncol=2)) +
  #theme(legend.position = c(1, 0),
   #     legend.justification = c(1, 0))
  theme(legend.position="none")

```

 or just the indices from inshore (alb), inshore bluefish, offshore bluefish, and further out
 
```{r}
in2off <- splitoutput %>%
  dplyr::select(Time, Region, Estimate) %>%
  tidyr::pivot_wider(names_from = Region, values_from = Estimate) %>%
  dplyr::mutate(AlbInshore = MABGBalbinshore,
                BlueInshore = bfin,
                BlueOffshore = bfoff,
                OthOffshore = MABGB - (bfoff + bfin + MABGBalbinshore),
                SumMABGB = AlbInshore + BlueInshore + BlueOffshore + OthOffshore) %>%
  dplyr::select(Time, AlbInshore, BlueInshore, BlueOffshore, OthOffshore, SumMABGB, MABGB) %>%
  tidyr::pivot_longer(!Time, names_to = "Region", values_to = "Estimate")

ggplot(in2off, aes(x=Time, y=Estimate, colour = Region)) +
  geom_point()+
  geom_line()+
  #facet_wrap(~Region) + #+ , scales = "free_y"
  #theme(legend.position = c(1, 0),
  #      legend.justification = c(1, 0))
  ggtitle("Fall Prey Index, Mid-Atlantic and Georges Bank")


```
 
 
 or as proportions (here proportion of MABGB index).

```{r}
MABGBprop <- in2off %>%
  #dplyr::filter(Region != "AllEPU") %>%
  dplyr::select(Time, Region, Estimate) %>%
  tidyr::pivot_wider(names_from = Region, values_from = Estimate) %>%
  dplyr::mutate(AlbInshoreprop = AlbInshore/MABGB,
                BlueInshoreprop = BlueInshore/MABGB,
                BlueOffshoreprop = BlueOffshore/MABGB,
                OthOffshoreprop = OthOffshore/MABGB) %>%
  tidyr::pivot_longer(!Time, names_to = "Region", values_to = "Estimate") %>%
  dplyr::filter(Region %in% c("AlbInshoreprop", "BlueInshoreprop", "BlueOffshoreprop",
                              "OthOffshoreprop"))
  

ggplot(MABGBprop, aes(x=Time, y=Estimate, colour = Region)) +
  geom_point()+
  geom_line()+
  #facet_wrap(~Region) + #+ , scales = "free_y"
  #theme(legend.position = c(1, 0),
  #      legend.justification = c(1, 0))
  ggtitle("Fall Prey Index as proportion of Mid-Atlantic and Georges Bank")
  
  
```
## Spring

Plot individual time series

```{r}
splitoutput <- read.csv("pyindex/allagg_spring_500_lenno_split/Index.csv")

splitoutput <- splitoutput %>%
  left_join(stratlook)

ggplot(splitoutput, aes(x=Time, y=Estimate, colour=Region)) +
  geom_errorbar(aes(ymin=Estimate+Std..Error.for.Estimate, ymax=Estimate-Std..Error.for.Estimate))+
  geom_point()+
  geom_line()+
  facet_wrap(~Region, scales = "free_y") +
  guides(colour = guide_legend(ncol=2)) +
  #theme(legend.position = c(1, 0),
   #     legend.justification = c(1, 0))
  theme(legend.position="none")

```

 or just the indices from inshore (alb), inshore bluefish, offshore bluefish, and further out
 
```{r}
in2off <- splitoutput %>%
  dplyr::select(Time, Region, Estimate) %>%
  tidyr::pivot_wider(names_from = Region, values_from = Estimate) %>%
  dplyr::mutate(AlbInshore = MABGBalbinshore,
                BlueInshore = bfin,
                BlueOffshore = bfoff,
                OthOffshore = MABGB - (bfoff + bfin + MABGBalbinshore),
                SumMABGB = AlbInshore + BlueInshore + BlueOffshore + OthOffshore) %>%
  dplyr::select(Time, AlbInshore, BlueInshore, BlueOffshore, OthOffshore, SumMABGB, MABGB) %>%
  tidyr::pivot_longer(!Time, names_to = "Region", values_to = "Estimate")

ggplot(in2off, aes(x=Time, y=Estimate, colour = Region)) +
  geom_point()+
  geom_line()+
  #facet_wrap(~Region) + #+ , scales = "free_y"
  #theme(legend.position = c(1, 0),
  #      legend.justification = c(1, 0))
  ggtitle("Spring Prey Index, Mid-Atlantic and Georges Bank")


```

 or as proportions (here proportion of MABGB index).

```{r}
MABGBprop <- in2off %>%
  #dplyr::filter(Region != "AllEPU") %>%
  dplyr::select(Time, Region, Estimate) %>%
  tidyr::pivot_wider(names_from = Region, values_from = Estimate) %>%
  dplyr::mutate(AlbInshoreprop = AlbInshore/MABGB,
                BlueInshoreprop = BlueInshore/MABGB,
                BlueOffshoreprop = BlueOffshore/MABGB,
                OthOffshoreprop = OthOffshore/MABGB) %>%
  tidyr::pivot_longer(!Time, names_to = "Region", values_to = "Estimate") %>%
  dplyr::filter(Region %in% c("AlbInshoreprop", "BlueInshoreprop", "BlueOffshoreprop",
                              "OthOffshoreprop"))
  

ggplot(MABGBprop, aes(x=Time, y=Estimate, colour = Region)) +
  geom_point()+
  geom_line()+
  #facet_wrap(~Region) + #+ , scales = "free_y"
  #theme(legend.position = c(1, 0),
  #      legend.justification = c(1, 0))
  ggtitle("Spring Prey Index as proportion of Mid-Atlantic and Georges Bank")
  
  
```

