---
title: "Updated VAST Input Data"
author: "Sarah Gaichas, Jim Gartland, Brian Smith, Bluefish WG"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_fold: hide
link-citations: yes
csl: ices-journal-of-marine-science.csl
bibliography: FishDiet_EcoIndicators.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

library(tidyverse)
library(here)
library(DT)

```


## Update Input Data

Working group decision after the February 2022 Data Meeting was to update the predator list based on the most recent diet similarity matrix by Smith posted on the [NEFSC shiny app](https://fwdp.shinyapps.io/tm2020/#4_DIET_OVERLAP_AND_TROPHIC_GUILDS), which results in a new Piscivore guild relative to our initial models based on @garrison_dietary_2000. 

We investigated alternative cluster algorithms [here](https://sgaichas.github.io/bluefishdiet/PreySimilarityUpdate.html). 

Input NEFSC food habits overlap matrix:
```{r}
dietoverlap <- read_csv(here("datfromshiny/tgmat.2022-02-15.csv"))
```

Get NEFSC food habits data (as of October 8 2022 contains only 1973-2020 data, check years):
```{r}
# object is called `allfh`
load(url("https://github.com/Laurels1/Condition/raw/master/data/allfh.RData"))

# as of October 8 2022 contains only 1973-2020 data
unique(allfh$year)
```

Load 2021 NEFSC food habits data (October 8 2022, check years):

```{r}
#object is called allfh21
load(here("fhdat/allfh21.Rdata"))

# check years
unique(allfh21$year)
```

Make new NEFSC dataset 1973-2021: 

```{r}
allfh <- allfh %>%
  dplyr::bind_rows(allfh21)
```


Generate the Piscivore list based on clustering with the "complete" algorithm. Identify which species cluster with all 3 sizes of bluefish:
```{r, fig.height=12}
# follows example here https://cran.r-project.org/web/packages/dendextend/vignettes/Cluster_Analysis.html

library(dendextend)

d_dietoverlap <- dist(dietoverlap)

guilds <- hclust(d_dietoverlap)

#plot(guilds)

dend <- as.dendrogram(guilds)

dend <- rotate(dend, 1:136)

dend <- color_branches(dend, k=6) # Brian uses 6 categories

labels(dend) <- paste(as.character(names(dietoverlap[-1]))[order.dendrogram(dend)],
                           "(",labels(dend),")", 
                           sep = "")

dend <- hang.dendrogram(dend,hang_height=0.1)

# reduce the size of the labels:
# dend <- assign_values_to_leaves_nodePar(dend, 0.5, "lab.cex")
dend <- set(dend, "labels_cex", 0.5)
# And plot:
par(mar = c(3,3,3,7))
plot(dend, 
     main = "Clustered NEFSC diet data, (complete)
     (the labels give the predator species/size)", 
     horiz =  TRUE,  nodePar = list(cex = .007))
#legend("topleft", legend = iris_species, fill = rainbow_hcl(3))

```

This is the list of predators and sizes:
```{r}
# list of species in node with all three bluefish sizes
pisccomplete <- partition_leaves(dend)[[
  which_node(dend, c("Bluefish..S(37)", "Bluefish..M(36)", "Bluefish..L(35)"))
]]

pisccomplete
```

### Create the NEFSC input dataset.

First filter to the predators and identify the bluefish prey:  
```{r}
pisccompletedf <- data.frame("COMNAME" = toupper(str_remove(pisccomplete, "\\..*")),
                              "SizeCat" = str_remove(str_extract(pisccomplete, "\\..*[:upper:]+"), "\\.."),
                              "feedguild" = "pisccomplete")
 
 fh.nefsc.pisc.pisccomplete <- allfh %>%
  #filter(pynam != "EMPTY") %>%
  left_join(pisccompletedf, by = c("pdcomnam" = "COMNAME",
                               "sizecat" = "SizeCat")) %>%
  filter(!is.na(feedguild))
 
preycount  <- fh.nefsc.pisc.pisccomplete %>%
   #group_by(year, season, pdcomnam, pynam) %>%
   group_by(pdcomnam, pynam) %>%
   summarise(count = n()) %>%
   #arrange(desc(count))
   pivot_wider(names_from = pdcomnam, values_from = count)

 
gencomlist <- allfh %>%
  select(pynam, gencom2) %>%
  distinct()

blueprey <- preycount %>% 
  filter(BLUEFISH > 9) %>%
  filter(!pynam %in% c("EMPTY", "BLOWN",
                       "FISH", "OSTEICHTHYES",
                       "ANIMAL REMAINS",
                       "FISH SCALES")) %>%
  #filter(!str_detect(pynam, "SHRIMP|CRAB")) %>%
  left_join(gencomlist) %>%
  filter(!gencom2 %in% c("ARTHROPODA", "ANNELIDA",
                         "CNIDARIA", "UROCHORDATA",
                         "ECHINODERMATA", "WORMS",
                         "BRACHIOPODA", "COMB JELLIES",
                         "BRYOZOA", "SPONGES",
                         "MISCELLANEOUS", "OTHER"))

fh.nefsc.pisc.pisccomplete.blueprey <- fh.nefsc.pisc.pisccomplete %>%
  mutate(blueprey = case_when(pynam %in% blueprey$pynam ~ "blueprey",
                              TRUE ~ "othprey"))

preystn.pisccomplete <- fh.nefsc.pisc.pisccomplete.blueprey %>%
  group_by(year, season, station) %>%
  count(blueprey) %>%
  pivot_wider(names_from = blueprey, values_from = n) %>%
  filter(year>1984)

#dim(preystn)[1]

bluepreystn.pisccomplete <- preystn.pisccomplete %>% 
  arrange(desc(blueprey)) %>%
  filter(!is.na(blueprey))

#dim(bluepreystn)[1]

```

Assign station id, change the months for spring and fall to align with the assessment, and calculate mean bluefish prey per station in NEFSC:  
```{r}
bluepyall_stn <- fh.nefsc.pisc.pisccomplete.blueprey %>%
  #create id linking cruise6_station
  #create season_ng spring and fall Spring=Jan-May, Fall=June-Dec
  mutate(id = paste0(cruise6, "_", station),
         year = as.numeric(year),
         month = as.numeric(month),
         season_ng = case_when(month <= 6 ~ "SPRING",
                               month >= 7 ~ "FALL",
                               TRUE ~ as.character(NA))
         ) %>%
  select(year, season_ng, id, stratum,
         pynam, pyamtw, pywgti, pyvoli, blueprey, 
         pdcomnam, pdid, pdlen, pdsvol, pdswgt, 
         beglat, beglon, declat, declon, 
         bottemp, surftemp, setdepth) %>%
  group_by(id) %>%
  #mean blueprey g per stomach per tow: sum all blueprey g/n stomachs in tow
  mutate(bluepywt = case_when(blueprey == "blueprey" ~ pyamtw,
                               TRUE ~ 0.0),
         bluepynam = case_when(blueprey == "blueprey" ~ pynam,
                               TRUE ~ NA_character_)) 

# save at prey disaggregated stage for paper
saveRDS(bluepyall_stn, here("fhdat/bluepyall_stn.rds"))

stndat <- bluepyall_stn %>%
  select(year, season_ng, id, 
         beglat, beglon, declat, declon, 
         bottemp, surftemp, setdepth) %>%
  distinct()

#pisc stomachs in tow count pdid for each pred and sum
piscstom <- bluepyall_stn %>%
  group_by(id, pdcomnam) %>%
  summarise(nstompd = n_distinct(pdid)) %>%
  group_by(id) %>%
  summarise(nstomtot = sum(nstompd))

#mean and var pred length per tow
pisclen <- bluepyall_stn %>%
  summarise(meanpisclen = mean(pdlen),
            varpisclen = var(pdlen))

bluepyagg_stn <- bluepyall_stn %>%
  summarise(sumbluepywt = sum(bluepywt),
            nbluepysp = n_distinct(bluepynam, na.rm = T),
            npreysp = n_distinct(pynam),
            npiscsp = n_distinct(pdcomnam)) %>%
  left_join(piscstom) %>%
  mutate(meanbluepywt = sumbluepywt/nstomtot) %>%
  left_join(pisclen) %>%
  left_join(stndat)

# save at same stage as before, writing over old file
saveRDS(bluepyagg_stn, here("fhdat/bluepyagg_stn.rds"))

# current dataset, fix declon, add vessel
nefsc_bluepyagg_stn <- readRDS(here("fhdat/bluepyagg_stn.rds")) %>%
  mutate(declon = -declon,
         vessel = case_when(year<2009 ~ "AL",
                            year>=2009 ~ "HB", 
                            TRUE ~ as.character(NA)))


```

### Combine with NEAMAP

NEAMAP inputs were similarly updated based on this predator size category list. NEAMAP includes the following predators, adding two not captured by the NEFSC survey offshore and leaving out those from NEFSC not captured inshore:

+  Summer Flounder 21-70 cm
+  Silver Hake 21-76 cm
+  Weakfish 26-50 cm
+  Atlantic Cod 81-150 cm (we actually had some!)
+  Bluefish 3 – 118 cm
+  Striped Bass 31 – 120 cm
+  Spanish Mackerel 10 – 33.5 cm (everything we had)
+  Spotted Sea Trout 15.5 – 34 cm (again, everything we had)
+  Spiny Dogfish 36 – 117 cm
+  Goosefish 5 – 124 cm


Read in new inputs, align columns, merge datasets, correct single station with wrong data in original dataset, and save:  
```{r}
neamap_bluepreyagg_stn <- read_csv(here("fhdat/NEAMAP_Mean stomach weights_Bluefish PreyWQ2.csv")) %>%
  mutate(vessel = "NEAMAP") %>%
  rename(id = station,
         sumbluepywt = sumbluepreywt,
         nbluepysp = nbfpreyspp,
         #npreysp = ,
         npiscsp = npiscspp,
         nstomtot = nstomtot, 
         meanbluepywt = meanbluepreywt,
         meanpisclen = meanpisclen.simple, 
         #varpisclen = ,
         season_ng = season,
         declat  = lat,
         declon = lon,
         bottemp = bWT,
         #surftemp = , 
         setdepth = depthm) 

  
# combine  
bluepyagg_stn <-  nefsc_bluepyagg_stn %>%
  bind_rows(neamap_bluepreyagg_stn) 

# check for incorrect NEAMAP station
bluepyagg_stn %>% filter(id == "NM20070901011") # has this station
# if sumbluepywt is 106564.2, this is incorrect
# corrected by Jim Gartland in September 2022

# correct single NEAMAP station 
bluepyagg_stn$sumbluepywt[bluepyagg_stn$id == "NM20070901011"] <- 4.8404
bluepyagg_stn$meanbluepywt[bluepyagg_stn$id == "NM20070901011"] <- 0.186169231


saveRDS(bluepyagg_stn, here("fhdat/bluepyagg_stn_all.rds"))
```

## References