---
title: "VAST take 1"
author: "Sarah Gaichas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_fold: hide
link-citations: yes
csl: ices-journal-of-marine-science.csl
bibliography: FishDiet_EcoIndicators.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

library(tidyverse)
library(here)
#library(DT)
#library(pdftools)
#library(patchwork)
#library(ggiraph)

#library(ecodata)
library(VAST)
```

Having built an initial dataset of haul-specific mean bluefish prey weight per stomach for piscivores, now we'll try to get a forage biomass index using VAST.

The approach here is to use exactly what @ng_predator_2021 for herring, but combining all bluefish prey (defined [here](https://sgaichas.github.io/bluefishdiet/PreyAggs.html)) as sampled by all piscivore predators at each station.

In @ng_predator_2021, seasons were modeled separately, so we will start that way as well. They used 100 knots, estimated by k-means clustering of the data, to define the spatial dimensions of each seasonal model. They used a a Poisson-link delta model to estimate expected prey mass per predator stomach.  

Read in data, separate spring and fall, and rename columns for VAST:

```{r, eval=FALSE}
bluepyagg_stn <- readRDS(here("fhdat/bluepyagg_stn.rds"))

bluepyagg_stn_fall <- bluepyagg_stn %>%
  ungroup() %>%
  filter(season_ng == "FALL") %>%
  mutate(Vessel = "NEFSC",
         AreaSwept_km2 = 0.0384) %>%
  select(Catch_g = meanbluepywt,
         Year = year,
         Vessel,
         AreaSwept_km2,
         Lat = declat,
         Lon = declon) %>%
  as.data.frame()

bluepyagg_stn_spring <- bluepyagg_stn %>%
  filter(season_ng == "SPRING")%>%
  mutate(Vessel = "NEFSC",
         AreaSwept_km2 = 0.0384) %>%
  select(Catch_g = meanbluepywt,
         Year = year,
         Vessel,
         AreaSwept_km2,
         Lat = declat,
         Lon = declon)%>%
  as.data.frame()
```

Try the simplest possible index standardization model, fall (run from script `VASTunivariate_bluefishprey.R`, *not* in rmd):

```{r, code = readLines(here("VASTunivariate_bluefishprey.R")), eval=F}
```

R console output of full script (TMB Warning gone after updating Matrix package to current; no longer advised to update TMB so I'm leaving it alone).

In the initial run, we bomb when parameters hit bounds (clipped output below)
```
Loading required package: TMB
###########################################################################################
Loading package VAST version 3.8.2
For information and examples, please see http://github.com/james-thorson/VAST/
###########################################################################################
Loading package `FishStatsUtils` version 2.10.2
Loading required package: units
udunits database from /Library/Frameworks/R.framework/Versions/4.0/Resources/library/units/share/udunits/udunits2.xml

[...code in script...]

[...skipping to the end...]



### Making data object
Coercing `b_i` to have units `kg`; I recommend using explicit units, e.g., `as_units(b_i,'kg')`, `as_units(b_i,'count') or `as_units(b_i,unitless)`
Coercing `a_i` to have units `km^2`; I recommend using explicit units, e.g., `as_units(a_i,'km^2')` or `as_units(a_i,unitless)`
FieldConfig_input is:
             Component_1 Component_2
Omega                 -2          -2
Epsilon               -2          -2
Beta                  -2          -2
Epsilon_time          -3          -3
OverdispersionConfig_input is:
Eta1 Eta2 
  -1   -1 
Calculating range shift for stratum #1:

### Making TMB object
Note: Using Makevars in /Users/sarah.gaichas/.R/Makevars 
make: Nothing to be done for `all'.
Constructing atomic logspace_sub
Constructing atomic D_lgamma
Constructing atomic D_incpl_gamma_shape
Constructing atomic logspace_sub
Constructing atomic D_lgamma
Constructing atomic D_incpl_gamma_shape
List of estimated fixed and random effects:
    Coefficient_name Number_of_coefficients   Type
1           beta1_ft                     21  Fixed
2           beta2_ft                     21  Fixed
3       L_epsilon1_z                      1  Fixed
4       L_epsilon2_z                      1  Fixed
5         L_omega1_z                      1  Fixed
6         L_omega2_z                      1  Fixed
7         ln_H_input                      2  Fixed
8          logkappa1                      1  Fixed
9          logkappa2                      1  Fixed
10         logSigmaM                      1  Fixed
11 Epsiloninput1_sff                   6627 Random
12 Epsiloninput2_sff                   6627 Random
13    Omegainput1_sf                    141 Random
14    Omegainput2_sf                    141 Random

### Testing model at initial values
No problem detected: All fixed effects have a nonzero gradient

### Estimating parameters
Note that `getReportCovariance=FALSE` causes an error in `TMB::sdreport` when no ADREPORTed variables are present
  0:     3407.4426:  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  1.00000  1.00000 -2.71885  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  1.00000  1.00000 -2.71885  1.60944
  1:     2988.5057: 0.000768207 0.000577006 0.0287776 0.0279307 0.0169915 0.0530422 0.0708692 0.165965 0.329559 0.127660 -0.0176126 -0.00226152 -0.0169023 -0.0135198 -0.0138058 -0.0199080 -0.0209304 -0.0255203 -0.0196997 -0.0146035 -0.0200739 -0.0270282 -0.0250568  1.16823  1.07727 -2.96382 0.0490667 0.0242394 0.00565546 0.0463988 0.0419860 0.125744 0.308510 0.0446797 1.00017e-05 0.00235638 0.00297993 0.0127676 0.00436147 0.000628474 -6.59582e-05 0.000247511 -0.000110302 0.00151567 -0.000209251 -0.000172832 -0.000106104  1.34391  1.09188 -3.15321  1.05881
[clipped!]
  3:     2120.9336:  3.74033  5.00000  1.60078  1.80387  1.48409  2.32322  2.25007  2.26809  2.88404  2.43985 -0.756209 0.108572 -0.945033 -0.618733 -0.621652 -1.94459 -1.98219 -2.16495 -1.07546 -0.681230 -1.37603 -1.63556 -2.15642 -0.435066 2.22260e-05 -5.10642  2.11197  1.28940 0.481313  1.44014  1.65877  1.66037  1.68343 0.829616 -1.75029 -0.221611 0.535181  2.00696  1.01644 0.656818 -2.34267 0.943145 -1.48131 -0.00953320 -5.14626 -3.12832 -5.51046  1.10880 1.44275e-06 -6.35962 0.437069

  [after 107 + 3 more iterations]
  
Check bounds for the following parameters:
        Param starting_value     Lower       MLE     Upper final_gradient
2  ln_H_input      0.0000000 -5.000000  5.000000  5.000000    -0.06354718
50  logkappa2     -0.1053605 -6.359621 -6.359621 -2.718847     0.42225521

The following parameters appear to be approaching zero:
          Param starting_value Lower          MLE Upper final_gradient
25 L_epsilon1_z              1  -Inf 2.222603e-05   Inf   0.0002381819
49 L_epsilon2_z              1  -Inf 1.442753e-06   Inf   0.0001268970
Please turn off factor-model variance parameters `L_` that are approaching zero and re-run the model


Error: Please change model structure to avoid problems with parameter estimates and then re-try; see details in `?check_fit`
In addition: Warning messages:
1: In sparseMatrix(i = index.i, j = index.j, x = Aij, dims = c(mesh$n,  :
  'giveCsparse' has been deprecated; setting 'repr = "T"' for you
2: In sparseMatrix(i = index.i, j = index.j, x = Aij, dims = c(mesh$n,  :
  'giveCsparse' has been deprecated; setting 'repr = "T"' for you
3: In sparseMatrix(i = index.i, j = index.j, x = Aij, dims = c(mesh$n,  :
  'giveCsparse' has been deprecated; setting 'repr = "T"' for you

```

Another run corrected units and increased the knots to 1000 but the results are basically the same:

```
Check bounds for the following parameters:
        Param starting_value     Lower       MLE     Upper final_gradient
2  ln_H_input      0.0000000 -5.000000  5.000000  5.000000    -0.06422987
50  logkappa2     -0.1053605 -6.397277 -6.397277 -1.112772     0.40923276

The following parameters appear to be approaching zero:
          Param starting_value Lower           MLE Upper final_gradient
25 L_epsilon1_z              1  -Inf  7.461783e-05   Inf   0.0008391968
49 L_epsilon2_z              1  -Inf -2.667453e-06   Inf  -0.0002574581
Please turn off factor-model variance parameters `L_` that are approaching zero and re-run the model
```


Corrections to the initial run included turning off anistopy and epsilon parameters.
This still resulted in logkappa1 hitting the upper bound. I increased knots several times.
Some variant had me turn off the omegas as well, which allowed the model to finish and plot output, but the output is very dumb. Plots are in the allagg_fall folder.

In the latest run corresponding to the script above, logkappa1 still hits a bound even with 1000 knots and one of the epsilons is still approaching 0:

```
### Writing output from `fit_model` in directory: /Users/sarah.gaichas/Documents/0_Data/bluefishdiet/pyindex/allagg_fall//

### Making extrapolation-grid
Using strata 1:100000
For the UTM conversion, automatically detected zone 19.
# Reducing extrapolation-grid from 31311 to 10000 cells for Region(s): northwest_atlantic
Loaded from /Users/sarah.gaichas/Documents/0_Data/bluefishdiet/pyindex/allagg_fall///Kmeans_extrapolation-10000.RData

### Making spatial information
Loaded from /Users/sarah.gaichas/Documents/0_Data/bluefishdiet/pyindex/allagg_fall///Kmeans_knots-1000.RData

### Making data object
Coercing `b_i` to have units `kg`; I recommend using explicit units, e.g., `as_units(b_i,'kg')`, `as_units(b_i,'count') or `as_units(b_i,unitless)`
Coercing `a_i` to have units `km^2`; I recommend using explicit units, e.g., `as_units(a_i,'km^2')` or `as_units(a_i,unitless)`
FieldConfig_input is:
             Component_1 Component_2
Omega                 -2          -2
Epsilon               -2          -2
Beta                  -2          -2
Epsilon_time          -3          -3
OverdispersionConfig_input is:
Eta1 Eta2 
  -1   -1 
Calculating range shift for stratum #1:

### Making TMB object
Note: Using Makevars in /Users/sarah.gaichas/.R/Makevars 
make: Nothing to be done for `all'.
Constructing atomic logspace_sub
Constructing atomic D_lgamma
Constructing atomic D_incpl_gamma_shape
Constructing atomic logspace_sub
Constructing atomic D_lgamma
Constructing atomic D_incpl_gamma_shape
List of estimated fixed and random effects:
    Coefficient_name Number_of_coefficients   Type
1           beta1_ft                     21  Fixed
2           beta2_ft                     21  Fixed
3       L_epsilon1_z                      1  Fixed
4       L_epsilon2_z                      1  Fixed
5         L_omega1_z                      1  Fixed
6         L_omega2_z                      1  Fixed
7          logkappa1                      1  Fixed
8          logkappa2                      1  Fixed
9          logSigmaM                      1  Fixed
10 Epsiloninput1_sff                  48927 Random
11 Epsiloninput2_sff                  48927 Random
12    Omegainput1_sf                   1041 Random
13    Omegainput2_sf                   1041 Random

### Testing model at initial values
No problem detected: All fixed effects have a nonzero gradient

### Estimating parameters
Note that `getReportCovariance=FALSE` causes an error in `TMB::sdreport` when no ADREPORTed variables are present
  0:     3608.5964:  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  1.00000  1.00000 -1.11277  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  1.00000  1.00000 -1.11277  1.60944
  1:     3606.5027: 0.0298858 0.0282088 0.0178513 0.0526752 0.0706111 0.166521 0.325127 0.126229 -0.0102282 0.00395157 -0.0107211 -0.00742165 -0.00748834 -0.0142419 -0.0152455 -0.0184490 -0.0133931 -0.00854901 -0.0135556 -0.0192200 -0.0180578  1.00969  1.00323 -1.12569 0.0782274 0.0387443 0.00937083 0.0807723 0.0655116 0.215387 0.618908 0.0756272 0.000349619 0.00442799 0.00540485 0.0203244 0.00729302 0.000919746 -3.34898e-05 0.000262139 -3.03321e-05 0.00272187 -0.000194337 -0.000137666 -9.98810e-05  1.05433  1.01669 -1.18378  2.22251
  2:     3256.1372: 0.0697148 0.0662425 0.0420960 0.123616 0.166053 0.389382 0.756682 0.296899 -0.0240576 0.00924851 -0.0252903 -0.0176942 -0.0177067 -0.0335466 -0.0358873 -0.0433844 -0.0314915 -0.0201465 -0.0318976 -0.0451417 -0.0424661  1.02248  1.00747 -1.14280 0.139489 0.0694397 0.0168658 0.144047 0.116957 0.377588  1.04445 0.134850 0.000634336 0.00798194 0.00974350 0.0365253 0.0131352 0.00165588 -5.94884e-05 0.000470608 -5.30786e-05 0.00490704 -0.000348568 -0.000246449 -0.000179179  1.08700  1.02646 -1.22635  1.46264
  3:     3026.8243: 0.182613 0.172867 0.109314 0.322945 0.431082 0.995872  1.91177 0.764901 -0.0611649 0.0236295 -0.0642425 -0.0443741 -0.0448935 -0.0856227 -0.0915218 -0.110202 -0.0799921 -0.0512227 -0.0812788 -0.114213 -0.107936  1.05971  1.01931 -1.19280 0.482576 0.251852 0.0634209 0.495284 0.409470  1.10673  2.09063 0.463504 0.00239131 0.0301663 0.0368465 0.135828 0.0495939 0.00632377 -0.000232375 0.00180743 -0.000210544 0.0186229 -0.00133994 -0.000949950 -0.000688621  1.24907  1.05278 -1.42951  1.76460
  4:     2728.0616: 0.456195 0.434492 0.274612 0.811411  1.06869  2.26903  3.86728  1.84016 -0.145213 0.0563444 -0.153302 -0.105097 -0.107108 -0.206181 -0.219674 -0.261547 -0.189578 -0.122128 -0.194436 -0.267785 -0.256555  1.13553  1.04004 -1.29544  1.32968 0.740129 0.197485  1.35594  1.14469  2.56297  3.61413  1.26559 0.00762348 0.0949847 0.116030 0.414603 0.155470 0.0201203 -0.000737811 0.00575687 -0.000661807 0.0589642 -0.00426545 -0.00302142 -0.00219225  1.60097  1.10153 -1.87639 0.318046
  5:     2300.8484: 0.811366 0.781367 0.493187  1.44559  1.88826  3.44164  3.32804  3.10370 -0.248684 0.100631 -0.262496 -0.175821 -0.181611 -0.357209 -0.380437 -0.450208 -0.325458 -0.208765 -0.335723 -0.458053 -0.442149  1.20525  1.08406 -1.41679  2.39226  1.60072 0.528065  2.33254  2.11867  3.17726  3.50689  2.07330 0.0136603 0.252801 0.317025  1.04689 0.431138 0.0649124 -0.00433541 0.0223891 -0.00558607 0.166670 -0.0170364 -0.0131303 -0.00869316  2.95140  1.22172 -4.13654 0.684452
  6:     2228.5886: 0.992416 0.965602 0.616179  1.76281  2.22411  2.13292  2.91114  2.89037 -0.299132 0.124617 -0.318498 -0.213530 -0.219137 -0.436780 -0.464634 -0.547232 -0.393488 -0.251831 -0.408192 -0.553386 -0.537893  1.28507  1.12576 -1.55370  2.73301  1.83828 0.629671  2.63081  2.43757  3.51925  3.85071  2.28729 0.00851116 0.295506 0.378250  1.23924 0.529698 0.0842309 -0.00753439 0.0428279 -0.00993048 0.202983 -0.0258499 -0.0207127 -0.0131428  3.27482  1.34716 -4.80026 0.181707
  7:     2185.7719: 0.998600 0.972614 0.621386  1.77244  2.22746  2.14629  2.91357  2.86669 -0.300983 0.125249 -0.320651 -0.215075 -0.220598 -0.439935 -0.467934 -0.550872 -0.395968 -0.253449 -0.410980 -0.556778 -0.541522  1.28517  1.12591 -1.55400  2.73420  1.83854 0.632285  2.62785  2.44022  3.51512  3.84140  2.28527 0.00739911 0.296382 0.379876  1.24345 0.533456 0.0855593 -0.00800645 0.0451171 -0.0105513 0.204391 -0.0272032 -0.0218728 -0.0138250  3.27528  1.36578 -4.82403 0.543239
  8:     2171.7516:  1.06251  1.04515 0.674823  1.87361  2.26326  2.23353  2.96261  2.63318 -0.320104 0.131832 -0.343001 -0.231245 -0.235889 -0.472630 -0.502058 -0.588682 -0.421654 -0.270265 -0.439763 -0.591951 -0.579087  1.28841  1.12808 -1.56027  2.74840  1.84463 0.651511  2.61545  2.46183  3.49925  3.79879  2.27099 0.000497563 0.303011 0.391928  1.27368 0.560511 0.0947814 -0.0108372 0.0609156 -0.0142094 0.214924 -0.0351208 -0.0287175 -0.0178124  3.27000  1.45745 -4.93669 0.454072
  9:     2167.1560:  1.16683  1.16791 0.768876  2.02567  2.29432  2.33759  2.92242  2.59767 -0.352873 0.142162 -0.381831 -0.259432 -0.262515 -0.530245 -0.562005 -0.654701 -0.465866 -0.299288 -0.489947 -0.652501 -0.644677  1.29146  1.12842 -1.56444  2.75644  1.84017 0.676712  2.58002  2.48194  3.46773  3.73503  2.25262 -0.0118014 0.311253 0.408973  1.31399 0.599267 0.109791 -0.0160662 0.0867267 -0.0209727 0.230163 -0.0504100 -0.0417445 -0.0255221  3.24377  1.53658 -5.01537 0.381454
 10:     2158.0470:  1.38157  1.42917 0.978403  2.30692  2.34881  2.32502  3.06471  2.42922 -0.424081 0.163950 -0.467342 -0.320918 -0.320751 -0.659530 -0.696245 -0.801884 -0.562852 -0.362642 -0.601335 -0.785825 -0.790892  1.29894  1.13062 -1.57627  2.77772  1.83559 0.733330  2.50606  2.53118  3.38415  3.57022  2.21746 -0.0386904 0.330306 0.448758  1.40811 0.684602 0.143460 -0.0282066 0.142785 -0.0361287 0.263913 -0.0875245 -0.0726796 -0.0442853  3.20639  1.61702 -5.11272 0.476795
 11:     2151.9623:  1.54225  1.66754  1.22576  2.34515  2.31613  2.35713  2.88229  2.46985 -0.504701 0.184542 -0.569527 -0.391866 -0.388121 -0.825608 -0.867657 -0.987331 -0.677155 -0.435331 -0.738772 -0.946563 -0.975195  1.31281  1.13322 -1.59596  2.79868  1.79950 0.790976  2.40628  2.58550  3.39250  3.58383  2.19203 -0.0764204 0.348503 0.495055  1.50984 0.783965 0.188879 -0.0462697 0.218943 -0.0576079 0.303853 -0.145784 -0.119995 -0.0738277  3.08865  1.53877 -4.88217 0.459894
 12:     2151.6427:  1.54286  1.66886  1.22833  2.34564  2.31678  2.35686  2.89136  2.47261 -0.505701 0.184671 -0.570863 -0.392744 -0.388961 -0.827992 -0.870107 -0.989943 -0.678633 -0.436236 -0.740654 -0.948709 -0.977797  1.31307  1.13326 -1.59634  2.79943  1.79988 0.792619  2.40453  2.58666  3.38920  3.57729  2.19103 -0.0771458 0.349168 0.496298  1.51268 0.786439 0.189864 -0.0466097 0.220545 -0.0580124 0.304880 -0.146793 -0.120841 -0.0743376  3.08876  1.54109 -4.88692 0.436781
 13:     2151.3825:  1.54382  1.67092  1.23238  2.34639  2.31780  2.35651  2.90366  2.47672 -0.507276 0.184877 -0.572970 -0.394125 -0.390283 -0.831761 -0.873979 -0.994070 -0.680964 -0.437661 -0.743627 -0.952097 -0.981908  1.31348  1.13330 -1.59693  2.80059  1.80040 0.795246  2.40161  2.58854  3.38403  3.56701  2.18947 -0.0783404 0.350223 0.498289  1.51724 0.790426 0.191463 -0.0471717 0.223155 -0.0586814 0.306525 -0.148469 -0.122243 -0.0751850  3.08891  1.54522 -4.89493 0.450791
 14:     2150.9752:  1.54725  1.67834  1.24542  2.34467  2.31817  2.35203  2.91858  2.48817 -0.512052 0.185611 -0.579373 -0.398345 -0.394316 -0.843140 -0.885668 -1.00654 -0.688043 -0.441997 -0.752624 -0.962363 -0.994323  1.31479  1.13347 -1.59879  2.80349  1.80049 0.801803  2.39347  2.59350  3.37457  3.54838  2.18589 -0.0816736 0.352772 0.503431  1.52879 0.800781 0.195819 -0.0487646 0.230292 -0.0605597 0.310798 -0.153351 -0.126281 -0.0776559  3.08606  1.54835 -4.90089 0.427671
 15:     2150.0833:  1.55358  1.69455  1.27655  2.33381  2.31634  2.33754  2.93033  2.51129 -0.523410 0.187328 -0.594793 -0.408429 -0.403953 -0.870926 -0.914186 -1.03692 -0.705055 -0.452341 -0.774434 -0.987181 -1.02456  1.31829  1.13384 -1.60361  2.81025  1.79867 0.816419  2.37410  2.60517  3.36075  3.52124  2.17882 -0.0898531 0.358372 0.515308  1.55502 0.824745 0.206309 -0.0527317 0.247549 -0.0651937 0.320693 -0.165693 -0.136421 -0.0839090  3.07460  1.54456 -4.89215 0.450288
 16:     2143.1931:  1.47747  1.72327  1.65067  2.10152  2.32319  2.28548  3.01978  2.63878 -0.683880 0.199001 -0.827022 -0.552295 -0.542141 -1.32663 -1.38010 -1.52868 -0.958690 -0.599817 -1.11741 -1.37072 -1.51432  1.39597  1.13824 -1.70596  2.96899  1.79663  1.08450  2.07094  2.82023  3.17122  3.12681  2.07184 -0.242828 0.468640 0.743698  2.04914  1.26993 0.405820 -0.128582 0.573481 -0.152079 0.507835 -0.400432 -0.329209 -0.202860  2.91371  1.35015 -4.65335 0.426089
 17:     2138.8573:  1.28256  1.45389  1.51804  2.18053  2.26210  2.51091  3.02491  2.43289 -0.754879 0.176816 -0.972895 -0.619689 -0.607993 -1.73503 -1.79387 -1.95610 -1.11269 -0.667799 -1.38040 -1.65126 -1.94059  1.51488  1.14201 -1.86263  3.17725  1.89994  1.38678  1.88360  2.92459  2.94354  2.71261  1.92171 -0.434060 0.627444  1.05169  2.62912  1.79530 0.670257 -0.230613 0.997770 -0.259749 0.748905 -0.710425 -0.583469 -0.360067  2.82269  1.06490 -4.53432 0.460200
 18:     2136.9174:  1.46123  1.52732  1.24710  2.68726  2.29746  2.22374  3.02007  2.42926 -0.769602 0.164270 -1.05332 -0.638253 -0.625898 -2.10656 -2.16901 -2.34142 -1.19528 -0.683694 -1.57978 -1.86065 -2.32500  1.64902  1.14605 -2.04769  3.24671  2.03345  1.63080  1.83250  2.71121  2.57091  2.43095  1.70774 -0.649727 0.791986  1.38426  3.12291  2.28299 0.973299 -0.357157  1.47736 -0.383789 0.996003 -1.09174 -0.894090 -0.553740  2.61442 0.887375 -4.45874 0.451350
 19:     2135.3625:  1.80814  1.87647  1.03381  2.40319  2.36269  2.36022  2.90934  2.64103 -0.705793 0.160090 -1.02526 -0.586843 -0.576516 -2.38544 -2.44819 -2.62346 -1.15953 -0.627073 -1.65724 -1.93325 -2.60676  1.85433  1.15641 -2.35860  3.15765  2.24155  1.75518  2.01232  2.19425  2.29212  2.35929  1.51206 -0.877057 0.919222  1.71461  3.49013  2.66896  1.29772 -0.513363  1.97396 -0.530381  1.20998 -1.55755 -1.26905 -0.791005  2.55045 0.861141 -4.98048 0.421767
 20:     2135.3441:  1.62854  2.24639  1.81946  2.14023  2.31366  2.19526  2.89060  2.22748 -0.641943 0.223939 -0.886167 -0.522522 -0.515894 -2.44828 -2.51042 -2.69008 -1.01510 -0.566621 -1.53549 -1.80893 -2.67314  2.19609  1.18641 -2.98272  2.85174  2.31258  1.57901  2.28101  2.13590  2.46391  2.17316  1.68483 -0.993868 0.887271  1.85945  3.47199  2.64485  1.51904 -0.677511  2.26988 -0.663648  1.21470 -2.06379 -1.64764 -1.05281  2.56574 0.377885 -5.32942 0.422369
 21:     2132.8401:  1.50011  1.97731  2.07483  2.27115  2.24290  2.22243  2.85437  2.30139 -0.660134 0.185063 -0.836193 -0.532380 -0.528403 -2.40714 -2.46846 -2.65093 -0.964593 -0.583546 -1.44298 -1.71594 -2.63418  2.40095  1.21507 -3.41043  2.72368  2.25515  1.40990  2.34958  2.36206  2.50635  2.26096  1.75676 -0.996652 0.807995  1.84521  3.34325  2.50113  1.56969 -0.749205  2.31988 -0.713154  1.13687 -2.29060 -1.80359 -1.17230  2.54264 0.321396 -5.52156 0.437110
 22:     2129.8704:  1.54316  1.95217  1.68221  2.23040  2.32608  2.24173  2.87482  2.32522 -0.766486 0.0818025 -0.877197 -0.617413 -0.611436 -2.31103 -2.37156 -2.56038 -1.01060 -0.680394 -1.37837 -1.65557 -2.54430  2.43122  1.20497 -3.43220  2.83336  2.16277  1.25159  2.23871  2.74742  2.53999  2.41346  1.76679 -0.917862 0.707760  1.73927  3.14945  2.25344  1.55029 -0.804786  2.25418 -0.716434 0.988578 -2.48291 -1.90331 -1.27921  2.46309 0.127418 -5.57275 0.463928
 23:     2129.6515:  1.50075  1.84616  1.50775  2.27591  1.93105  2.24518  2.89569  2.34155 -0.853161 0.0587323 -0.959731 -0.691013 -0.682369 -2.20700 -2.26575 -2.46031 -1.09602 -0.758720 -1.36429 -1.64223 -2.44543  2.34813  1.15560 -3.16210  3.05875  2.13357  1.23942  2.17888  2.66177  2.49783  2.73910  1.73065 -0.830882 0.657901  1.61948  3.00949  2.04069  1.51515 -0.857646  2.16494 -0.689458 0.848217 -2.67323 -1.98023 -1.38984  2.34505 0.0187531 -5.68958 0.466301
 24:     2128.2568:  1.47906  1.73159  1.45524  2.32373  1.99154  2.26863  2.88889  2.39439 -0.872949 0.0655178 -1.00224 -0.711140 -0.702656 -2.15649 -2.21345 -2.40983 -1.13738 -0.776897 -1.37312 -1.64813 -2.39575  2.31237  1.13522 -3.04407  3.16787  2.15566  1.28877  2.23376  2.50775  2.64610  2.69982  1.77559 -0.793262 0.659782  1.56502  2.95421  1.95957  1.50492 -0.890089  2.13081 -0.665070 0.799142 -2.78937 -2.02206 -1.45873  2.19172 -0.00224236 -5.69432 0.435361
 25:     2127.5928:  1.47524  1.66478  1.49762  2.30419  2.19475  2.29031  2.87186  2.39607 -0.849406 0.0948497 -1.01751 -0.695520 -0.688943 -2.11874 -2.17317 -2.36923 -1.14924 -0.756000 -1.38649 -1.65534 -2.35592  2.32081  1.11574 -3.02262  3.21083  2.24466  1.37890  2.34270  2.48625  2.46916  2.75329  1.79205 -0.771342 0.696706  1.53919  2.94046  1.93319  1.50915 -0.928503  2.11862 -0.639254 0.792997 -2.92539 -2.06853 -1.54122  2.01735 -0.0128354 -5.66238 0.435960
 26:     2127.1062:  1.55949  1.71023  1.50183  2.30125  2.18011  2.31032  2.86416  2.43316 -0.792702 0.117350 -1.00417 -0.651441 -0.647846 -2.07385 -2.12464 -2.31826 -1.13146 -0.705758 -1.39326 -1.65323 -2.30578  2.36736  1.08499 -3.07010  3.18895  2.36675  1.47446  2.42959  2.59274  2.48811  2.66146  1.72079 -0.752934 0.759427  1.52616  2.94111  1.93072  1.52033 -0.978774  2.11007 -0.610155 0.814663 -3.10608 -2.12349 -1.65440  1.82999 -0.00380138 -5.62681 0.467521
 27:     2126.4061:  1.57956  1.80836  1.48538  2.28995  2.19398  2.29843  2.84875  2.43048 -0.739479 0.103495 -0.969063 -0.607091 -0.606073 -2.04254 -2.08950 -2.27977 -1.09439 -0.659066 -1.40017 -1.65349 -2.26808  2.44428  1.05365 -3.19281  3.06219  2.37856  1.51718  2.31968  2.69277  2.52189  2.66460  1.75757 -0.751211 0.813923  1.53195  2.96314  1.96616  1.53927 -1.03588  2.11391 -0.593916 0.859977 -3.31613 -2.18241 -1.79247  1.71545 0.0408659 -5.67749 0.437733
 28:     2126.1159:  1.60397  1.80816  1.47425  2.32892  2.26384  2.29918  2.85634  2.43336 -0.759540 0.0597531 -0.956047 -0.620909 -0.619518 -2.02281 -2.06627 -2.25531 -1.08461 -0.678374 -1.41290 -1.66685 -2.24436  2.48842  1.01376 -3.23403  2.98853  2.28001  1.46717  2.26231  2.60204  2.59596  2.69652  1.84027 -0.738990 0.810828  1.53553  2.96317  1.98599  1.55227 -1.10161  2.10202 -0.578118 0.891730 -3.56007 -2.23301 -1.96887  1.71844 -0.0897258 -5.78149 0.438839
 29:     2125.9448:  1.57795  1.79863  1.45880  2.31985  2.30413  2.27948  2.85240  2.41520 -0.799312 0.0713505 -0.944195 -0.649134 -0.646234 -1.99338 -2.03331 -2.22125 -1.07761 -0.714339 -1.40983 -1.66813 -2.21096  2.48842 0.969034 -3.17062  3.02589  2.18423  1.37109  2.34674  2.55830  2.65960  2.69320  1.87001 -0.712607 0.764346  1.53680  2.93930  1.98951  1.55314 -1.16818  2.06555 -0.552024 0.915918 -3.80638 -2.25097 -2.17704  1.74700 0.0524304 -5.76821 0.437660
 30:     2125.7852:  1.59160  1.79733  1.47168  2.33745  2.27540  2.29562  2.87244  2.43693 -0.827549 0.109006 -0.944854 -0.671351 -0.668253 -1.97651 -2.01380 -2.20216 -1.08141 -0.739663 -1.40099 -1.66574 -2.19230  2.49754 0.936991 -3.13258  3.11869  2.20824  1.31886  2.47341  2.56855  2.63642  2.63849  1.83691 -0.696343 0.716892  1.55217  2.91688  1.99211  1.56855 -1.24417  2.04773 -0.529853 0.936138 -4.06687 -2.27127 -2.42460  1.74652 -0.0166646 -5.78002 0.429906
 31:     2125.6001:  1.57700  1.76718  1.49409  2.32834  2.29062  2.28807  2.87178  2.44760 -0.800973 0.130918 -0.950321 -0.651867 -0.650879 -1.95628 -1.99166 -2.18017 -1.08518 -0.714803 -1.38300 -1.65134 -2.17053  2.50020 0.912590 -3.09202  3.16107  2.33238  1.37950  2.37550  2.56839  2.65310  2.63118  1.73773 -0.692018 0.716242  1.56318  2.90584  1.98678  1.58076 -1.31826  2.02301 -0.511850 0.939813 -4.28729 -2.26846 -2.71090  1.73799 -0.0194655 -5.80747 0.433135
 32:     2125.4708:  1.58012  1.77005  1.48624  2.32347  2.26080  2.28971  2.87636  2.45818 -0.774747 0.127226 -0.954728 -0.632367 -0.632844 -1.94551 -1.98011 -2.16866 -1.08756 -0.690786 -1.37297 -1.64239 -2.15904  2.50514 0.899363 -3.07693  3.16229  2.39169  1.43188  2.31800  2.56820  2.62658  2.60779  1.80163 -0.695418 0.728016  1.56672  2.90504  1.98204  1.58658 -1.36315  2.00534 -0.504449 0.936594 -4.40136 -2.26053 -2.90468  1.72522 -0.00495619 -5.80803 0.443012
 33:     2125.3487:  1.59636  1.78455  1.47490  2.31816  2.24898  2.28760  2.88274  2.45212 -0.745883 0.0889103 -0.958720 -0.610613 -0.611541 -1.94689 -1.98208 -2.17002 -1.08794 -0.665374 -1.37547 -1.64083 -2.16014  2.51941 0.888828 -3.09474  3.06760  2.32577  1.47817  2.36703  2.57810  2.61044  2.60976  1.75870 -0.716098 0.765470  1.56227  2.93043  1.98212  1.58661 -1.39488  1.98745 -0.514834 0.917940 -4.40578 -2.24201 -3.11048  1.71619 -0.00692215 -5.82600 0.447130
 34:     2125.1428:  1.61088  1.83756  1.47845  2.34831  2.25467  2.30388  2.89774  2.46266 -0.722063 0.231738 -0.917141 -0.586937 -0.586661 -1.92431 -1.96049 -2.14265 -1.03972 -0.644138 -1.35565 -1.60337 -2.13220  2.55414 0.823616 -3.09464  2.99172  2.23433  1.42367  2.31175  2.57206  2.56209  2.60599  1.74151 -0.774539 0.785311  1.53303  2.96470  1.96659  1.57599 -1.47042  1.92821 -0.556771 0.869952 -4.31115 -2.19062 -3.75244  1.66868 -0.0121193 -5.89050 0.442384
 35:     2125.0246:  1.66333  1.86346  1.53014  2.36563  2.26315  2.31688  2.91561  2.46249 -0.706504 0.101415 -0.879040 -0.569476 -0.568945 -1.89900 -1.93597 -2.11327 -1.00137 -0.628748 -1.33146 -1.56976 -2.10228  2.58740 0.743737 -3.07411  2.97415  2.22112  1.35351  2.25290  2.53618  2.51110  2.58520  1.72299 -0.823021 0.740970  1.50334  2.96985  1.94465  1.56329 -1.54229  1.86999 -0.598435 0.832598 -4.22371 -2.15541 -4.40848  1.63660 0.00192353 -5.92599 0.434881
 36:     2124.9759:  1.60290  1.87451  1.50266  2.36308  2.26644  2.31363  2.91545  2.46679 -0.711474 0.102278 -0.896981 -0.575245 -0.575923 -1.90355 -1.94102 -2.12030 -1.02689 -0.632436 -1.33686 -1.58676 -2.10908  2.60945 0.712835 -3.09074  2.95567  2.23274  1.35370  2.26199  2.50243  2.50526  2.57460  1.71212 -0.825853 0.679865  1.49525  2.93633  1.93379  1.55835 -1.55222  1.86393 -0.611507 0.835845 -4.21326 -2.17722 -4.55474  1.64450 0.00313375 -5.93481 0.435791
 37:     2124.9299:  1.62339  1.82668  1.48886  2.33451  2.26540  2.29945  2.91330  2.45532 -0.717954 0.130251 -0.916078 -0.582392 -0.584227 -1.90957 -1.94734 -2.12912 -1.05190 -0.638054 -1.34353 -1.60553 -2.11774  2.62440 0.684460 -3.09252  2.94541  2.22153  1.35411  2.26253  2.48011  2.50517  2.55924  1.70849 -0.825711 0.629872  1.48750  2.89580  1.92158  1.55209 -1.55466  1.86215 -0.622946 0.841782 -4.20731 -2.20793 -4.65361  1.65522 0.00279746 -5.94154 0.438602
 38:     2124.9247:  1.59271  1.80821  1.50703  2.34155  2.28174  2.30100  2.90454  2.47037 -0.728648 0.131321 -0.920705 -0.592268 -0.594237 -1.90779 -1.94456 -2.12815 -1.05012 -0.650493 -1.34412 -1.60876 -2.11678  2.61173 0.646491 -3.01558  2.95304  2.15548  1.33121  2.24491  2.49242  2.49886  2.53261  1.69452 -0.824450 0.650076  1.47293  2.84290  1.89692  1.53612 -1.54071  1.86205 -0.630991 0.840782 -4.20945 -2.25866 -4.65882  1.66817 -0.00627829 -5.95184 0.442400
 39:     2124.9022:  1.60159  1.81152  1.50288  2.34116  2.27922  2.30180  2.90511  2.46835 -0.740513 0.132999 -0.921189 -0.601878 -0.603067 -1.91365 -1.95020 -2.13436 -1.04710 -0.661906 -1.34902 -1.60943 -2.12295  2.62786 0.636979 -3.04393  2.95658  2.16467  1.31150  2.23632  2.46289  2.48937  2.52105  1.68059 -0.831289 0.663253  1.46395  2.84085  1.88663  1.52705 -1.53491  1.86093 -0.636312 0.826461 -4.22353 -2.28073 -4.63650  1.67279 -0.000909314 -5.93461 0.441840
 40:     2124.8796:  1.61974  1.81065  1.49575  2.34379  2.27098  2.30058  2.90440  2.46286 -0.733704 0.135210 -0.921258 -0.595060 -0.596945 -1.92349 -1.95968 -2.14449 -1.05274 -0.652488 -1.35681 -1.61141 -2.13305  2.64503 0.607728 -3.04957  2.91223  2.18010  1.28582  2.22111  2.43680  2.47108  2.50298  1.66345 -0.862751 0.589782  1.43232  2.83173  1.85783  1.49812 -1.53646  1.84459 -0.662728 0.780157 -4.27058 -2.32313 -4.65353  1.65497 0.00244633 -5.92294 0.438083
 41:     2124.8655:  1.62166  1.82068  1.49586  2.33798  2.26626  2.29679  2.90335  2.45913 -0.729094 0.130680 -0.917860 -0.592500 -0.594664 -1.92761 -1.96395 -2.14901 -1.05341 -0.649845 -1.35435 -1.61241 -2.13744  2.67305 0.574229 -3.07520  2.91804  2.13110  1.26127  2.18491  2.40195  2.43858  2.47321  1.62895 -0.894956 0.555675  1.40409  2.80607  1.83357  1.46810 -1.54704  1.82452 -0.693044 0.754063 -4.29852 -2.35652 -4.71093  1.65325 0.00232989 -5.91362 0.437753
 42:     2124.8218:  1.62899  1.82834  1.50110  2.33404  2.26129  2.29118  2.90613  2.45329 -0.759507 0.128011 -0.918195 -0.619336 -0.620739 -1.93880 -1.97578 -2.16190 -1.05209 -0.682703 -1.34934 -1.61933 -2.14984  2.75002 0.426203 -3.07097  2.77709  2.02309  1.11165  2.04442  2.26401  2.30072  2.34056  1.48998 -1.02581 0.484256  1.27668  2.67592  1.71774  1.32757 -1.59734  1.72068 -0.820812 0.647366 -4.39327 -2.48382 -4.91848  1.70463 0.00692916 -5.84287 0.438201
 43:     2124.7680:  1.61944  1.81820  1.49450  2.33203  2.25831  2.28484  2.90201  2.45176 -0.757307 0.124401 -0.929615 -0.614336 -0.615586 -1.94663 -1.98390 -2.17142 -1.04887 -0.675347 -1.36290 -1.62323 -2.15901  2.81847 0.278397 -3.03692  2.66162  1.88933 0.977514  1.91634  2.12290  2.17325  2.21192  1.35763 -1.15761 0.375994  1.13359  2.53768  1.57374  1.17451 -1.67054  1.60110 -0.954077 0.501098 -4.52836 -2.62488 -5.00663  1.67110 0.00676545 -5.78838 0.439281
 44:     2124.7233:  1.61953  1.82173  1.49984  2.34113  2.26165  2.28445  2.90104  2.45306 -0.748339 0.128404 -0.928499 -0.614009 -0.616670 -1.94738 -1.98440 -2.17157 -1.05618 -0.674201 -1.36860 -1.62163 -2.15909  2.88417 0.134144 -2.99637  2.53794  1.74463 0.882018  1.78624  2.00866  2.04790  2.08277  1.23188 -1.28568 0.220139 0.997502  2.39932  1.43485  1.02685 -1.77569  1.47264 -1.08418 0.359191 -4.67777 -2.75614 -5.09322  1.70689 0.00911793 -5.73136 0.439602
 45:     2124.6975:  1.60333  1.81090  1.49338  2.33142  2.25847  2.27660  2.89597  2.44959 -0.745866 0.123630 -0.928312 -0.598029 -0.599439 -1.94554 -1.98257 -2.16962 -1.06221 -0.657755 -1.36404 -1.62789 -2.15735  2.94906 -0.00765556 -2.94971  2.40687  1.62131 0.725589  1.67245  1.91774  1.93351  1.96635  1.12149 -1.41664 0.0939030 0.872225  2.27274  1.31647 0.895619 -1.94161  1.33482 -1.21157 0.235901 -4.84773 -2.87853 -5.24585  1.70080 0.00287269 -5.72247 0.439309
 46:     2124.6850:  1.60374  1.80760  1.49576  2.33832  2.26144  2.28449  2.89772  2.45436 -0.733806 0.126243 -0.929523 -0.612983 -0.618792 -1.92918 -1.96578 -2.15077 -1.04555 -0.667620 -1.35299 -1.61334 -2.13892  2.97187 -0.0623214 -2.91981  2.34600  1.56308 0.727544  1.62544  1.86999  1.88735  1.92162  1.07750 -1.45974 0.0170209 0.821158  2.21967  1.26317 0.843774 -2.07712  1.24910 -1.25952 0.189034 -4.88942 -2.91323 -5.28410  1.68986 -0.00543231 -5.74225 0.438858
 47:     2124.6802:  1.61301  1.81513  1.50183  2.35034  2.26861  2.29264  2.90162  2.45757 -0.739529 0.131854 -0.926514 -0.585381 -0.585186 -1.92525 -1.96154 -2.14531 -1.07221 -0.648073 -1.36301 -1.61460 -2.13361  2.97638 -0.0697867 -2.92037  2.34024  1.55963 0.697141  1.61170  1.85595  1.87514  1.91053  1.06577 -1.46577 -0.00464078 0.813777  2.21233  1.25243 0.836141 -2.15183  1.21468 -1.26765 0.178794 -4.86773 -2.91566 -5.23822  1.70944 -0.00799748 -5.76427 0.439625
 48:     2124.6731:  1.61144  1.81466  1.49704  2.34045  2.26466  2.28649  2.90026  2.45499 -0.728824 0.129212 -0.916071 -0.602261 -0.607469 -1.92844 -1.96466 -2.14936 -1.05951 -0.658513 -1.36089 -1.61797 -2.13756  2.98732 -0.0828281 -2.93029  2.32996  1.55383 0.674178  1.60226  1.84296  1.86261  1.89721  1.05347 -1.48290 0.00219105 0.808572  2.20644  1.24502 0.831558 -2.18175  1.20354 -1.27960 0.167015 -4.88783 -2.93671 -5.25097  1.68825 -0.00410066 -5.78643 0.439291
 49:     2124.6719:  1.61163  1.81415  1.49639  2.33876  2.26392  2.28596  2.90073  2.45564 -0.742891 0.129276 -0.923071 -0.600097 -0.601991 -1.92738 -1.96357 -2.14846 -1.05227 -0.659985 -1.35569 -1.61534 -2.13665  2.99393 -0.0931642 -2.92955  2.31987  1.54276 0.671484  1.59303  1.83089  1.85262  1.88736  1.04360 -1.49239 -0.00234528 0.799875  2.19779  1.23637 0.823724 -2.19393  1.19354 -1.28943 0.159557 -4.90120 -2.94803 -5.26923  1.68187 -0.00207379 -5.79143 0.438979
 50:     2124.6713:  1.61294  1.81471  1.49738  2.34013  2.26501  2.28746  2.90202  2.45699 -0.736549 0.130304 -0.925651 -0.599710 -0.602695 -1.92576 -1.96194 -2.14681 -1.05216 -0.658183 -1.35321 -1.61307 -2.13501  3.00061 -0.103583 -2.92643  2.30931  1.53178 0.660083  1.58200  1.81793  1.84164  1.87712  1.03257 -1.50221 -0.0131108 0.788207  2.18716  1.22555 0.813468 -2.20498  1.18137 -1.30113 0.150371 -4.91096 -2.95902 -5.28081  1.67975 -0.000513460 -5.79537 0.438993
 51:     2124.6710:  1.61353  1.81535  1.49838  2.34084  2.26621  2.28901  2.90316  2.45808 -0.737194 0.130701 -0.916793 -0.599429 -0.602160 -1.92422 -1.96044 -2.14527 -1.05081 -0.658324 -1.35372 -1.61191 -2.13350  3.00825 -0.112239 -2.92334  2.29822  1.52141 0.649666  1.57122  1.80632  1.83073  1.86682  1.02177 -1.51363 -0.0277136 0.776151  2.17563  1.21384 0.803122 -2.21117  1.17087 -1.31345 0.138590 -4.92079 -2.97123 -5.28168  1.67664 0.000593599 -5.80296 0.439150
 52:     2124.6709:  1.61343  1.81518  1.49884  2.34092  2.26679  2.28961  2.90374  2.45866 -0.733634 0.130938 -0.922726 -0.598083 -0.601369 -1.92362 -1.95989 -2.14466 -1.05105 -0.656224 -1.35382 -1.61179 -2.13290  3.01196 -0.111982 -2.92157  2.29549  1.51829 0.647337  1.56883  1.80406  1.82799  1.86357  1.01963 -1.51650 -0.0286101 0.773744  2.17230  1.21078 0.800672 -2.20338  1.17127 -1.31602 0.134800 -4.92556 -2.97449 -5.27816  1.67934 0.000464008 -5.80694 0.439012
 53:     2124.6709:  1.61400  1.81575  1.49913  2.34131  2.26683  2.28945  2.90361  2.45857 -0.734995 0.131314 -0.921702 -0.598228 -0.601131 -1.92333 -1.95957 -2.14423 -1.05242 -0.657026 -1.35212 -1.61112 -2.13246  3.01335 -0.110306 -2.92130  2.29565  1.51918 0.647110  1.56936  1.80485  1.82859  1.86430  1.01996 -1.51547 -0.0287119 0.774649  2.17411  1.21222 0.800627 -2.19774  1.17338 -1.31551 0.136356 -4.92551 -2.97365 -5.28300  1.67726 3.21909e-05 -5.80613 0.439096
 54:     2124.6708:  1.61379  1.81537  1.49866  2.34126  2.26660  2.28927  2.90354  2.45852 -0.735299 0.131250 -0.919654 -0.597969 -0.601021 -1.92367 -1.95993 -2.14462 -1.05069 -0.656107 -1.35346 -1.61208 -2.13285  3.01466 -0.107868 -2.92044  2.29653  1.51994 0.648456  1.57014  1.80544  1.82930  1.86508  1.02064 -1.51480 -0.0275293 0.775342  2.17451  1.21287 0.800732 -2.19505  1.17451 -1.31473 0.137460 -4.92404 -2.97252 -5.28349  1.67796 -7.73514e-05 -5.80527 0.439075
 55:     2124.6708:  1.61361  1.81537  1.49863  2.34107  2.26651  2.28918  2.90345  2.45835 -0.735276 0.131047 -0.920466 -0.598150 -0.600887 -1.92344 -1.95969 -2.14436 -1.05108 -0.657339 -1.35343 -1.61164 -2.13259  3.01654 -0.105883 -2.92000  2.29679  1.52014 0.648600  1.57035  1.80592  1.82956  1.86531  1.02096 -1.51499 -0.0274203 0.775392  2.17427  1.21265 0.800561 -2.19441  1.17474 -1.31469 0.137053 -4.92383 -2.97261 -5.28149  1.67775 -1.85673e-05 -5.80588 0.439079
 56:     2124.6708:  1.61359  1.81548  1.49870  2.34095  2.26656  2.28920  2.90340  2.45832 -0.735818 0.130947 -0.921361 -0.598667 -0.601938 -1.92301 -1.95925 -2.14388 -1.05219 -0.656294 -1.35262 -1.61109 -2.13212  3.02130 -0.102124 -2.91862  2.29652  1.51983 0.648284  1.57014  1.80586  1.82937  1.86506  1.02082 -1.51520 -0.0276920 0.775344  2.17432  1.21250 0.799880 -2.19408  1.17456 -1.31497 0.136398 -4.92446 -2.97317 -5.27995  1.67753 3.39949e-05 -5.80661 0.439077
 57:     2124.6708:  1.61370  1.81552  1.49866  2.34101  2.26668  2.28926  2.90343  2.45843 -0.735066 0.131029 -0.921528 -0.598330 -0.601230 -1.92275 -1.95897 -2.14357 -1.05228 -0.657198 -1.35213 -1.61115 -2.13181  3.03006 -0.0955409 -2.91566  2.29594  1.51934 0.647754  1.56972  1.80522  1.82883  1.86449  1.02031 -1.51530 -0.0281622 0.775217  2.17447  1.21245 0.798729 -2.19386  1.17406 -1.31539 0.135999 -4.92543 -2.97375 -5.28042  1.67765 5.37858e-06 -5.80683 0.439071
 58:     2124.6707:  1.61399  1.81571  1.49851  2.34134  2.26682  2.28922  2.90350  2.45839 -0.734114 0.131254 -0.922081 -0.597800 -0.600150 -1.92213 -1.95831 -2.14282 -1.05078 -0.658505 -1.35256 -1.61105 -2.13106  3.06877 -0.0651786 -2.90277  2.29514  1.51874 0.646491  1.56887  1.80422  1.82779  1.86350  1.01929 -1.51628 -0.0292615 0.774359  2.17321  1.21117 0.795070 -2.19334  1.17245 -1.31648 0.135167 -4.92680 -2.97485 -5.28324  1.67783 -6.39553e-05 -5.80710 0.439093
 59:     2124.6706:  1.61389  1.81517  1.49796  2.34126  2.26659  2.28888  2.90351  2.45837 -0.733111 0.131235 -0.920087 -0.597157 -0.598845 -1.92153 -1.95770 -2.14216 -1.05285 -0.660040 -1.35223 -1.61082 -2.13039  3.16670 0.0132364 -2.86989  2.29378  1.51731 0.646048  1.56757  1.80226  1.82626  1.86200  1.01784 -1.51750 -0.0293327 0.773277  2.17167  1.20985 0.789406 -2.19383  1.16979 -1.31780 0.134463 -4.92755 -2.97604 -5.28562  1.67829 -0.000128205 -5.80657 0.439026
 60:     2124.6705:  1.61409  1.81555  1.49816  2.34134  2.26675  2.28891  2.90347  2.45842 -0.733766 0.131289 -0.921446 -0.597514 -0.599630 -1.92186 -1.95803 -2.14251 -1.04865 -0.658659 -1.35197 -1.61172 -2.13075  3.27149 0.0970655 -2.83663  2.29317  1.51693 0.644161  1.56681  1.80187  1.82570  1.86153  1.01713 -1.51759 -0.0318939 0.772992  2.17237  1.21033 0.787883 -2.19600  1.16876 -1.31845 0.134076 -4.92740 -2.97675 -5.28502  1.67856 -0.000103668 -5.80604 0.439110
 61:     2124.6704:  1.61407  1.81568  1.49849  2.34147  2.26685  2.28941  2.90356  2.45847 -0.734747 0.131417 -0.920744 -0.597839 -0.600789 -1.92248 -1.95869 -2.14325 -1.05043 -0.656856 -1.35353 -1.61151 -2.13150  3.32550 0.138088 -2.82134  2.29368  1.51712 0.645245  1.56728  1.80256  1.82627  1.86200  1.01769 -1.51781 -0.0303900 0.772551  2.17100  1.20915 0.791696 -2.19887  1.16941 -1.31808 0.133841 -4.92856 -2.97651 -5.28778  1.67785 4.02024e-06 -5.80623 0.439090
 62:     2124.6704:  1.61364  1.81533  1.49872  2.34101  2.26661  2.28943  2.90345  2.45847 -0.735470 0.130994 -0.920575 -0.598519 -0.601198 -1.92361 -1.95988 -2.14457 -1.05162 -0.656375 -1.35291 -1.61136 -2.13281  3.35778 0.160479 -2.81237  2.29343  1.51681 0.645221  1.56698  1.80249  1.82621  1.86195  1.01763 -1.51827 -0.0308670 0.772148  2.17122  1.20969 0.795426 -2.19931  1.17071 -1.31793 0.134147 -4.92668 -2.97598 -5.28442  1.67792 -1.10095e-05 -5.80553 0.439068
 63:     2124.6704:  1.61365  1.81535  1.49883  2.34108  2.26664  2.28944  2.90346  2.45849 -0.735510 0.131064 -0.920649 -0.597723 -0.601740 -1.92359 -1.95986 -2.14455 -1.05171 -0.656679 -1.35292 -1.61173 -2.13279  3.37464 0.170145 -2.80716  2.29336  1.51664 0.645180  1.56693  1.80251  1.82619  1.86191  1.01761 -1.51818 -0.0308715 0.771940  2.17120  1.20945 0.796848 -2.19956  1.17091 -1.31803 0.133533 -4.92726 -2.97603 -5.28533  1.67783 2.12917e-05 -5.80586 0.439072
 64:     2124.6703:  1.61376  1.81545  1.49903  2.34130  2.26675  2.28949  2.90348  2.45853 -0.735177 0.131264 -0.920902 -0.598981 -0.600632 -1.92344 -1.95966 -2.14433 -1.05164 -0.656793 -1.35329 -1.61222 -2.13258  3.41253 0.187485 -2.79562  2.29312  1.51628 0.644963  1.56679  1.80250  1.82609  1.86173  1.01749 -1.51811 -0.0309353 0.771544  2.17093  1.20883 0.800319 -2.19995  1.17131 -1.31832 0.132451 -4.92900 -2.97627 -5.28770  1.67762 6.81340e-05 -5.80665 0.439082
 65:     2124.6703:  1.61380  1.81550  1.49894  2.34130  2.26680  2.28957  2.90346  2.45853 -0.735016 0.131240 -0.921091 -0.598033 -0.600937 -1.92341 -1.95964 -2.14430 -1.05131 -0.657288 -1.35361 -1.61172 -2.13255  3.42717 0.184627 -2.79173  2.29285  1.51615 0.644669  1.56663  1.80230  1.82585  1.86151  1.01728 -1.51850 -0.0312609 0.771521  2.17063  1.20875 0.802174 -2.19957  1.17149 -1.31848 0.132927 -4.92933 -2.97645 -5.28747  1.67760 3.33668e-06 -5.80658 0.439084
 66:     2124.6702:  1.61379  1.81550  1.49855  2.34125  2.26678  2.28963  2.90341  2.45843 -0.734673 0.131092 -0.921208 -0.596440 -0.601254 -1.92310 -1.95931 -2.14391 -1.05080 -0.658190 -1.35285 -1.61147 -2.13217  3.49384 0.178711 -2.77260  2.29255  1.51612 0.644223  1.56631  1.80179  1.82538  1.86112  1.01687 -1.51931 -0.0317826 0.771301  2.17017  1.20853 0.805658 -2.19811  1.17143 -1.31870 0.133284 -4.92864 -2.97664 -5.28599  1.67790 -0.000153784 -5.80595 0.439081
 67:     2124.6701:  1.61376  1.81548  1.49803  2.34113  2.26671  2.28960  2.90333  2.45835 -0.734395 0.130922 -0.921272 -0.595124 -0.601551 -1.92238 -1.95857 -2.14306 -1.05035 -0.658987 -1.35323 -1.60996 -2.13132  3.65102 0.168810 -2.72728  2.29256  1.51636 0.644056  1.56634  1.80163  1.82528  1.86111  1.01681 -1.51928 -0.0320487 0.771703  2.17061  1.20919 0.810658 -2.19619  1.17139 -1.31850 0.134447 -4.92762 -2.97655 -5.28425  1.67827 -0.000256837 -5.80531 0.439075
 68:     2124.6699:  1.61379  1.81554  1.49723  2.34113  2.26661  2.28945  2.90328  2.45812 -0.734195 0.130753 -0.920992 -0.594131 -0.601769 -1.92137 -1.95752 -2.14187 -1.04961 -0.659298 -1.35109 -1.61081 -2.13014  3.98562 0.100145 -2.63490  2.29443  1.51840 0.645642  1.56799  1.80299  1.82676  1.86272  1.01833 -1.51797 -0.0305086 0.773510  2.17201  1.21075 0.817599 -2.19257  1.17197 -1.31676 0.136675 -4.92449 -2.97510 -5.28006  1.67883 -0.000336723 -5.80437 0.439072
 69:     2124.6697:  1.61381  1.81555  1.49704  2.34099  2.26641  2.28885  2.90336  2.45808 -0.734607 0.130811 -0.920504 -0.595445 -0.601706 -1.92092 -1.95706 -2.14139 -1.04983 -0.658239 -1.35163 -1.61029 -2.12964  4.09606 -0.0665292 -2.61380  2.29794  1.52167 0.648974  1.57122  1.80613  1.83008  1.86611  1.02156 -1.51350 -0.0271350 0.776962  2.17648  1.21461 0.815661 -2.18972  1.17361 -1.31338 0.138942 -4.92036 -2.97196 -5.27698  1.67913 -0.000186529 -5.80405 0.439073
 70:     2124.6695:  1.61385  1.81553  1.49801  2.34111  2.26653  2.28892  2.90355  2.45836 -0.735135 0.131129 -0.920400 -0.597617 -0.601455 -1.92185 -1.95802 -2.14252 -1.05096 -0.656421 -1.35391 -1.60876 -2.13077  4.44566 -0.133883 -2.52151  2.29752  1.52104 0.649003  1.57103  1.80624  1.83010  1.86595  1.02151 -1.51394 -0.0270465 0.776742  2.17609  1.21437 0.810910 -2.19294  1.17308 -1.31374 0.138693 -4.92190 -2.97215 -5.27912  1.67837 -6.98785e-05 -5.80475 0.439071
 71:     2124.6694:  1.61380  1.81552  1.49896  2.34134  2.26676  2.28954  2.90360  2.45856 -0.735322 0.131285 -0.920502 -0.598662 -0.601086 -1.92322 -1.95945 -2.14411 -1.05151 -0.655866 -1.35283 -1.61150 -2.13237  4.30707 -0.0832823 -2.56046  2.29581  1.51920 0.647783  1.56954  1.80513  1.82876  1.86442  1.02016 -1.51625 -0.0281745 0.774720  2.17301  1.21171 0.803640 -2.19712  1.17260 -1.31556 0.137079 -4.92526 -2.97367 -5.28211  1.67745 9.43869e-06 -5.80585 0.439073
 72:     2124.6693:  1.61381  1.81556  1.49903  2.34124  2.26667  2.28931  2.90361  2.45852 -0.735396 0.131265 -0.920515 -0.598669 -0.601092 -1.92366 -1.95991 -2.14464 -1.05154 -0.656146 -1.35288 -1.61193 -2.13289  4.37980 -0.0862434 -2.54316  2.29652  1.51982 0.648389  1.57013  1.80576  1.82941  1.86511  1.02080 -1.51477 -0.0275438 0.775126  2.17415  1.21238 0.800850 -2.19652  1.17378 -1.31481 0.136613 -4.92453 -2.97285 -5.28215  1.67759 4.54522e-05 -5.80594 0.439077
 73:     2124.6693:  1.61390  1.81566  1.49915  2.34114  2.26657  2.28893  2.90364  2.45853 -0.735412 0.131318 -0.920699 -0.598829 -0.601031 -1.92429 -1.96058 -2.14541 -1.05167 -0.656563 -1.35335 -1.61258 -2.13363  4.59527 -0.0776252 -2.49268  2.29782  1.52095 0.649558  1.57129  1.80693  1.83067  1.86641  1.02199 -1.51325 -0.0264114 0.776293  2.17614  1.21399 0.795335 -2.19563  1.17645 -1.31359 0.137077 -4.92349 -2.97140 -5.28197  1.67767 0.000120822 -5.80631 0.439085
 74:     2124.6692:  1.61392  1.81566  1.49909  2.34110  2.26654  2.28878  2.90366  2.45849 -0.735279 0.131318 -0.920739 -0.598516 -0.601014 -1.92431 -1.96060 -2.14544 -1.05152 -0.656890 -1.35350 -1.61205 -2.13365  4.66524 -0.0536001 -2.47874  2.29778  1.52096 0.649434  1.57123  1.80681  1.83059  1.86635  1.02192 -1.51255 -0.0265130 0.776230  2.17642  1.21401 0.794072 -2.19530  1.17706 -1.31354 0.136497 -4.92324 -2.97129 -5.28213  1.67783 8.25883e-05 -5.80626 0.439086
 75:     2124.6691:  1.61398  1.81564  1.49902  2.34127  2.26660  2.28882  2.90371  2.45848 -0.734975 0.131406 -0.920674 -0.598073 -0.600897 -1.92367 -1.95992 -2.14470 -1.05117 -0.657059 -1.35253 -1.61266 -2.13292  4.98021 0.0102361 -2.41286  2.29710  1.52038 0.648787  1.57058  1.80613  1.82988  1.86563  1.02124 -1.51364 -0.0271522 0.775646  2.17533  1.21315 0.794372 -2.19583  1.17739 -1.31429 0.136361 -4.92376 -2.97208 -5.28200  1.67783 4.34306e-05 -5.80617 0.439086
 76:     2124.6689:  1.61393  1.81548  1.49889  2.34143  2.26673  2.28915  2.90371  2.45857 -0.734827 0.131439 -0.920516 -0.597803 -0.600917 -1.92262 -1.95882 -2.14345 -1.05105 -0.656733 -1.35284 -1.61100 -2.13169  5.21596 0.0683312 -2.36978  2.29555  1.51895 0.647323  1.56919  1.80467  1.82839  1.86408  1.01978 -1.51643 -0.0286348 0.774512  2.17359  1.21191 0.799116 -2.19714  1.17512 -1.31592 0.136146 -4.92513 -2.97393 -5.28280  1.67787 -5.52281e-06 -5.80581 0.439080
 77:     2124.6689:  1.61388  1.81543  1.49889  2.34150  2.26680  2.28937  2.90371  2.45861 -0.734843 0.131440 -0.920372 -0.597888 -0.600908 -1.92225 -1.95843 -2.14300 -1.05102 -0.656342 -1.35294 -1.61011 -2.13126  5.60403 0.0964333 -2.29102  2.29492  1.51841 0.646773  1.56867  1.80416  1.82783  1.86349  1.01924 -1.51696 -0.0291437 0.774064  2.17272  1.21125 0.801529 -2.19782  1.17383 -1.31648 0.136041 -4.92568 -2.97466 -5.28306  1.67780 -2.36023e-05 -5.80568 0.439075
 78:     2124.6689:  1.61388  1.81549  1.49887  2.34143  2.26673  2.28931  2.90367  2.45852 -0.734983 0.131347 -0.920455 -0.598000 -0.600985 -1.92265 -1.95885 -2.14346 -1.05113 -0.656446 -1.35235 -1.61157 -2.13172  5.50219 0.0679814 -2.31514  2.29552  1.51898 0.647346  1.56920  1.80472  1.82837  1.86407  1.01980 -1.51598 -0.0285592 0.774434  2.17292  1.21144 0.801003 -2.19697  1.17349 -1.31584 0.136552 -4.92509 -2.97401 -5.28230  1.67771 6.07846e-08 -5.80579 0.439074
 79:     2124.6688:  1.61389  1.81551  1.49886  2.34139  2.26671  2.28927  2.90365  2.45852 -0.735050 0.131328 -0.920507 -0.598067 -0.601035 -1.92284 -1.95905 -2.14368 -1.05123 -0.656465 -1.35245 -1.61171 -2.13194  5.66588 0.0553041 -2.28614  2.29574  1.51916 0.647544  1.56938  1.80486  1.82855  1.86427  1.01996 -1.51623 -0.0283943 0.774606  2.17325  1.21172 0.800989 -2.19649  1.17258 -1.31572 0.136594 -4.92495 -2.97380 -5.28238  1.67775 5.56817e-06 -5.80581 0.439076
 80:     2124.6688:  1.61388  1.81556  1.49892  2.34129  2.26663  2.28917  2.90361  2.45848 -0.735124 0.131296 -0.920598 -0.598158 -0.601091 -1.92332 -1.95955 -2.14424 -1.05132 -0.656549 -1.35286 -1.61162 -2.13249  6.32136 0.0176902 -2.16903  2.29583  1.51926 0.647631  1.56950  1.80500  1.82868  1.86443  1.02010 -1.51494 -0.0282822 0.774726  2.17342  1.21175 0.800651 -2.19555  1.17027 -1.31543 0.136695 -4.92488 -2.97344 -5.28239  1.67758 4.10917e-06 -5.80608 0.439075
 81:     2124.6687:  1.61390  1.81556  1.49897  2.34129  2.26667  2.28913  2.90365  2.45854 -0.735054 0.131356 -0.920591 -0.598106 -0.601031 -1.92335 -1.95959 -2.14429 -1.05127 -0.656608 -1.35324 -1.61089 -2.13254  6.00905 0.00721801 -2.22815  2.29591  1.51929 0.647680  1.56955  1.80502  1.82876  1.86449  1.02015 -1.51526 -0.0282614 0.774819  2.17398  1.21215 0.799639 -2.19587  1.17168 -1.31545 0.136205 -4.92488 -2.97336 -5.28283  1.67773 -8.82643e-06 -5.80603 0.439079
 82:     2124.6687:  1.61392  1.81557  1.49896  2.34129  2.26666  2.28912  2.90365  2.45853 -0.735052 0.131348 -0.920610 -0.598051 -0.601038 -1.92337 -1.95961 -2.14431 -1.05126 -0.656685 -1.35299 -1.61139 -2.13256  6.18505 -0.00765507 -2.19838  2.29603  1.51940 0.647789  1.56965  1.80512  1.82885  1.86459  1.02024 -1.51533 -0.0281618 0.774874  2.17401  1.21218 0.799528 -2.19568  1.17177 -1.31536 0.136308 -4.92474 -2.97325 -5.28261  1.67773 -5.51381e-06 -5.80601 0.439080
 83:     2124.6686:  1.61392  1.81558  1.49897  2.34129  2.26666  2.28912  2.90365  2.45853 -0.735055 0.131343 -0.920617 -0.598036 -0.601041 -1.92342 -1.95966 -2.14437 -1.05126 -0.656712 -1.35298 -1.61144 -2.13262  6.39558 -0.0236319 -2.16340  2.29608  1.51945 0.647840  1.56970  1.80518  1.82891  1.86465  1.02030 -1.51522 -0.0281117 0.774913  2.17406  1.21223 0.799459 -2.19564  1.17193 -1.31529 0.136350 -4.92470 -2.97318 -5.28255  1.67772 -3.91170e-06 -5.80602 0.439080
 84:     2124.6686:  1.61392  1.81559  1.49896  2.34130  2.26665  2.28913  2.90365  2.45852 -0.735052 0.131331 -0.920629 -0.597985 -0.601047 -1.92339 -1.95963 -2.14434 -1.05124 -0.656765 -1.35278 -1.61183 -2.13258  6.60626 -0.0405976 -2.12976  2.29614  1.51952 0.647900  1.56974  1.80524  1.82896  1.86470  1.02035 -1.51523 -0.0280554 0.774930  2.17401  1.21221 0.799438 -2.19564  1.17243 -1.31523 0.136488 -4.92460 -2.97313 -5.28232  1.67772 2.19476e-07 -5.80599 0.439079
 85:     2124.6686:  1.61392  1.81559  1.49894  2.34132  2.26666  2.28916  2.90365  2.45851 -0.735041 0.131323 -0.920617 -0.597931 -0.601042 -1.92331 -1.95954 -2.14424 -1.05121 -0.656787 -1.35256 -1.61211 -2.13249  6.78322 -0.0557903 -2.10368  2.29619  1.51957 0.647946  1.56978  1.80530  1.82900  1.86474  1.02040 -1.51532 -0.0280108 0.774934  2.17393  1.21220 0.799491 -2.19586  1.17345 -1.31519 0.136616 -4.92452 -2.97313 -5.28211  1.67773 5.41627e-06 -5.80594 0.439079
 86:     2124.6685:  1.61391  1.81558  1.49892  2.34134  2.26670  2.28923  2.90367  2.45854 -0.735015 0.131335 -0.920579 -0.597911 -0.601020 -1.92317 -1.95940 -2.14408 -1.05119 -0.656711 -1.35275 -1.61157 -2.13233  7.06770 -0.0686594 -2.06438  2.29606  1.51945 0.647827  1.56967  1.80520  1.82889  1.86461  1.02029 -1.51551 -0.0281299 0.774852  2.17388  1.21219 0.799635 -2.19657  1.17513 -1.31531 0.136523 -4.92464 -2.97328 -5.28227  1.67778 1.07967e-06 -5.80587 0.439078
 87:     2124.6685:  1.61391  1.81557  1.49891  2.34135  2.26672  2.28926  2.90368  2.45856 -0.734989 0.131352 -0.920553 -0.597905 -0.601008 -1.92308 -1.95930 -2.14398 -1.05118 -0.656640 -1.35299 -1.61098 -2.13223  7.54999 -0.0753537 -1.99465  2.29587  1.51927 0.647645  1.56950  1.80503  1.82873  1.86443  1.02012 -1.51558 -0.0283064 0.774724  2.17377  1.21209 0.799772 -2.19707  1.17596 -1.31546 0.136388 -4.92481 -2.97345 -5.28251  1.67779 -7.49699e-06 -5.80585 0.439078
 88:     2124.6685:  1.61392  1.81557  1.49888  2.34137  2.26669  2.28922  2.90368  2.45852 -0.734988 0.131341 -0.920561 -0.597888 -0.601023 -1.92298 -1.95920 -2.14386 -1.05117 -0.656671 -1.35267 -1.61160 -2.13211  7.55646 -0.0544546 -1.99793  2.29586  1.51927 0.647632  1.56947  1.80501  1.82869  1.86441  1.02010 -1.51554 -0.0283108 0.774669  2.17352  1.21190 0.799884 -2.19687  1.17548 -1.31547 0.136575 -4.92476 -2.97349 -5.28225  1.67775 -6.48973e-07 -5.80585 0.439076
 89:     2124.6684:  1.61393  1.81557  1.49889  2.34139  2.26670  2.28921  2.90368  2.45853 -0.734980 0.131361 -0.920532 -0.597901 -0.601011 -1.92297 -1.95919 -2.14385 -1.05115 -0.656644 -1.35259 -1.61162 -2.13210  7.91345 -0.0344155 -1.95116  2.29588  1.51929 0.647659  1.56949  1.80502  1.82871  1.86443  1.02011 -1.51568 -0.0282858 0.774690  2.17359  1.21194 0.799874 -2.19680  1.17513 -1.31549 0.136477 -4.92475 -2.97349 -5.28232  1.67778 -1.53895e-06 -5.80585 0.439077
 90:     2124.6684:  1.61393  1.81557  1.49892  2.34138  2.26670  2.28919  2.90369  2.45854 -0.734988 0.131373 -0.920524 -0.597945 -0.601002 -1.92302 -1.95923 -2.14390 -1.05116 -0.656615 -1.35270 -1.61146 -2.13215  8.16505 -0.0181694 -1.91890  2.29591  1.51931 0.647690  1.56953  1.80505  1.82875  1.86447  1.02014 -1.51560 -0.0282526 0.774741  2.17371  1.21202 0.799786 -2.19668  1.17467 -1.31547 0.136419 -4.92476 -2.97345 -5.28241  1.67777 -2.47619e-07 -5.80588 0.439078
 91:     2124.6684:  1.61393  1.81557  1.49897  2.34136  2.26671  2.28918  2.90369  2.45857 -0.735001 0.131396 -0.920511 -0.598019 -0.600984 -1.92315 -1.95938 -2.14406 -1.05117 -0.656571 -1.35290 -1.61113 -2.13231  8.41596 0.00882757 -1.88854  2.29601  1.51938 0.647782  1.56963  1.80512  1.82885  1.86456  1.02023 -1.51557 -0.0281648 0.774863  2.17401  1.21223 0.799613 -2.19639  1.17366 -1.31541 0.136248 -4.92475 -2.97335 -5.28263  1.67779 -1.64915e-06 -5.80593 0.439080
 92:     2124.6684:  1.61393  1.81558  1.49902  2.34133  2.26669  2.28915  2.90368  2.45857 -0.735039 0.131393 -0.920544 -0.598114 -0.600986 -1.92328 -1.95951 -2.14421 -1.05123 -0.656559 -1.35308 -1.61113 -2.13246  8.72308 0.0534665 -1.85389  2.29609  1.51946 0.647861  1.56972  1.80521  1.82894  1.86466  1.02032 -1.51521 -0.0280798 0.774976  2.17416  1.21230 0.799458 -2.19581  1.17194 -1.31530 0.136311 -4.92471 -2.97324 -5.28263  1.67772 5.43786e-06 -5.80601 0.439080
 93:     2124.6684:  1.61394  1.81559  1.49899  2.34135  2.26667  2.28914  2.90368  2.45854 -0.735030 0.131375 -0.920562 -0.598079 -0.600992 -1.92323 -1.95946 -2.14415 -1.05122 -0.656599 -1.35272 -1.61169 -2.13240  9.21631 0.0972896 -1.79617  2.29608  1.51948 0.647853  1.56970  1.80518  1.82890  1.86464  1.02030 -1.51520 -0.0280801 0.774930  2.17388  1.21211 0.799598 -2.19546  1.17109 -1.31531 0.136506 -4.92465 -2.97327 -5.28235  1.67769 7.87798e-06 -5.80602 0.439078
 94:     2124.6683:  1.61395  1.81559  1.49897  2.34136  2.26670  2.28918  2.90368  2.45856 -0.735002 0.131385 -0.920527 -0.598026 -0.600976 -1.92324 -1.95947 -2.14415 -1.05117 -0.656597 -1.35261 -1.61151 -2.13241  9.19064 0.0977642 -1.80227  2.29609  1.51947 0.647853  1.56970  1.80514  1.82889  1.86461  1.02028 -1.51563 -0.0280939 0.774913  2.17394  1.21220 0.799680 -2.19564  1.17155 -1.31539 0.136305 -4.92469 -2.97332 -5.28252  1.67777 -3.19552e-06 -5.80597 0.439080
 95:     2124.6683:  1.61394  1.81558  1.49897  2.34135  2.26670  2.28919  2.90367  2.45857 -0.735013 0.131377 -0.920544 -0.598041 -0.600983 -1.92319 -1.95942 -2.14410 -1.05120 -0.656599 -1.35284 -1.61137 -2.13235  9.48032 0.114012 -1.77093  2.29600  1.51938 0.647770  1.56962  1.80508  1.82882  1.86455  1.02021 -1.51557 -0.0281791 0.774870  2.17395  1.21215 0.799643 -2.19583  1.17187 -1.31544 0.136306 -4.92476 -2.97337 -5.28260  1.67775 -1.39155e-06 -5.80597 0.439079
 96:     2124.6683:  1.61393  1.81558  1.49897  2.34135  2.26670  2.28920  2.90368  2.45856 -0.735008 0.131377 -0.920543 -0.598032 -0.600981 -1.92318 -1.95940 -2.14409 -1.05119 -0.656598 -1.35283 -1.61134 -2.13234  9.66125 0.120721 -1.75157  2.29598  1.51936 0.647749  1.56960  1.80507  1.82880  1.86452  1.02019 -1.51555 -0.0281978 0.774847  2.17391  1.21213 0.799620 -2.19592  1.17213 -1.31545 0.136315 -4.92478 -2.97338 -5.28260  1.67775 -1.64544e-06 -5.80597 0.439077
 97:     2124.6683:  1.61393  1.81558  1.49896  2.34135  2.26669  2.28921  2.90368  2.45856 -0.735011 0.131372 -0.920554 -0.598031 -0.600986 -1.92314 -1.95936 -2.14404 -1.05120 -0.656603 -1.35292 -1.61131 -2.13230  9.84234 0.122029 -1.73269  2.29593  1.51932 0.647708  1.56956  1.80505  1.82877  1.86449  1.02016 -1.51546 -0.0282361 0.774819  2.17387  1.21208 0.799575 -2.19607  1.17256 -1.31545 0.136359 -4.92479 -2.97340 -5.28258  1.67773 8.53650e-07 -5.80597 0.439076
 98:     2124.6683:  1.61392  1.81558  1.49895  2.34136  2.26670  2.28922  2.90369  2.45855 -0.734995 0.131371 -0.920559 -0.597997 -0.600987 -1.92304 -1.95926 -2.14394 -1.05120 -0.656604 -1.35307 -1.61114 -2.13219  10.4268 0.103561 -1.67334  2.29582  1.51923 0.647606  1.56947  1.80501  1.82869  1.86441  1.02010 -1.51522 -0.0283256 0.774725  2.17372  1.21198 0.799409 -2.19672  1.17453 -1.31546 0.136458 -4.92484 -2.97346 -5.28252  1.67771 4.55797e-06 -5.80595 0.439073
 99:     2124.6683:  1.61392  1.81558  1.49896  2.34135  2.26668  2.28921  2.90369  2.45854 -0.735012 0.131359 -0.920592 -0.598006 -0.601006 -1.92295 -1.95917 -2.14384 -1.05124 -0.656616 -1.35330 -1.61115 -2.13209  10.4006 0.0702555 -1.67824  2.29573  1.51916 0.647522  1.56939  1.80499  1.82863  1.86435  1.02004 -1.51490 -0.0284017 0.774669  2.17364  1.21186 0.799320 -2.19705  1.17553 -1.31544 0.136613 -4.92486 -2.97348 -5.28242  1.67765 1.21959e-05 -5.80594 0.439070
100:     2124.6682:  1.61394  1.81559  1.49894  2.34140  2.26672  2.28921  2.90371  2.45856 -0.734946 0.131400 -0.920513 -0.597903 -0.600969 -1.92300 -1.95922 -2.14389 -1.05113 -0.656607 -1.35285 -1.61109 -2.13214  10.7011 0.0299752 -1.64970  2.29589  1.51930 0.647670  1.56952  1.80505  1.82875  1.86445  1.02014 -1.51549 -0.0282703 0.774737  2.17378  1.21207 0.799344 -2.19717  1.17630 -1.31545 0.136331 -4.92477 -2.97343 -5.28249  1.67780 -3.75414e-06 -5.80586 0.439077
101:     2124.6682:  1.61395  1.81559  1.49894  2.34139  2.26672  2.28920  2.90372  2.45856 -0.734953 0.131397 -0.920516 -0.597898 -0.600976 -1.92298 -1.95920 -2.14387 -1.05113 -0.656618 -1.35282 -1.61125 -2.13212  10.9980 -0.00630293 -1.62156  2.29593  1.51933 0.647702  1.56955  1.80509  1.82878  1.86449  1.02018 -1.51544 -0.0282393 0.774761  2.17380  1.21208 0.799393 -2.19713  1.17637 -1.31541 0.136389 -4.92472 -2.97340 -5.28240  1.67778 -1.01219e-06 -5.80586 0.439078
102:     2124.6682:  1.61396  1.81560  1.49894  2.34140  2.26673  2.28920  2.90371  2.45857 -0.734952 0.131405 -0.920487 -0.597897 -0.600968 -1.92307 -1.95930 -2.14398 -1.05110 -0.656610 -1.35259 -1.61137 -2.13223  11.2929 -0.0577418 -1.59498  2.29607  1.51945 0.647834  1.56967  1.80517  1.82889  1.86460  1.02028 -1.51562 -0.0281143 0.774854  2.17391  1.21222 0.799581 -2.19672  1.17531 -1.31536 0.136331 -4.92464 -2.97333 -5.28238  1.67781 -4.05140e-06 -5.80586 0.439081
103:     2124.6682:  1.61395  1.81560  1.49896  2.34137  2.26671  2.28920  2.90369  2.45857 -0.734995 0.131387 -0.920513 -0.597956 -0.600987 -1.92317 -1.95940 -2.14408 -1.05115 -0.656613 -1.35261 -1.61155 -2.13234  11.4928 -0.105032 -1.57857  2.29612  1.51950 0.647889  1.56973  1.80520  1.82893  1.86466  1.02032 -1.51562 -0.0280649 0.774922  2.17398  1.21225 0.799826 -2.19609  1.17332 -1.31533 0.136379 -4.92462 -2.97328 -5.28238  1.67778 -1.83266e-06 -5.80591 0.439082
104:     2124.6682:  1.61393  1.81560  1.49898  2.34134  2.26669  2.28921  2.90367  2.45856 -0.735036 0.131361 -0.920558 -0.598011 -0.601013 -1.92322 -1.95945 -2.14414 -1.05122 -0.656617 -1.35285 -1.61149 -2.13239  11.7899 -0.141224 -1.55219  2.29604  1.51942 0.647811  1.56966  1.80516  1.82887  1.86460  1.02026 -1.51543 -0.0281390 0.774889  2.17392  1.21216 0.799952 -2.19588  1.17237 -1.31535 0.136487 -4.92469 -2.97330 -5.28242  1.67772 2.64550e-06 -5.80596 0.439079
105:     2124.6682:  1.61392  1.81559  1.49897  2.34133  2.26669  2.28922  2.90366  2.45856 -0.735044 0.131348 -0.920575 -0.598018 -0.601021 -1.92325 -1.95948 -2.14417 -1.05124 -0.656621 -1.35294 -1.61136 -2.13242  11.9061 -0.143432 -1.54268  2.29596  1.51935 0.647735  1.56959  1.80509  1.82880  1.86453  1.02020 -1.51542 -0.0282120 0.774831  2.17382  1.21210 0.800009 -2.19589  1.17211 -1.31540 0.136496 -4.92478 -2.97335 -5.28250  1.67770 1.67560e-06 -5.80599 0.439077
106:     2124.6682:  1.61392  1.81558  1.49895  2.34132  2.26668  2.28925  2.90364  2.45855 -0.735037 0.131328 -0.920617 -0.597972 -0.601039 -1.92323 -1.95946 -2.14414 -1.05125 -0.656675 -1.35302 -1.61132 -2.13240  12.3710 -0.136339 -1.50413  2.29580  1.51920 0.647571  1.56943  1.80492  1.82863  1.86437  1.02003 -1.51569 -0.0283868 0.774702  2.17369  1.21194 0.800056 -2.19597  1.17201 -1.31557 0.136435 -4.92492 -2.97348 -5.28265  1.67771 -7.85332e-06 -5.80598 0.439075
107:     2124.6682:  1.61394  1.81558  1.49890  2.34136  2.26670  2.28924  2.90366  2.45855 -0.734961 0.131346 -0.920612 -0.597837 -0.601024 -1.92310 -1.95932 -2.14400 -1.05119 -0.656739 -1.35290 -1.61126 -2.13225  13.0072 -0.0318990 -1.45458  2.29563  1.51905 0.647402  1.56926  1.80474  1.82846  1.86419  1.01986 -1.51604 -0.0285624 0.774527  2.17349  1.21179 0.799775 -2.19659  1.17381 -1.31575 0.136291 -4.92504 -2.97363 -5.28276  1.67777 -2.15036e-05 -5.80592 0.439077
108:     2124.6682:  1.61394  1.81558  1.49891  2.34136  2.26670  2.28923  2.90367  2.45855 -0.734960 0.131353 -0.920599 -0.597845 -0.601018 -1.92310 -1.95933 -2.14400 -1.05118 -0.656725 -1.35288 -1.61126 -2.13226  13.1394 -0.0213436 -1.44400  2.29567  1.51908 0.647438  1.56930  1.80478  1.82849  1.86422  1.01990 -1.51597 -0.0285234 0.774553  2.17351  1.21182 0.799748 -2.19659  1.17389 -1.31571 0.136295 -4.92501 -2.97360 -5.28273  1.67777 -1.92412e-05 -5.80592 0.439079
109:     2124.6682:  1.61396  1.81560  1.49899  2.34139  2.26671  2.28915  2.90374  2.45857 -0.734964 0.131421 -0.920479 -0.597956 -0.600961 -1.92310 -1.95932 -2.14401 -1.05111 -0.656580 -1.35269 -1.61135 -2.13226  13.6793 0.0785392 -1.40332  2.29606  1.51944 0.647835  1.56968  1.80520  1.82891  1.86462  1.02030 -1.51531 -0.0280998 0.774877  2.17394  1.21221 0.799460 -2.19654  1.17457 -1.31532 0.136343 -4.92466 -2.97330 -5.28239  1.67776 3.19590e-06 -5.80593 0.439090
110:     2124.6682:  1.61396  1.81560  1.49901  2.34139  2.26671  2.28916  2.90374  2.45857 -0.734985 0.131428 -0.920465 -0.598014 -0.600953 -1.92310 -1.95933 -2.14401 -1.05112 -0.656536 -1.35270 -1.61141 -2.13226  13.6620 0.0912435 -1.40579  2.29618  1.51955 0.647956  1.56979  1.80532  1.82903  1.86474  1.02042 -1.51515 -0.0279748 0.774992  2.17409  1.21232 0.799451 -2.19637  1.17427 -1.31520 0.136404 -4.92454 -2.97321 -5.28229  1.67775 1.05233e-05 -5.80593 0.439085
111:     2124.6682:  1.61396  1.81560  1.49900  2.34138  2.26671  2.28917  2.90372  2.45857 -0.735002 0.131416 -0.920495 -0.598044 -0.600962 -1.92308 -1.95930 -2.14399 -1.05117 -0.656536 -1.35279 -1.61148 -2.13224  13.8416 0.102397 -1.39247  2.29618  1.51955 0.647951  1.56979  1.80531  1.82902  1.86473  1.02040 -1.51522 -0.0279874 0.775014  2.17413  1.21229 0.799479 -2.19620  1.17373 -1.31521 0.136452 -4.92453 -2.97322 -5.28229  1.67774 1.12035e-05 -5.80592 0.439077
112:     2124.6682:  1.61395  1.81560  1.49899  2.34137  2.26670  2.28919  2.90369  2.45857 -0.735013 0.131394 -0.920529 -0.598062 -0.600970 -1.92310 -1.95933 -2.14401 -1.05120 -0.656544 -1.35284 -1.61144 -2.13226  14.1652 0.115663 -1.36877  2.29612  1.51951 0.647892  1.56974  1.80524  1.82895  1.86467  1.02034 -1.51529 -0.0280485 0.774978  2.17404  1.21222 0.799579 -2.19597  1.17284 -1.31527 0.136499 -4.92459 -2.97327 -5.28235  1.67773 1.02572e-05 -5.80594 0.439072
113:     2124.6682:  1.61394  1.81559  1.49896  2.34135  2.26668  2.28922  2.90365  2.45856 -0.735031 0.131355 -0.920602 -0.598052 -0.601001 -1.92312 -1.95935 -2.14402 -1.05127 -0.656602 -1.35301 -1.61143 -2.13228  14.4221 0.0982295 -1.35062  2.29594  1.51934 0.647708  1.56956  1.80504  1.82876  1.86449  1.02015 -1.51556 -0.0282461 0.774851  2.17387  1.21202 0.799746 -2.19577  1.17175 -1.31545 0.136502 -4.92475 -2.97341 -5.28253  1.67771 1.46461e-06 -5.80596 0.439066
114:     2124.6681:  1.61393  1.81558  1.49892  2.34132  2.26667  2.28925  2.90361  2.45854 -0.735033 0.131312 -0.920671 -0.597996 -0.601040 -1.92319 -1.95942 -2.14409 -1.05131 -0.656688 -1.35312 -1.61132 -2.13235  14.6507 0.0374031 -1.33549  2.29567  1.51910 0.647445  1.56932  1.80477  1.82849  1.86423  1.01989 -1.51587 -0.0285188 0.774630  2.17355  1.21178 0.800004 -2.19566  1.17073 -1.31570 0.136466 -4.92502 -2.97359 -5.28279  1.67770 -1.17589e-05 -5.80601 0.439064
115:     2124.6681:  1.61393  1.81558  1.49893  2.34132  2.26667  2.28924  2.90362  2.45854 -0.735029 0.131317 -0.920657 -0.597976 -0.601046 -1.92323 -1.95946 -2.14413 -1.05129 -0.656699 -1.35309 -1.61128 -2.13239  14.9736 0.0110002 -1.31318  2.29564  1.51907 0.647419  1.56929  1.80475  1.82847  1.86421  1.01987 -1.51584 -0.0285410 0.774594  2.17350  1.21177 0.800048 -2.19572  1.17081 -1.31572 0.136419 -4.92506 -2.97360 -5.28283  1.67769 -1.40164e-05 -5.80603 0.439069
116:     2124.6681:  1.61394  1.81559  1.49898  2.34134  2.26669  2.28919  2.90368  2.45856 -0.735009 0.131369 -0.920574 -0.597948 -0.601027 -1.92322 -1.95945 -2.14414 -1.05120 -0.656667 -1.35296 -1.61134 -2.13239  15.4418 -0.0570735 -1.28230  2.29580  1.51920 0.647580  1.56944  1.80494  1.82865  1.86438  1.02005 -1.51560 -0.0283713 0.774698  2.17374  1.21195 0.799894 -2.19614  1.17248 -1.31556 0.136327 -4.92492 -2.97345 -5.28267  1.67771 -1.04103e-05 -5.80599 0.439082
117:     2124.6681:  1.61395  1.81560  1.49901  2.34138  2.26671  2.28917  2.90373  2.45857 -0.734985 0.131417 -0.920484 -0.597956 -0.600982 -1.92317 -1.95939 -2.14409 -1.05112 -0.656588 -1.35274 -1.61137 -2.13234  15.5282 -0.0796026 -1.27795  2.29607  1.51944 0.647843  1.56969  1.80521  1.82892  1.86464  1.02031 -1.51529 -0.0280941 0.774884  2.17396  1.21224 0.799664 -2.19645  1.17419 -1.31531 0.136359 -4.92467 -2.97327 -5.28239  1.67774 2.40078e-06 -5.80594 0.439086
118:     2124.6681:  1.61397  1.81562  1.49901  2.34141  2.26673  2.28918  2.90374  2.45858 -0.734973 0.131441 -0.920439 -0.597991 -0.600942 -1.92309 -1.95931 -2.14400 -1.05110 -0.656513 -1.35261 -1.61141 -2.13225  15.9438 -0.0827660 -1.25058  2.29629  1.51966 0.648065  1.56990  1.80544  1.82914  1.86484  1.02052 -1.51512 -0.0278654 0.775062  2.17415  1.21246 0.799475 -2.19654  1.17519 -1.31510 0.136472 -4.92444 -2.97314 -5.28214  1.67777 1.56114e-05 -5.80588 0.439081
119:     2124.6681:  1.61396  1.81561  1.49899  2.34140  2.26672  2.28919  2.90373  2.45858 -0.734977 0.131425 -0.920470 -0.598003 -0.600941 -1.92304 -1.95926 -2.14394 -1.05113 -0.656521 -1.35268 -1.61140 -2.13219  16.1126 -0.0603093 -1.23996  2.29624  1.51962 0.648012  1.56985  1.80537  1.82908  1.86479  1.02046 -1.51524 -0.0279260 0.775045  2.17415  1.21235 0.799442 -2.19648  1.17496 -1.31516 0.136484 -4.92446 -2.97319 -5.28220  1.67778 1.24736e-05 -5.80587 0.439078
120:     2124.6681:  1.61395  1.81559  1.49891  2.34137  2.26669  2.28923  2.90366  2.45855 -0.734990 0.131355 -0.920576 -0.598001 -0.600976 -1.92302 -1.95924 -2.14390 -1.05123 -0.656603 -1.35291 -1.61128 -2.13216  16.5313 0.0447074 -1.21484  2.29588  1.51930 0.647652  1.56951  1.80497  1.82869  1.86442  1.02009 -1.51566 -0.0282993 0.774780  2.17375  1.21200 0.799609 -2.19617  1.17305 -1.31552 0.136431 -4.92478 -2.97348 -5.28259  1.67777 -1.92678e-06 -5.80593 0.439071
121:     2124.6681:  1.61395  1.81559  1.49892  2.34137  2.26670  2.28922  2.90366  2.45855 -0.734989 0.131359 -0.920568 -0.597994 -0.600978 -1.92304 -1.95926 -2.14392 -1.05122 -0.656605 -1.35289 -1.61128 -2.13218  16.7294 0.0508704 -1.20252  2.29588  1.51929 0.647647  1.56950  1.80497  1.82869  1.86442  1.02009 -1.51564 -0.0283021 0.774767  2.17373  1.21200 0.799627 -2.19620  1.17307 -1.31552 0.136416 -4.92480 -2.97348 -5.28260  1.67776 -2.09146e-06 -5.80594 0.439073
122:     2124.6681:  1.61394  1.81559  1.49896  2.34137  2.26670  2.28920  2.90369  2.45856 -0.734994 0.131378 -0.920546 -0.597969 -0.600993 -1.92312 -1.95934 -2.14402 -1.05118 -0.656620 -1.35286 -1.61134 -2.13228  17.1258 0.0551705 -1.17880  2.29590  1.51929 0.647665  1.56952  1.80501  1.82873  1.86445  1.02012 -1.51557 -0.0282827 0.774771  2.17385  1.21196 0.799684 -2.19629  1.17328 -1.31549 0.136372 -4.92481 -2.97342 -5.28258  1.67774 -5.47827e-06 -5.80595 0.439079
123:     2124.6681:  1.61395  1.81560  1.49903  2.34137  2.26671  2.28917  2.90372  2.45858 -0.734994 0.131414 -0.920506 -0.597932 -0.601006 -1.92324 -1.95947 -2.14417 -1.05113 -0.656626 -1.35278 -1.61142 -2.13242  17.4679 0.0341866 -1.15934  2.29598  1.51935 0.647760  1.56961  1.80514  1.82885  1.86456  1.02024 -1.51538 -0.0281814 0.774816  2.17394  1.21210 0.799748 -2.19640  1.17371 -1.31538 0.136334 -4.92477 -2.97330 -5.28246  1.67771 -4.14703e-06 -5.80596 0.439086
124:     2124.6681:  1.61396  1.81561  1.49903  2.34137  2.26671  2.28917  2.90372  2.45858 -0.734985 0.131418 -0.920514 -0.597927 -0.600999 -1.92324 -1.95947 -2.14417 -1.05113 -0.656623 -1.35278 -1.61141 -2.13242  17.8637 0.0105433 -1.13703  2.29603  1.51941 0.647810  1.56966  1.80519  1.82889  1.86461  1.02028 -1.51534 -0.0281324 0.774862  2.17394  1.21219 0.799722 -2.19632  1.17373 -1.31533 0.136389 -4.92471 -2.97327 -5.28238  1.67771 -1.42317e-06 -5.80596 0.439084
125:     2124.6681:  1.61395  1.81561  1.49902  2.34137  2.26671  2.28917  2.90372  2.45858 -0.734985 0.131415 -0.920515 -0.597934 -0.600995 -1.92322 -1.95945 -2.14415 -1.05114 -0.656618 -1.35279 -1.61140 -2.13240  17.9914 0.00239098 -1.13009  2.29603  1.51941 0.647810  1.56966  1.80519  1.82889  1.86461  1.02028 -1.51535 -0.0281327 0.774868  2.17396  1.21217 0.799722 -2.19629  1.17368 -1.31533 0.136399 -4.92471 -2.97328 -5.28239  1.67772 -1.34919e-06 -5.80595 0.439083
126:     2124.6681:  1.61395  1.81560  1.49897  2.34138  2.26670  2.28920  2.90369  2.45856 -0.734990 0.131388 -0.920536 -0.597975 -0.600984 -1.92313 -1.95935 -2.14403 -1.05118 -0.656601 -1.35284 -1.61135 -2.13229  18.3109 -0.00808028 -1.11277  2.29598  1.51938 0.647758  1.56961  1.80511  1.82882  1.86454  1.02021 -1.51545 -0.0281859 0.774839  2.17382  1.21218 0.799675 -2.19622  1.17336 -1.31540 0.136408 -4.92473 -2.97336 -5.28246  1.67773 1.74401e-06 -5.80595 0.439078
127:     2124.6681:  1.61395  1.81560  1.49897  2.34137  2.26670  2.28919  2.90369  2.45856 -0.734991 0.131389 -0.920532 -0.597976 -0.600985 -1.92313 -1.95936 -2.14404 -1.05117 -0.656600 -1.35282 -1.61134 -2.13229  18.3142 -0.00465311 -1.11277  2.29598  1.51937 0.647749  1.56960  1.80510  1.82881  1.86454  1.02021 -1.51546 -0.0281944 0.774836  2.17389  1.21207 0.799683 -2.19625  1.17340 -1.31541 0.136420 -4.92473 -2.97336 -5.28248  1.67774 -5.01177e-07 -5.80595 0.439078
  0:     2124.6681:  1.61395  1.81560  1.49897  2.34137  2.26670  2.28919  2.90369  2.45856 -0.734991 0.131389 -0.920532 -0.597976 -0.600985 -1.92313 -1.95936 -2.14404 -1.05117 -0.656600 -1.35282 -1.61134 -2.13229  18.3142 -0.00465311 -1.11277  2.29598  1.51937 0.647749  1.56960  1.80510  1.82881  1.86454  1.02021 -1.51546 -0.0281944 0.774836  2.17389  1.21207 0.799683 -2.19625  1.17340 -1.31541 0.136420 -4.92473 -2.97336 -5.28248  1.67774 -5.01177e-07 -5.80595 0.439078
  1:     2124.6681:  1.61395  1.81560  1.49897  2.34137  2.26670  2.28919  2.90369  2.45856 -0.734991 0.131389 -0.920532 -0.597976 -0.600985 -1.92313 -1.95936 -2.14404 -1.05117 -0.656600 -1.35282 -1.61134 -2.13229  18.3142 -0.00465311 -1.11277  2.29598  1.51937 0.647749  1.56960  1.80510  1.82881  1.86454  1.02021 -1.51546 -0.0281944 0.774836  2.17389  1.21207 0.799683 -2.19625  1.17340 -1.31541 0.136420 -4.92473 -2.97336 -5.28248  1.67774 -5.01177e-07 -5.80595 0.439078

Check bounds for the following parameters:
       Param starting_value     Lower       MLE     Upper final_gradient
24 logkappa1     -0.1053605 -6.397277 -1.112772 -1.112772  -0.0005235711

The following parameters appear to be approaching zero:
          Param starting_value Lower           MLE Upper final_gradient
47 L_epsilon2_z              1  -Inf -5.011771e-07   Inf  -1.052103e-05
Please turn off factor-model variance parameters `L_` that are approaching zero and re-run the model


Error: Please change model structure to avoid problems with parameter estimates and then re-try; see details in `?check_fit`
In addition: Warning messages:
1: In sparseMatrix(i = index.i, j = index.j, x = Aij, dims = c(mesh$n,  :
  'giveCsparse' has been deprecated; setting 'repr = "T"' for you
2: In sparseMatrix(i = index.i, j = index.j, x = Aij, dims = c(mesh$n,  :
  'giveCsparse' has been deprecated; setting 'repr = "T"' for you
3: In sparseMatrix(i = index.i, j = index.j, x = Aij, dims = c(mesh$n,  :
  'giveCsparse' has been deprecated; setting 'repr = "T"' for you

```

Crashes with error: 
Error: Please change model structure to avoid problems with parameter estimates and then re-try; see details in `?check_fit`

There is no file output when it stops with parameters at bounds or 0. 

Tried spring data with everything on at first and 1000 knots. Ran more iterations but still unable to finish. Settings:

```
settings = make_settings( n_x = 1000, 
                          Region = "northwest_atlantic",
                          strata.limits = list('All_areas' = 1:1e5), 
                          purpose = "index2", 
                          bias.correct = FALSE,
                          #use_anisotropy = FALSE,
                          #fine_scale = FALSE,
                          FieldConfig = c(Omega1 = "IID", 
                                          Epsilon1 = "IID", 
                                          Omega2 = "IID", 
                                          Epsilon2 = "IID")
```
and results:
```
Check bounds for the following parameters:
        Param starting_value     Lower       MLE     Upper final_gradient
2  ln_H_input      0.0000000 -5.000000 -5.000000  5.000000    0.112599280
20  logkappa1     -0.1053605 -6.397277 -1.112772 -1.112772   -0.003133263
38  logkappa2     -0.1053605 -6.397277 -6.397277 -1.112772    0.916661889

The following parameters appear to be approaching zero:
          Param starting_value Lower          MLE Upper final_gradient
19 L_epsilon1_z              1  -Inf 2.614913e-05   Inf   9.785198e-08
37 L_epsilon2_z              1  -Inf 2.112385e-08   Inf   1.336896e-06
Please turn off factor-model variance parameters `L_` that are approaching zero and re-run the model

```

turn off anistropy, spring settings:
```
settings = make_settings( n_x = 1000, 
                          Region = "northwest_atlantic",
                          strata.limits = list('All_areas' = 1:1e5), 
                          purpose = "index2", 
                          bias.correct = FALSE,
                          use_anisotropy = FALSE,
                          #fine_scale = FALSE,
                          FieldConfig = c(Omega1 = "IID", 
                                          Epsilon1 = "IID", 
                                          Omega2 = "IID", 
                                          Epsilon2 = "IID")
                         )
                         
```
and results:

```
Check bounds for the following parameters:
       Param starting_value     Lower       MLE     Upper final_gradient
18 logkappa1     -0.1053605 -6.397277 -1.112772 -1.112772  -0.0003071745
36 logkappa2     -0.1053605 -6.397277 -6.397277 -1.112772   0.1456314221

The following parameters appear to be approaching zero:
          Param starting_value Lower           MLE Upper final_gradient
35 L_epsilon2_z              1  -Inf -1.438294e-07   Inf  -9.645067e-06
Please turn off factor-model variance parameters `L_` that are approaching zero and re-run the model
```