---
title: "VAST take 1"
author: "Sarah Gaichas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_fold: hide
link-citations: yes
csl: ices-journal-of-marine-science.csl
bibliography: FishDiet_EcoIndicators.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

library(tidyverse)
library(here)
#library(DT)
#library(pdftools)
#library(patchwork)
#library(ggiraph)

#library(ecodata)
library(VAST)
```

Having built an initial dataset of haul-specific mean bluefish prey weight per stomach for piscivores, now we'll try to get a forage biomass index using VAST.

The approach here is to use exactly what @ng_predator_2021 for herring, but combining all bluefish prey (defined [here](https://sgaichas.github.io/bluefishdiet/PreyAggs.html)) as sampled by all piscivore predators at each station.

In @ng_predator_2021, seasons were modeled separately, so we will start that way as well. They used 100 knots, estimated by k-means clustering of the data, to define the spatial dimensions of each seasonal model. They used a a Poisson-link delta model to estimate expected prey mass per predator stomach.  

Read in data, separate spring and fall, and rename columns for VAST:

```{r}
bluepyagg_stn <- readRDS(here("fhdat/bluepyagg_stn.rds"))

bluepyagg_stn_fall <- bluepyagg_stn %>%
  ungroup() %>%
  filter(season_ng == "FALL") %>%
  mutate(Vessel = "NEFSC",
         AreaSwept_km2 = 0.0384) %>%
  select(Catch_KG = meanbluepywt,
         Year = year,
         Vessel,
         AreaSwept_km2,
         Lat = declat,
         Lon = declon) %>%
  as.data.frame()

bluepyagg_stn_spring <- bluepyagg_stn %>%
  filter(season_ng == "SPRING")%>%
  mutate(Vessel = "NEFSC",
         AreaSwept_km2 = 0.0384) %>%
  select(Catch_KG = meanbluepywt,
         Year = year,
         Vessel,
         AreaSwept_km2,
         Lat = declat,
         Lon = declon)%>%
  as.data.frame()
```

Try the simplest possible index standardization model, fall:

```{r, eval=F}
# modified from https://github.com/James-Thorson-NOAA/VAST/wiki/Index-standardization
# and https://github.com/NOAA-EDAB/neusvast/blob/master/analysis/models/pisc_pesc.R

season <- c("fall")

working_dir <- here::here(sprintf("pyindex/allagg_%s/", season))

if(!dir.exists(working_dir)) {
  dir.create(working_dir)
}

# Make settings (turning off bias.correct to save time for example)
# from NEUSvast
# Options <- c("SD_site_density"          = 0,
#              "SD_site_logdensity"       = 0,
#              "Calculate_Range"          = 1, # Center of gravity
#              "Calculate_evenness"       = 0,
#              "Calculate_effective_area" = 1, # Area occupied
#              "Calculate_Cov_SE"         = 0,
#              "Calculate_Synchrony"      = 1,
#              "Calculate_proportion"     = 1)
# 
# #if(purpose == "index2"){
#     
#     settings<-make_settings( n_x=100, 
#                              Region="northwest_atlantic",
#                              use_anisotropy = FALSE,
#                              Options=Options, 
#                              strata.limits = "EPU",
#                              purpose= "index2",
#                              ObsModel = c(2,1))
#     settings$RhoConfig<-c("Beta1"=2,"Beta2"=0,"Epsilon1"=0,"Epsilon2"=0)
#     
    
settings = make_settings( n_x = 100, 
  Region = "northwest_atlantic", 
  purpose = "index2", 
  bias.correct = FALSE,
  strata.limits = list('All_areas' = 1:1e5)
  )

######## Change settings from defaults
settings$ObsModel_ez = c(1,2) #make_data()
#settings$knot_method = "samples"
#settings$Options[2:4] = FALSE
settings$use_anisotropy = FALSE
#settings$fine_scale = TRUE



# Run model
fit = fit_model( settings = settings, 
  Lat_i = bluepyagg_stn_fall[,'Lat'], 
  Lon_i = bluepyagg_stn_fall[,'Lon'], 
  t_i = bluepyagg_stn_fall[,'Year'], 
  b_i = bluepyagg_stn_fall[,'Catch_KG'],
  a_i = bluepyagg_stn_fall[,'AreaSwept_km2'], 
  working_dir = paste0(working_dir, "/"))

# Plot results
plot( fit )
```

Looks like it is doing iterations, then 

Rmarkdown console output:
```
### Writing output from `fit_model` in directory: /Users/sarah.gaichas/Documents/0_Data/bluefishdiet/pyindex/allagg_fall//

### Making extrapolation-grid
Using strata 1:100000
For the UTM conversion, automatically detected zone 19.
# Reducing extrapolation-grid from 31311 to 2000 cells for Region(s): northwest_atlantic
Loaded from /Users/sarah.gaichas/Documents/0_Data/bluefishdiet/pyindex/allagg_fall///Kmeans_extrapolation-2000.RData

### Making spatial information
Loaded from /Users/sarah.gaichas/Documents/0_Data/bluefishdiet/pyindex/allagg_fall///Kmeans_knots-100.RData

### Making data object
Coercing `b_i` to have units `kg`; I recommend using explicit units, e.g., `as_units(b_i,'kg')`, `as_units(b_i,'count') or `as_units(b_i,unitless)`
Coercing `a_i` to have units `km^2`; I recommend using explicit units, e.g., `as_units(a_i,'km^2')` or `as_units(a_i,unitless)`
FieldConfig_input is:
OverdispersionConfig_input is:
Calculating range shift for stratum #1:

### Making TMB object
make: Nothing to be done for `all'.
List of estimated fixed and random effects:

### Testing model at initial values
No problem detected: All fixed effects have a nonzero gradient

### Estimating parameters
Note that `getReportCovariance=FALSE` causes an error in `TMB::sdreport` when no ADREPORTed variables are present


Check bounds for the following parameters:

The following parameters appear to be approaching zero:
Please turn off factor-model variance parameters `L_` that are approaching zero and re-run the model


Quitting from lines 69-130 (VASTmod1.Rmd) 
Error: Please change model structure to avoid problems with parameter estimates and then re-try; see details in `?check_fit`
In addition: Warning messages:
1: In sparseMatrix(i = index.i, j = index.j, x = Aij, dims = c(mesh$n,  :
  'giveCsparse' has been deprecated; setting 'repr = "T"' for you
2: In sparseMatrix(i = index.i, j = index.j, x = Aij, dims = c(mesh$n,  :
  'giveCsparse' has been deprecated; setting 'repr = "T"' for you
3: In sparseMatrix(i = index.i, j = index.j, x = Aij, dims = c(mesh$n,  :
  'giveCsparse' has been deprecated; setting 'repr = "T"' for you
Execution halted
```
Console output:
```
             Component_1 Component_2
Omega                 -2          -2
Epsilon               -2          -2
Beta                  -2          -2
Epsilon_time          -3          -3
Eta1 Eta2 
  -1   -1 
Note: Using Makevars in /Users/sarah.gaichas/.R/Makevars 
make: Nothing to be done for `all'.
Constructing atomic logspace_sub
Constructing atomic D_lgamma
Constructing atomic D_incpl_gamma_shape
Constructing atomic logspace_sub
Constructing atomic D_lgamma
Constructing atomic D_incpl_gamma_shape
  0:     3407.4426:  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  1.00000  1.00000 -2.71885  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  1.00000  1.00000 -2.71885  1.60944
  1:     2988.5065: 0.0287776 0.0279307 0.0169915 0.0530423 0.0708692 0.165965 0.329559 0.127660 -0.0176126 -0.00226153 -0.0169023 -0.0135198 -0.0138058 -0.0199080 -0.0209304 -0.0255203 -0.0196997 -0.0146035 -0.0200739 -0.0270282 -0.0250568  1.16823  1.07727 -2.96382 0.0490667 0.0242394 0.00565546 0.0463988 0.0419860 0.125744 0.308510 0.0446797 1.00017e-05 0.00235638 0.00297993 0.0127676 0.00436148 0.000628475 -6.59583e-05 0.000247511 -0.000110302 0.00151567 -0.000209251 -0.000172832 -0.000106104  1.34391  1.09188 -3.15321  1.05881
  2:     2501.1694: 0.0591335 0.0580978 0.0344198 0.111077 0.147619 0.339913 0.679330 0.265096 -0.0442621 -0.0117224 -0.0416776 -0.0344067 -0.0353162 -0.0473421 -0.0494569 -0.0601979 -0.0475961 -0.0368626 -0.0486051 -0.0641137 -0.0592634  1.38407  1.21108 -3.35884 0.106145 0.0507856 0.0106324 0.0893566 0.0944839 0.248189 0.525903 0.0868347 -0.00100477 0.00293525 0.00537315 0.0276317 0.00888043 0.00134500 -0.000390339 0.000764769 -0.000865219 0.00235479 -0.000945136 -0.000862512 -0.000475490  1.93960  1.19569 -4.06173 0.429675
  3:     2331.5130: 0.111315 0.113539 0.0641545 0.219284 0.286493 0.622778  1.21968 0.507922 -0.112322 -0.0487853 -0.105366 -0.0900265 -0.0916307 -0.114679 -0.119083 -0.143014 -0.118336 -0.0960748 -0.119771 -0.154060 -0.141634  1.64948  1.61917 -4.21564 0.159565 0.0660777 0.00333952 0.107819 0.147800 0.322039 0.574381 0.0826679 -0.0109713 -0.0124825 0.00346819 0.0447344 0.0100453 0.000636631 -0.00301513 0.000770452 -0.00825663 -0.00413228 -0.00637704 -0.00620860 -0.00319383  2.21113  1.25390 -4.64655 0.801205
  4:     2262.3085: 0.117888 0.122086 0.0686152 0.233913 0.301763 0.644091  1.24414 0.530280 -0.119681 -0.0532438 -0.112795 -0.0963664 -0.0975008 -0.123009 -0.127835 -0.152563 -0.126590 -0.102784 -0.128038 -0.164090 -0.151228  1.65294  1.68911 -4.33227 0.163385 0.0671531 0.00271356 0.108985 0.151690 0.326257 0.575257 0.0820002 -0.0119105 -0.0138322 0.00333291 0.0463415 0.0102224 0.000584144 -0.00326466 0.000794598 -0.00895534 -0.00471479 -0.00689613 -0.00671854 -0.00345365  2.22154  1.25277 -4.66811 0.421890
  5:     2237.5192: 0.134236 0.144124 0.0799996 0.269886 0.338909 0.692729  1.29785 0.582241 -0.137255 -0.0639767 -0.130606 -0.111394 -0.111269 -0.143318 -0.149221 -0.175636 -0.146333 -0.118653 -0.147988 -0.188096 -0.174445  1.65780  1.86138 -4.62546 0.177443 0.0698249 -0.000527003 0.111114 0.167917 0.341834 0.577014 0.0795812 -0.0173856 -0.0205294 0.00245782 0.0539770 0.0111731 0.000271421 -0.00473957 0.00102994 -0.0130640 -0.00803285 -0.00998126 -0.00974566 -0.00499807  2.24848  1.26468 -4.74043 0.586405
  6:     2234.7604: 0.148137 0.161262 0.0894828 0.297609 0.371758 0.750853  1.39772 0.633279 -0.148419 -0.0688153 -0.141800 -0.120503 -0.119760 -0.156716 -0.163364 -0.191393 -0.158969 -0.128198 -0.161020 -0.204353 -0.190164  1.68588  1.94362 -4.78700 0.192643 0.0751583 -0.00153124 0.121354 0.181792 0.373236 0.654154 0.0847485 -0.0202043 -0.0238740 0.00258286 0.0600122 0.0123208 0.000155496 -0.00550754 0.00110113 -0.0152210 -0.00952833 -0.0115970 -0.0113275 -0.00580717  2.24770  1.27796 -4.72068 0.289614
  7:     2215.1979: 0.150342 0.164625 0.0912271 0.302180 0.376681 0.755667  1.40267 0.638931 -0.150546 -0.0701811 -0.143963 -0.122257 -0.121298 -0.159413 -0.166222 -0.194372 -0.161336 -0.129967 -0.163552 -0.207303 -0.193166  1.68464  1.96151 -4.82137 0.196065 0.0755913 -0.00235225 0.121485 0.185984 0.377032 0.654320 0.0844527 -0.0218874 -0.0256288 0.00236455 0.0622777 0.0127467 9.56645e-05 -0.00597142 0.00125248 -0.0164882 -0.0104724 -0.0125747 -0.0122835 -0.00629673  2.25285  1.28304 -4.73772 0.477872
  8:     2209.5349: 0.159423 0.178638 0.0985098 0.321031 0.396671 0.775098  1.42268 0.661997 -0.159256 -0.0757941 -0.152818 -0.129427 -0.127560 -0.170550 -0.178019 -0.206651 -0.171010 -0.137140 -0.173960 -0.219406 -0.205536  1.67883  2.03223 -4.95926 0.208825 0.0781288 -0.00506793 0.123185 0.200301 0.390343 0.654234 0.0825964 -0.0269938 -0.0315906 0.00173765 0.0698392 0.0140470 -0.000103352 -0.00735812 0.00164392 -0.0203097 -0.0133946 -0.0154861 -0.0151348 -0.00775440  2.27447  1.28845 -4.79246 0.402706
  9:     2206.5016: 0.180687 0.203419 0.113189 0.359237 0.448087 0.875372  1.61909 0.743465 -0.172810 -0.0797141 -0.166091 -0.139661 -0.137303 -0.188009 -0.196496 -0.227597 -0.186254 -0.147422 -0.190477 -0.240423 -0.226263  1.73318  2.06105 -5.07434 0.241433 0.0885675 -0.00742966 0.144359 0.230322 0.459798 0.833437 0.0956992 -0.0349208 -0.0395775 0.00205832 0.0849399 0.0175391 -0.000289737 -0.00956343 0.00225907 -0.0263763 -0.0173263 -0.0201583 -0.0196952 -0.0100946  2.23461  1.32135 -4.68378 0.524537
 10:     2199.3551: 0.201903 0.247264 0.136794 0.396629 0.487027 0.839164  1.50180 0.746759 -0.194618 -0.100409 -0.187867 -0.156105 -0.150059 -0.222423 -0.233113 -0.262342 -0.209022 -0.160529 -0.219395 -0.270258 -0.261429  1.57979  2.03893 -5.17981 0.306823 0.0940827 -0.0279710 0.130215 0.309184 0.482751 0.643833 0.0665673 -0.0741054 -0.0828766 -0.00296844 0.137522 0.0282452 -0.00137011 -0.0203183 0.00662258 -0.0556024 -0.0390040 -0.0428131 -0.0418422 -0.0214388  2.19876  1.30011 -4.82471 0.446963
 11:     2193.9869: 0.262328 0.353476 0.197657 0.499828 0.594852 0.811231  1.32275 0.798261 -0.252577 -0.149171 -0.245660 -0.200817 -0.187062 -0.312399 -0.328171 -0.354934 -0.271226 -0.197910 -0.295784 -0.351401 -0.354520  1.21727  1.85225 -5.30958 0.461384 0.108605 -0.0730866 0.107719 0.475175 0.549211 0.387060 0.0309474 -0.178647 -0.186165 -0.0130337 0.269058 0.0595099 -0.00314892 -0.0495598 0.0194936 -0.134020 -0.0931940 -0.104671 -0.102170 -0.0524218  2.18756  1.19151 -5.10225 0.508238
 12:     2181.3747: 0.455768 0.609994 0.353762 0.828000  1.00214  1.34667  2.22488  1.31620 -0.395516 -0.225100 -0.386551 -0.309778 -0.285757 -0.519647 -0.546427 -0.584502 -0.429657 -0.297466 -0.479359 -0.565383 -0.582743  1.02185  1.42113 -5.66208 0.824464 0.182284 -0.137565 0.204434 0.814181  1.01047  1.23358 0.0968665 -0.369689 -0.359349 -0.0218063 0.524245 0.125692 -0.00525615 -0.103704 0.0429878 -0.278508 -0.186528 -0.219604 -0.214089 -0.110000  1.98891  1.12916 -4.68957 0.495439
 13:     2180.0695: 0.456920 0.611563 0.354778 0.829901  1.00413  1.34821  2.22608  1.31820 -0.396329 -0.225451 -0.387392 -0.310431 -0.286337 -0.520920 -0.547739 -0.585884 -0.430605 -0.298105 -0.480459 -0.566638 -0.584119  1.01919  1.41702 -5.66339 0.827116 0.183849 -0.137436 0.206089 0.816091  1.01179  1.23092 0.0986670 -0.370835 -0.360152 -0.0216779 0.526015 0.126369 -0.00518997 -0.104041 0.0432326 -0.279352 -0.186894 -0.220322 -0.214783 -0.110360  1.99627  1.12948 -4.70379 0.452076
 14:     2175.2138: 0.486183 0.651300 0.380567 0.878078  1.05493  1.38808  2.25874  1.36939 -0.417108 -0.234439 -0.408861 -0.327110 -0.301182 -0.553406 -0.581204 -0.621136 -0.454814 -0.314442 -0.508519 -0.598654 -0.619215 0.950533  1.31225 -5.69681 0.893593 0.221192 -0.134671 0.244931 0.864863  1.04529  1.16917 0.144336 -0.402632 -0.381724 -0.0186422 0.572650 0.144345 -0.00348363 -0.113432 0.0499834 -0.302854 -0.197293 -0.240353 -0.234146 -0.120400  2.16394  1.14528 -5.03778 0.487149
 15:     2155.1500: 0.940813  1.24413 0.772834  1.62072  1.85590  2.19528  3.22263  2.27669 -0.739351 -0.363758 -0.741730 -0.587114 -0.536566 -1.05397 -1.09684 -1.16848 -0.832782 -0.570101 -0.942889 -1.09921 -1.16292 -0.0590525 -0.286683 -6.03456  1.53822 0.496865 -0.132918 0.551811  1.33069  1.43050  1.50542 0.606405 -0.880310 -0.668036 0.00704167  1.14411 0.372495 0.0168639 -0.257365 0.147537 -0.661498 -0.362309 -0.549107 -0.532191 -0.275196  2.34321 0.488549 -4.90831 0.485246
 16:     2153.5276:  1.07412  1.41031 0.886553  1.83913  2.08333  2.41646  3.45397  2.52621 -0.822660 -0.386608 -0.829627 -0.654573 -0.598175 -1.18775 -1.23469 -1.31529 -0.932847 -0.637252 -1.05821 -1.23280 -1.30868 -0.360878 -0.768955 -6.15007  1.70727 0.575407 -0.129796 0.642816  1.45020  1.52930  1.59761 0.721043 -1.00711 -0.741043 0.0144174  1.29367 0.432718 0.0224293 -0.295711 0.173530 -0.756661 -0.405165 -0.631375 -0.611578 -0.316443  2.39371 0.325678 -4.87750 0.446987
 17:     2147.5698:  1.14178  1.47053 0.946131  1.94130  2.16325  2.46450  3.40765  2.58115 -0.825355 -0.339674 -0.841500 -0.657285 -0.602662 -1.22021 -1.26747 -1.35304 -0.948098 -0.644487 -1.07970 -1.26064 -1.34583 -0.500176 -0.491457 -5.92664  1.72447 0.674071 -0.0811676 0.786842  1.42480  1.48904  1.52673 0.666216 -1.04200 -0.709337 0.0317753  1.32049 0.458536 0.0304704 -0.309288 0.188367 -0.781628 -0.395585 -0.661057 -0.639489 -0.331362  2.44765 0.370760 -4.91587 0.501127
 18:     2146.1843:  1.14377  1.47241 0.948107  1.94356  2.16439  2.46390  3.40336  2.58099 -0.825378 -0.338180 -0.841821 -0.657306 -0.602731 -1.22119 -1.26842 -1.35415 -0.948488 -0.644648 -1.08034 -1.26143 -1.34693 -0.498742 -0.486654 -5.92182  1.72538 0.676284 -0.0800659 0.789361  1.42485  1.48825  1.52304 0.665717 -1.04291 -0.708673 0.0322345  1.32142 0.459236 0.0306744 -0.309645 0.188738 -0.782296 -0.395371 -0.661837 -0.640223 -0.331754  2.44878 0.370812 -4.91883 0.444636
 19:     2145.7019:  1.15089  1.47798 0.955022  1.95188  2.16785  2.46041  3.38278  2.57859 -0.823838 -0.330519 -0.841587 -0.656104 -0.601914 -1.22297 -1.27009 -1.35635 -0.948381 -0.644122 -1.08099 -1.26248 -1.34909 -0.496212 -0.457771 -5.89913  1.72521 0.685757 -0.0744163 0.801586  1.42112  1.48188  1.50794 0.659109 -1.04497 -0.703547 0.0342920  1.32241 0.461376 0.0315709 -0.310670 0.190093 -0.783742 -0.393438 -0.664114 -0.642324 -0.332900  2.45358 0.377827 -4.92881 0.464860
 20:     2144.8725:  1.16429  1.48688 0.967691  1.96766  2.17301  2.45201  3.33789  2.57151 -0.818951 -0.313361 -0.839413 -0.652282 -0.599103 -1.22409 -1.27091 -1.35816 -0.946285 -0.641764 -1.08007 -1.26215 -1.35083 -0.493267 -0.392750 -5.85381  1.71955 0.703201 -0.0627632 0.825892  1.40910  1.46631  1.48323 0.640894 -1.04658 -0.691120 0.0382622  1.32042 0.464265 0.0332763 -0.311994 0.192326 -0.784754 -0.388578 -0.667117 -0.645026 -0.334415  2.46298 0.392789 -4.94183 0.438228
 21:     2138.0718:  1.35471  1.65161  1.14615  2.17401  2.25064  2.37447  2.93010  2.51999 -0.818815 -0.174537 -0.865530 -0.652501 -0.606418 -1.30340 -1.34843 -1.44918 -0.977909 -0.654478 -1.13290 -1.32742 -1.44105 -0.245251 -0.153306 -5.67920  1.74411 0.829434 0.0219956 0.969047  1.37792  1.40509  1.39775 0.569094 -1.12544 -0.626517 0.0727580  1.37567 0.514792 0.0497169 -0.343618 0.223516 -0.843933 -0.372718 -0.736655 -0.710380 -0.369372  2.55624 0.314576 -4.96891 0.463790
 22:     2137.3922:  1.58022  1.79281  1.35502  2.40237  2.28689  2.14298  2.63975  2.34412 -0.803124 0.0105671 -0.887641 -0.643262 -0.609773 -1.38879 -1.43291 -1.54743 -1.00707 -0.661217 -1.18491 -1.39400 -1.53803 -0.308771 0.0777640 -5.53915  1.77986 0.913349 0.0870605  1.04038  1.35405  1.37115  1.44214 0.561389 -1.21862 -0.577547 0.102363  1.43347 0.560290 0.0646644 -0.380491 0.254095 -0.915962 -0.366317 -0.817783 -0.786808 -0.410146  2.66113 0.176208 -5.00410 0.463485
 23:     2136.5829:  1.80360  1.93776  1.61731  2.52279  2.23693  2.19397  2.89482  2.29563 -0.779544 0.255381 -0.920352 -0.632676 -0.620719 -1.50663 -1.54816 -1.68675 -1.04908 -0.679594 -1.25641 -1.48900 -1.67565 -0.442858 0.177553 -5.42242  1.83416  1.10053 0.204997  1.22609  1.30903  1.34662  1.41249 0.500854 -1.33166 -0.474002 0.155224  1.50091 0.623581 0.0888075 -0.428999 0.296827 -1.00318 -0.338017 -0.924859 -0.887048 -0.463995  2.64942 0.215557 -4.99942 0.410283
 24:     2136.1998:  1.84299  1.93855  1.76389  2.42977  2.30609  2.42506  2.85017  2.59131 -0.715563 0.424061 -0.917853 -0.587960 -0.599389 -1.60088 -1.64043 -1.80061 -1.05381 -0.663068 -1.29345 -1.54680 -1.78785 -0.772374 0.387741 -5.21420  1.85024  1.20808 0.296540  1.28837  1.28226  1.41000  1.48750 0.571293 -1.44146 -0.363383 0.207728  1.53583 0.670294 0.114043 -0.483189 0.338265 -1.09388 -0.302991 -1.04588 -0.999457 -0.524911  2.64277 0.247301 -5.01539 0.494317
 25:     2134.9663:  1.83042  1.96057  1.78956  2.42672  2.42502  2.51876  2.86504  2.72000 -0.703763 0.411243 -0.926255 -0.577059 -0.592679 -1.66349 -1.70318 -1.87268 -1.06607 -0.659368 -1.32539 -1.58893 -1.85953 -0.778418 0.268148 -5.22756  1.89973  1.21948 0.314753  1.25453  1.35521  1.50199  1.55932 0.668264 -1.51353 -0.344514 0.230721  1.58303 0.699482 0.126182 -0.517278 0.361344 -1.15497 -0.297877 -1.12192 -1.07030 -0.563179  2.62146 0.191089 -5.00065 0.422854
 26:     2133.1144:  1.75651  1.96780  1.71107  2.50456  2.59217  2.43593  2.97035  2.61543 -0.656382 0.321471 -0.889382 -0.530018 -0.544294 -1.68074 -1.72036 -1.89529 -1.02868 -0.612788 -1.30788 -1.57533 -1.88219 -0.699719 0.227896 -5.21311  1.92033  1.21541 0.332366  1.24219  1.46862  1.54214  1.54220 0.703620 -1.54861 -0.305828 0.262104  1.59795 0.721761 0.142509 -0.549127 0.385212 -1.19375 -0.269534 -1.19513 -1.13647 -0.600156  2.56749 0.224496 -5.00700 0.443522
 27:     2132.3820:  1.75912  1.98982  1.64812  2.55552  2.38285  2.41494  2.99073  2.55083 -0.617050 0.244673 -0.849629 -0.486538 -0.494832 -1.70163 -1.74213 -1.92015 -0.988350 -0.563487 -1.28820 -1.55779 -1.90733 -0.593342 0.165425 -5.22851  1.98059  1.20044 0.341471  1.22863  1.54608  1.57183  1.57501 0.747643 -1.59244 -0.287291 0.298275  1.64220 0.756883 0.163569 -0.592468 0.418832 -1.24448 -0.243566 -1.29520 -1.22642 -0.650741  2.50542 0.224468 -5.03608 0.476947
 28:     2131.5525:  1.76048  1.94284  1.61201  2.40980  2.30900  2.27185  2.99421  2.50715 -0.590089 0.239118 -0.811155 -0.457048 -0.461577 -1.71813 -1.75901 -1.93932 -0.948744 -0.526356 -1.26258 -1.53178 -1.92669 -0.492902 0.119428 -5.27300  2.03968  1.21322 0.367111  1.27012  1.58691  1.55700  1.59788 0.752500 -1.63228 -0.260393 0.345697  1.70086 0.805907 0.192865 -0.647441 0.463989 -1.29777 -0.207466 -1.42331 -1.33996 -0.715623  2.44053 0.217274 -5.07121 0.444222
 29:     2131.1766:  1.72396  1.87489  1.59180  2.34467  2.33435  2.39042  2.94838  2.37970 -0.595741 0.236635 -0.799964 -0.461030 -0.464619 -1.74960 -1.79058 -1.97438 -0.937312 -0.524787 -1.25686 -1.52662 -1.96169 -0.460967 0.0530906 -5.30230  2.09886  1.23830 0.396264  1.32149  1.61171  1.62138  1.64085 0.771885 -1.67951 -0.238181 0.394380  1.77178 0.860109 0.225160 -0.710664 0.513949 -1.35858 -0.174771 -1.57092 -1.47014 -0.790440  2.39238 0.157236 -5.09561 0.439596
 30:     2130.7476:  1.66500  1.82019  1.57590  2.37304  2.36612  2.38602  2.94316  2.47459 -0.621577 0.225335 -0.806399 -0.486237 -0.490466 -1.78770 -1.82847 -2.01667 -0.943749 -0.546557 -1.26207 -1.53279 -2.00381 -0.438315 -0.0301241 -5.32103  2.15074  1.28232 0.433115  1.39058  1.62315  1.68284  1.69406 0.827425 -1.72492 -0.211406 0.445753  1.84549 0.917210 0.260995 -0.780531 0.568476 -1.41968 -0.139785 -1.73493 -1.61344 -0.873683  2.34102 0.0985041 -5.11482 0.477353
 31:     2130.0011:  1.58531  1.80840  1.53356  2.48853  2.36727  2.40786  2.94560  2.53218 -0.654497 0.182870 -0.822362 -0.521778 -0.527930 -1.81303 -1.85304 -2.04430 -0.958736 -0.580977 -1.26519 -1.53453 -2.03118 -0.447436 -0.0715066 -5.31921  2.16935  1.33745 0.477000  1.44863  1.64311  1.72702  1.73843 0.892072 -1.74497 -0.171398 0.497550  1.90262 0.969350 0.300508 -0.853841 0.624859 -1.46330 -0.0974626 -1.90998 -1.76226 -0.962857  2.28737 0.0634514 -5.13295 0.437983
 32:     2129.4140:  1.63929  1.89383  1.53118  2.36849  2.37813  2.38181  2.93464  2.51986 -0.690971 0.154948 -0.853243 -0.559945 -0.565172 -1.83162 -1.87110 -2.06311 -0.988325 -0.620052 -1.27675 -1.54324 -2.04997 -0.445551 -0.105839 -5.32058  2.17533  1.40431 0.528812  1.44777  1.70254  1.72147  1.78796 0.910977 -1.72463 -0.122684 0.545481  1.94510  1.01442 0.343707 -0.930473 0.682220 -1.47542 -0.0517264 -2.09846 -1.91414 -1.05961  2.23518 0.0301346 -5.16845 0.435581
 33:     2128.8280:  1.65150  1.86211  1.52785  2.32126  2.33437  2.33728  2.92093  2.48574 -0.713375 0.156497 -0.878029 -0.584535 -0.589002 -1.83775 -1.87642 -2.06781 -1.01111 -0.646034 -1.28229 -1.54426 -2.05472 -0.443526 -0.0929646 -5.30904  2.17686  1.44903 0.582099  1.47517  1.72680  1.78648  1.75889 0.930656 -1.67292 -0.0639287 0.596711  1.97383  1.05662 0.394225 -1.01653 0.745392 -1.46325 0.00289461 -2.31527 -2.08052 -1.17170  2.18522 -0.00743053 -5.20838 0.448834
 34:     2128.2835:  1.61589  1.75819  1.51868  2.32198  2.29065  2.31204  2.90121  2.43247 -0.748698 0.150426 -0.927175 -0.618660 -0.619708 -1.86245 -1.89982 -2.08987 -1.05814 -0.681508 -1.31105 -1.56674 -2.07712 -0.446367 -0.0406095 -5.22583  2.25414  1.52634 0.665007  1.57500  1.79629  1.69890  1.90398 0.951339 -1.57540 0.0187150 0.695064  2.05116  1.14300 0.495460 -1.19556 0.873927 -1.43272 0.0967247 -2.77240 -2.41887 -1.40958  2.02049 -0.00731274 -5.32880 0.464019
 35:     2126.9699:  1.61111  1.78833  1.49830  2.22046  2.25279  2.25644  2.87027  2.39201 -0.750427 0.163746 -0.978905 -0.616645 -0.620110 -1.91605 -1.95021 -2.14137 -1.10980 -0.683191 -1.37427 -1.62678 -2.12868 -0.455201 0.0748634 -5.03044  2.45755  1.62258 0.790587  1.71987  1.83794  1.95945  2.10092  1.08577 -1.38531 0.156599 0.883898  2.18781  1.30055 0.704216 -1.57284  1.13177 -1.34200 0.267871 -3.76055 -3.09555 -1.93103  1.68917 0.0834092 -5.52320 0.453904
 36:     2126.3817:  1.62841  1.80429  1.48319  2.19614  2.22168  2.26351  2.85341  2.39316 -0.743997 0.145349 -0.983083 -0.609060 -0.614316 -1.93411 -1.96698 -2.15814 -1.11334 -0.674520 -1.39331 -1.64475 -2.14540 -0.490167 0.115122 -4.98463  2.51959  1.67830 0.857438  1.76481  1.97635  1.94419  2.07618  1.22668 -1.28660 0.228061 0.973744  2.25058  1.37497 0.807736 -1.75555  1.25485 -1.27508 0.353416 -4.25291 -3.37188 -2.20263  1.59918 0.00773965 -5.59502 0.436617
 37:     2126.1004:  1.63247  1.84885  1.47892  2.25010  2.22120  2.26864  2.86283  2.42520 -0.757723 0.0944342 -0.976431 -0.620147 -0.622524 -1.94592 -1.97905 -2.16895 -1.10722 -0.680995 -1.40083 -1.65322 -2.15640 -0.517434 0.101490 -4.94737  2.51594  1.72729 0.876179  1.75555  2.04206  1.99592  2.08619  1.14449 -1.26008 0.233428  1.00378  2.29538  1.40611 0.852145 -1.83173  1.30528 -1.23497 0.372371 -4.46880 -3.39390 -2.34883  1.61575 -0.0507729 -5.61310 0.438210
 38:     2125.7992:  1.64248  1.87329  1.49781  2.31732  2.25089  2.27865  2.89184  2.43657 -0.783266 0.0722910 -0.966410 -0.641531 -0.638913 -1.96365 -1.99838 -2.18593 -1.09844 -0.696364 -1.40749 -1.66269 -2.17382 -0.506566 0.0765927 -4.92621  2.49746  1.75524 0.873656  1.72435  2.00705  2.02583  2.08346  1.21103 -1.26116 0.208283  1.01624  2.35272  1.42873 0.892368 -1.89891  1.34915 -1.19217 0.365781 -4.66343 -3.29935 -2.52474  1.66991 -0.0115538 -5.59475 0.446434
 39:     2125.5420:  1.60271  1.78757  1.49892  2.30488  2.25917  2.26095  2.89330  2.44043 -0.781910 0.118447 -0.950237 -0.639280 -0.634167 -1.97995 -2.01657 -2.20210 -1.08319 -0.693062 -1.40265 -1.66121 -2.19053 -0.501134 0.0594529 -4.92690  2.48480  1.72949 0.860049  1.74198  2.00342  2.03344  2.05177  1.18049 -1.29035 0.184157  1.01204  2.39703  1.43865 0.924098 -1.94797  1.38171 -1.16110 0.343399 -4.79172 -3.12336 -2.71795  1.75206 -0.0147706 -5.57799 0.442895
 40:     2125.4072:  1.57073  1.83506  1.43514  2.30128  2.24948  2.26338  2.88127  2.44196 -0.753606 0.0974191 -0.945660 -0.619268 -0.621391 -1.98028 -2.01768 -2.20205 -1.07770 -0.679517 -1.38605 -1.64584 -2.19070 -0.533654 0.0787670 -4.90873  2.48052  1.69372 0.844171  1.79522  1.97109  2.02346  2.03529  1.18379 -1.31936 0.186838 0.989495  2.38951  1.42351 0.951769 -1.98649  1.40546 -1.13562 0.320201 -4.85699 -2.94861 -2.96075  1.78304 -0.0160704 -5.58982 0.442208
 41:     2125.2630:  1.61795  1.81547  1.45133  2.32483  2.25464  2.28011  2.88663  2.45775 -0.738040 0.0817191 -0.947550 -0.609370 -0.617650 -1.97741 -2.01520 -2.19928 -1.07888 -0.674242 -1.37272 -1.63374 -2.18797 -0.535807 0.0879598 -4.87104  2.48407  1.68054 0.838708  1.78013  1.98866  2.03257  2.03752  1.19650 -1.34318 0.193052 0.964490  2.36843  1.40343 0.979986 -2.02539  1.42749 -1.11459 0.302857 -4.90845 -2.80061 -3.24248  1.77113 -0.00179661 -5.61834 0.438140
 42:     2125.1478:  1.57632  1.83025  1.49718  2.33869  2.25021  2.28602  2.89025  2.45807 -0.737311 0.116647 -0.942882 -0.606106 -0.613028 -1.97315 -2.01124 -2.19511 -1.07434 -0.668769 -1.36438 -1.62643 -2.18383 -0.530980 0.0900855 -4.84210  2.48667  1.69623 0.840165  1.74988  2.00103  2.03491  2.04015  1.21310 -1.35645 0.188810 0.945945  2.35428  1.39068  1.00749 -2.06343  1.44808 -1.09827 0.295208 -4.95067 -2.69698 -3.54360  1.74348 -0.0188806 -5.66104 0.437815
 43:     2124.9493:  1.61404  1.78580  1.45374  2.36209  2.27606  2.29690  2.90659  2.45907 -0.770608 0.155896 -0.907472 -0.613295 -0.596680 -1.95946 -1.99850 -2.18143 -1.04178 -0.653142 -1.35893 -1.62296 -2.17021 -0.549912 0.0931127 -4.75927  2.50907  1.74896 0.839570  1.76952  1.97655  2.03139  2.04935  1.23529 -1.36530 0.131174 0.918954  2.36184  1.38862  1.08087 -2.16318  1.49818 -1.07289 0.299756 -5.01420 -2.52151 -4.51095  1.66108 -0.0616404 -5.77772 0.440342
 44:     2124.8539:  1.59911  1.77561  1.47243  2.36053  2.27108  2.29777  2.90214  2.45618 -0.774974 0.134776 -0.898514 -0.614934 -0.595429 -1.95210 -1.99145 -2.17395 -1.03365 -0.652429 -1.35884 -1.62312 -2.16265 -0.574248 0.107876 -4.71552  2.50100  1.74276 0.840871  1.76690  2.00323  2.02318  2.04452  1.22801 -1.36277 0.116856 0.913167  2.37165  1.39263  1.10422 -2.19039  1.50922 -1.06909 0.306009 -4.99658 -2.46650 -4.92575  1.66049 0.00619153 -5.79754 0.439421
 45:     2124.8387:  1.59897  1.78421  1.56065  2.34982  2.27617  2.29445  2.90213  2.45297 -0.717647 0.0732957 -0.931015 -0.597340 -0.613150 -1.93996 -1.97876 -2.16171 -1.06190 -0.671886 -1.36257 -1.62453 -2.15026 -0.595612 0.106965 -4.68669  2.44586  1.63303 0.822131  1.74290  1.93563  1.98895  2.02177  1.19632 -1.34764 0.165732 0.925168  2.37611  1.39360  1.08783 -2.14532  1.47241 -1.09146 0.314247 -4.80659 -2.48657 -5.23808  1.68961 -0.0302516 -5.83064 0.436991
 46:     2124.7835:  1.61069  1.80586  1.51516  2.35402  2.27456  2.30048  2.90442  2.46171 -0.705180 0.135485 -0.953686 -0.596062 -0.622839 -1.93827 -1.97636 -2.16031 -1.08281 -0.680986 -1.36650 -1.62717 -2.14861 -0.596898 0.107060 -4.67381  2.42557  1.61349 0.798453  1.70558  1.95725  1.98513  2.02074  1.18580 -1.34714 0.176138 0.933795  2.36641  1.38657  1.06163 -2.10113  1.43837 -1.11471 0.309702 -4.70618 -2.54986 -5.23295  1.70628 -0.0118803 -5.82231 0.437197
 47:     2124.7297:  1.60198  1.80654  1.50193  2.32402  2.25809  2.28569  2.89043  2.45477 -0.753769 0.114032 -0.944545 -0.606425 -0.601369 -1.94374 -1.98052 -2.16656 -1.07529 -0.656038 -1.36458 -1.62417 -2.15428 -0.603389 0.0950073 -4.68649  2.46309  1.72057 0.782364  1.74467  1.98332  2.00555  2.04323  1.19483 -1.36554 0.114263 0.943979  2.33086  1.36477  1.01054 -2.04138  1.38508 -1.15556 0.285184 -4.67780 -2.73868 -5.01892  1.69455 0.00978782 -5.79150 0.438504
 48:     2124.7115:  1.60151  1.81322  1.48682  2.32762  2.25840  2.28274  2.89365  2.45104 -0.763538 0.118931 -0.930047 -0.618000 -0.611876 -1.94733 -1.98418 -2.16985 -1.06268 -0.668506 -1.36715 -1.62682 -2.15755 -0.602225 0.0879559 -4.67731  2.49027  1.69208 0.829159  1.74678  1.98092  2.00311  2.03949  1.18977 -1.35987 0.134907 0.946028  2.34014  1.37334  1.00571 -2.04576  1.38066 -1.15145 0.290692 -4.73905 -2.79274 -5.05346  1.66960 0.0112879 -5.80452 0.438872
 49:     2124.7028:  1.60449  1.80871  1.48143  2.32941  2.25995  2.28415  2.89513  2.45068 -0.743602 0.120241 -0.928885 -0.607661 -0.609973 -1.94901 -1.98605 -2.17118 -1.06119 -0.667807 -1.37041 -1.63030 -2.15903 -0.607337 0.0872181 -4.66027  2.44950  1.69374 0.824168  1.74003  1.97512  1.99998  2.03482  1.19035 -1.35376 0.150193 0.941749  2.35340  1.38325  1.00055 -2.04915  1.37463 -1.14735 0.300441 -4.77849 -2.81676 -5.14574  1.65930 0.00395844 -5.82185 0.439246
 50:     2124.6975:  1.61678  1.81794  1.49837  2.34028  2.26988  2.29156  2.90297  2.45704 -0.739136 0.131379 -0.934143 -0.602883 -0.605418 -1.94142 -1.97858 -2.16292 -1.06464 -0.661573 -1.36632 -1.62575 -2.15092 -0.618137 0.0811066 -4.63683  2.45723  1.66807 0.787205  1.72159  1.95208  1.97885  2.01015  1.17158 -1.34827 0.129980 0.927951  2.34680  1.37930 0.978576 -2.03142  1.34895 -1.14632 0.304186 -4.76318 -2.82517 -5.21822  1.67512 -0.00642212 -5.82278 0.439309
 51:     2124.6884:  1.61295  1.81321  1.49696  2.33865  2.26514  2.28815  2.89982  2.45384 -0.749405 0.122735 -0.927570 -0.611063 -0.610971 -1.93485 -1.97186 -2.15635 -1.05934 -0.668775 -1.36032 -1.61983 -2.14440 -0.631623 0.0736174 -4.61898  2.42212  1.64030 0.798379  1.70082  1.93577  1.96560  1.99738  1.15894 -1.36969 0.105005 0.912281  2.32263  1.35613 0.946768 -2.01078  1.31520 -1.16292 0.281616 -4.74252 -2.84627 -5.18985  1.67595 -0.00711323 -5.82724 0.438828
 52:     2124.6772:  1.60618  1.80788  1.49767  2.33466  2.26343  2.28461  2.89759  2.45372 -0.737154 0.115409 -0.928744 -0.608072 -0.617235 -1.93243 -1.96938 -2.15426 -1.06112 -0.673823 -1.36114 -1.62081 -2.14227 -0.648679 0.0605696 -4.58544  2.41037  1.62542 0.772820  1.68839  1.92176  1.95154  1.98543  1.14347 -1.40372 0.105619 0.893663  2.29489  1.32585 0.911071 -2.00801  1.27862 -1.19047 0.246843 -4.77159 -2.88413 -5.17215  1.66262 8.66938e-06 -5.83422 0.439091
 53:     2124.6615:  1.60826  1.81279  1.49469  2.33658  2.25801  2.27960  2.89788  2.44795 -0.747510 0.118161 -0.933481 -0.602668 -0.597383 -1.92711 -1.96408 -2.14871 -1.06383 -0.654706 -1.36449 -1.62300 -2.13676 -0.698838 0.0386102 -4.47989  2.34935  1.59669 0.726256  1.63804  1.86033  1.89494  1.93223  1.08487 -1.45985 0.0536394 0.840540  2.23379  1.26373 0.829172 -2.02922  1.19436 -1.25401 0.181758 -4.86338 -2.94555 -5.19458  1.66053 0.0115766 -5.84676 0.437605
 54:     2124.6483:  1.61289  1.81436  1.50319  2.33037  2.26387  2.28688  2.89785  2.46032 -0.739162 0.128494 -0.916088 -0.595902 -0.592588 -1.92346 -1.96007 -2.14540 -1.04709 -0.650128 -1.35850 -1.61737 -2.13346 -0.756107 0.0216677 -4.36421  2.29999  1.53430 0.676565  1.59017  1.81887  1.84356  1.88110  1.03559 -1.51365 -0.0214379 0.784929  2.17445  1.20968 0.759025 -2.07440  1.12383 -1.31730 0.130588 -4.95880 -2.99209 -5.24656  1.65799 0.00928322 -5.86197 0.439610
 55:     2124.6411:  1.60552  1.80564  1.48635  2.33433  2.26184  2.28302  2.89863  2.45249 -0.724236 0.122301 -0.905770 -0.607169 -0.628298 -1.91703 -1.95330 -2.13816 -1.03975 -0.681374 -1.34115 -1.60036 -2.12638 -0.823152 -0.00148112 -4.25909  2.26462  1.49383 0.586012  1.51212  1.75335  1.78105  1.81423 0.976976 -1.56897 -0.0694192 0.718639  2.12267  1.16172 0.706454 -2.15140  1.07267 -1.37043 0.0885008 -5.00020 -3.01124 -5.29194  1.67282 -0.00269435 -5.86463 0.439074
 56:     2124.6384:  1.61358  1.81923  1.50323  2.35039  2.27539  2.29036  2.91162  2.45793 -0.751560 0.138981 -0.939496 -0.606483 -0.602114 -1.92260 -1.95901 -2.14283 -1.06963 -0.657304 -1.34984 -1.60858 -2.13122 -0.867276 -0.0233716 -4.20267  2.22633  1.43440 0.555710  1.52917  1.74841  1.76897  1.79810 0.965262 -1.60150 -0.0828273 0.688422  2.11359  1.14277 0.704158 -2.23187  1.07389 -1.39155 0.0638943 -5.00234 -3.02298 -5.32373  1.67305 -0.00798539 -5.85711 0.438731
 57:     2124.6293:  1.61319  1.81568  1.50132  2.34747  2.27718  2.29272  2.90860  2.46246 -0.748599 0.136200 -0.944508 -0.595782 -0.583713 -1.92804 -1.96450 -2.14835 -1.07251 -0.641118 -1.35990 -1.61844 -2.13676 -0.879897 -0.0184104 -4.20106  2.23695  1.44434 0.583758  1.50877  1.73683  1.76694  1.79931 0.962668 -1.59558 -0.0773273 0.696871  2.12314  1.14878 0.717588 -2.25111  1.08851 -1.38449 0.0662562 -4.99513 -3.02568 -5.32775  1.67604 -0.00368996 -5.85240 0.438942
 58:     2124.6223:  1.61689  1.81734  1.50266  2.34136  2.26747  2.28968  2.90272  2.45850 -0.730564 0.134987 -0.923663 -0.597866 -0.604372 -1.93092 -1.96743 -2.15163 -1.05305 -0.660456 -1.36509 -1.62360 -2.14000 -0.889715 -0.0104342 -4.19215  2.23566  1.46011 0.594224  1.51274  1.73934  1.76850  1.80373 0.962071 -1.57906 -0.0948348 0.708056  2.11959  1.14794 0.725014 -2.25945  1.09545 -1.37615 0.0665341 -4.99534 -3.03447 -5.33830  1.67519 0.00321465 -5.84829 0.438803
 59:     2124.6196:  1.61342  1.81373  1.49710  2.33659  2.26253  2.28671  2.89985  2.45584 -0.744004 0.128111 -0.917782 -0.603323 -0.602366 -1.92945 -1.96582 -2.15059 -1.04966 -0.658410 -1.35640 -1.61539 -2.13890 -0.912613 -0.0113717 -4.16262  2.22734  1.45105 0.576127  1.49821  1.73387  1.76000  1.79484 0.953582 -1.58464 -0.0936757 0.700968  2.10483  1.13884 0.718996 -2.27659  1.08939 -1.38351 0.0616019 -5.00394 -3.04561 -5.34977  1.67133 0.00239358 -5.84835 0.439092
 60:     2124.6156:  1.61032  1.81303  1.49299  2.33679  2.26518  2.28658  2.90216  2.45626 -0.733643 0.124908 -0.925469 -0.598688 -0.603062 -1.92576 -1.96200 -2.14727 -1.05655 -0.659099 -1.34570 -1.60456 -2.13551 -0.972045 -0.0204472 -4.08868  2.21171  1.43575 0.562270  1.47768  1.71718  1.74259  1.77555 0.935859 -1.61063 -0.116752 0.678082  2.07970  1.11808 0.705129 -2.32017  1.07644 -1.40750 0.0442933 -5.01837 -3.07279 -5.36574  1.66814 -0.000747315 -5.83751 0.439031
 61:     2124.6119:  1.61303  1.81597  1.49880  2.33969  2.26980  2.28931  2.90375  2.45901 -0.740401 0.130074 -0.916426 -0.602661 -0.604488 -1.92280 -1.95894 -2.14410 -1.04655 -0.659812 -1.35365 -1.61180 -2.13237 -1.05634 -0.0252932 -3.99807  2.19360  1.41980 0.542912  1.46724  1.69921  1.72851  1.76170 0.921353 -1.63229 -0.116088 0.661491  2.07024  1.10520 0.701200 -2.36072  1.07412 -1.42360 0.0279332 -5.02385 -3.09476 -5.37403  1.67398 -0.00182853 -5.81242 0.438756
 62:     2124.6091:  1.61286  1.81308  1.49814  2.33970  2.26332  2.28590  2.90143  2.45493 -0.736594 0.127711 -0.925665 -0.599151 -0.601558 -1.92257 -1.95859 -2.14347 -1.05793 -0.658281 -1.35972 -1.61847 -2.13178 -1.10659 -0.0213643 -3.95678  2.19982  1.41657 0.551461  1.47518  1.71006  1.73478  1.76867 0.927497 -1.61646 -0.120251 0.670686  2.07706  1.11231 0.713998 -2.34822  1.08752 -1.40944 0.0320881 -5.01813 -3.08267 -5.38590  1.67889 -0.00134161 -5.79313 0.439246
 63:     2124.6065:  1.61344  1.81544  1.49950  2.33926  2.26558  2.28855  2.90253  2.45718 -0.736630 0.129643 -0.926281 -0.600525 -0.603641 -1.92380 -1.96000 -2.14460 -1.05518 -0.658320 -1.35065 -1.60939 -2.13294 -1.14189 -0.00842032 -3.92610  2.21097  1.43227 0.566566  1.48661  1.72103  1.74731  1.78159 0.939323 -1.59958 -0.112763 0.685979  2.08645  1.12404 0.722083 -2.30363  1.09580 -1.39495 0.0464951 -5.01473 -3.06557 -5.39877  1.67656 0.000828951 -5.78594 0.438872
 64:     2124.6039:  1.61550  1.81721  1.50028  2.34013  2.26722  2.28970  2.90394  2.45843 -0.733066 0.130987 -0.916406 -0.594905 -0.598847 -1.92447 -1.96083 -2.14537 -1.04941 -0.659281 -1.35330 -1.61177 -2.13373 -1.20412 0.0100781 -3.86249  2.22307  1.44811 0.580374  1.49528  1.73258  1.75718  1.79086 0.948963 -1.59221 -0.0971771 0.695602  2.09395  1.13364 0.720342 -2.23796  1.09453 -1.38428 0.0598648 -5.00986 -3.04506 -5.38194  1.68057 0.000731869 -5.77667 0.438930
 65:     2124.6017:  1.61308  1.81482  1.49767  2.33891  2.26656  2.28819  2.90190  2.45771 -0.734647 0.130903 -0.923771 -0.605810 -0.609220 -1.92556 -1.96195 -2.14665 -1.04938 -0.651481 -1.35483 -1.61321 -2.13502 -1.25888 0.0342960 -3.81585  2.24843  1.47300 0.602541  1.51954  1.75437  1.78090  1.81457 0.972916 -1.57063 -0.0699225 0.719598  2.12409  1.16225 0.737158 -2.18066  1.11333 -1.36359 0.0853249 -4.99871 -3.02055 -5.35228  1.68421 -0.000251611 -5.77295 0.438874
 66:     2124.5992:  1.61081  1.81311  1.49582  2.33864  2.26636  2.28779  2.90119  2.45761 -0.743707 0.130217 -0.925121 -0.598895 -0.600942 -1.92703 -1.96346 -2.14815 -1.05359 -0.668756 -1.35451 -1.61300 -2.13654 -1.32284 0.0652895 -3.76125  2.27865  1.50127 0.627630  1.54975  1.78190  1.81036  1.84402  1.00265 -1.54017 -0.0394525 0.749732  2.15987  1.19511 0.764860 -2.13750  1.14345 -1.33581 0.113317 -4.97117 -2.99040 -5.31862  1.68320 -0.000893416 -5.77549 0.438798
 67:     2124.5960:  1.61151  1.81355  1.49668  2.34036  2.26693  2.28935  2.90347  2.45825 -0.739558 0.129310 -0.917633 -0.599808 -0.600728 -1.92818 -1.96464 -2.14903 -1.05422 -0.658214 -1.35501 -1.61360 -2.13746 -1.39515 0.100269 -3.69572  2.30407  1.52560 0.653959  1.57697  1.80977  1.83685  1.87017  1.02928 -1.51136 -0.0125851 0.776889  2.18604  1.21955 0.796685 -2.12431  1.17694 -1.30702 0.137227 -4.92593 -2.95987 -5.28199  1.67755 -0.00105173 -5.78550 0.438980
 68:     2124.5943:  1.61247  1.81338  1.49802  2.34048  2.26615  2.28929  2.90304  2.45709 -0.736791 0.129535 -0.927466 -0.598658 -0.600679 -1.92652 -1.96280 -2.14705 -1.04575 -0.657578 -1.35503 -1.61305 -2.13551 -1.42561 0.128825 -3.68349  2.32791  1.55099 0.683018  1.60345  1.83606  1.86139  1.89490  1.05419 -1.49139 0.0117481 0.802167  2.20485  1.24125 0.834733 -2.15549  1.21408 -1.28247 0.165531 -4.88666 -2.94338 -5.23939  1.67487 -0.00134205 -5.80310 0.439166
 69:     2124.5940:  1.61221  1.81395  1.49837  2.33989  2.26603  2.28897  2.90191  2.45737 -0.736287 0.130283 -0.920900 -0.600459 -0.603549 -1.92268 -1.95879 -2.14329 -1.05967 -0.657699 -1.35372 -1.61209 -2.13180 -1.48002 0.132900 -3.62579  2.31994  1.54216 0.674741  1.59480  1.82628  1.85369  1.88808  1.04672 -1.49525 -0.00128340 0.796024  2.19935  1.23564 0.832973 -2.19059  1.20997 -1.28960 0.158576 -4.90022 -2.95764 -5.25240  1.67329 -0.000446247 -5.80770 0.438930
 70:     2124.5932:  1.61214  1.81439  1.49783  2.34058  2.26675  2.28953  2.90315  2.45830 -0.735175 0.130196 -0.916387 -0.599299 -0.601807 -1.92283 -1.95902 -2.14355 -1.05566 -0.656459 -1.35433 -1.61286 -2.13199 -1.45907 0.123833 -3.65376  2.31591  1.53820 0.668698  1.59024  1.82225  1.84948  1.88375  1.04258 -1.49660 -0.00565799 0.790847  2.19772  1.23216 0.825875 -2.18195  1.20105 -1.29375 0.151584 -4.90346 -2.95835 -5.25519  1.67243 -0.000183900 -5.80578 0.438901
 71:     2124.5927:  1.61294  1.81431  1.49806  2.34115  2.26671  2.28980  2.90378  2.45842 -0.736278 0.130460 -0.926862 -0.597151 -0.600264 -1.92307 -1.95938 -2.14381 -1.04157 -0.657753 -1.35345 -1.61182 -2.13224 -1.48650 0.119927 -3.63484  2.30908  1.53277 0.662794  1.58401  1.81618  1.84246  1.87627  1.03532 -1.50473 -0.00921447 0.782932  2.18907  1.22284 0.815522 -2.17286  1.18784 -1.29971 0.142845 -4.90875 -2.95922 -5.26512  1.67340 -4.43266e-05 -5.80196 0.439077
 72:     2124.5915:  1.61333  1.81434  1.49838  2.34107  2.26674  2.28969  2.90357  2.45813 -0.736185 0.130954 -0.922653 -0.598495 -0.600025 -1.92332 -1.95966 -2.14407 -1.04733 -0.658224 -1.35300 -1.61104 -2.13250 -1.53611 0.121278 -3.60638  2.30692  1.53173 0.661943  1.58269  1.81430  1.84033  1.87397  1.03306 -1.51028 -0.00957062 0.780869  2.18391  1.21925 0.812711 -2.17327  1.18131 -1.30249 0.142736 -4.91208 -2.96138 -5.26744  1.67476 -0.000118326 -5.80219 0.439117
 73:     2124.5894:  1.61308  1.81519  1.49826  2.34087  2.26701  2.28945  2.90361  2.45820 -0.735887 0.130623 -0.918017 -0.596391 -0.601320 -1.92324 -1.95952 -2.14408 -1.05038 -0.656423 -1.35451 -1.61281 -2.13255 -1.67416 0.127477 -3.51582  2.30153  1.52463 0.654666  1.57647  1.80889  1.83522  1.86905  1.02806 -1.51454 -0.0175574 0.776461  2.17874  1.21552 0.808109 -2.18360  1.17048 -1.30841 0.139852 -4.92090 -2.97006 -5.27026  1.67362 -0.000129476 -5.80603 0.438946
 74:     2124.5888:  1.61361  1.81541  1.49905  2.34074  2.26638  2.28932  2.90314  2.45823 -0.731113 0.130549 -0.919848 -0.609139 -0.594622 -1.92304 -1.95931 -2.14399 -1.05551 -0.660024 -1.35261 -1.61132 -2.13253 -2.00849 0.141702 -3.30387  2.28836  1.51254 0.642110  1.56423  1.79562  1.82241  1.85642  1.01524 -1.52422 -0.0307559 0.763041  2.16983  1.20266 0.796701 -2.20363  1.15114 -1.32038 0.122259 -4.93338 -2.98314 -5.28341  1.67032 -2.03160e-05 -5.81413 0.438990
 75:     2124.5869:  1.61321  1.81507  1.49864  2.34025  2.26591  2.28884  2.90263  2.45782 -0.740638 0.129854 -0.922871 -0.591704 -0.609588 -1.92384 -1.96011 -2.14483 -1.05564 -0.655438 -1.35336 -1.61219 -2.13338 -1.96961 0.128558 -3.35006  2.28290  1.50583 0.636789  1.55828  1.78982  1.81704  1.85119  1.00985 -1.52987 -0.0372217 0.757852  2.16402  1.19693 0.790384 -2.21152  1.14938 -1.32576 0.117537 -4.94017 -2.99002 -5.29300  1.67081 -2.39961e-05 -5.81544 0.438967
 76:     2124.5864:  1.61269  1.81543  1.49808  2.34034  2.26635  2.28875  2.90307  2.45791 -0.732981 0.129493 -0.922546 -0.603999 -0.597185 -1.92492 -1.96117 -2.14592 -1.04995 -0.658425 -1.35579 -1.61422 -2.13446 -2.00594 0.127874 -3.34030  2.28647  1.50723 0.637517  1.56044  1.79325  1.82039  1.85455  1.01330 -1.52849 -0.0363196 0.761351  2.16440  1.20098 0.791819 -2.20574  1.15581 -1.32436 0.124633 -4.93933 -2.98964 -5.29006  1.67270 -0.000125950 -5.81306 0.438837
 77:     2124.5853:  1.61309  1.81542  1.49829  2.34082  2.26663  2.28904  2.90356  2.45807 -0.734280 0.130028 -0.920771 -0.600115 -0.598958 -1.92548 -1.96177 -2.14643 -1.04880 -0.657705 -1.35510 -1.61317 -2.13496 -2.20559 0.140553 -3.22838  2.29147  1.51359 0.643652  1.56626  1.79883  1.82533  1.85928  1.01819 -1.52528 -0.0296121 0.765777  2.16871  1.20566 0.795379 -2.19460  1.16380 -1.32018 0.129806 -4.93243 -2.98370 -5.28214  1.67366 -0.000150844 -5.81102 0.438922
 78:     2124.5847:  1.61367  1.81525  1.49905  2.34086  2.26646  2.28931  2.90342  2.45818 -0.735900 0.130498 -0.921304 -0.598809 -0.601844 -1.92406 -1.96037 -2.14498 -1.05244 -0.657708 -1.35272 -1.61159 -2.13350 -2.32622 0.143816 -3.17478  2.29186  1.51644 0.646378  1.56798  1.79968  1.82601  1.85985  1.01877 -1.52145 -0.0264661 0.766354  2.17307  1.20637 0.796254 -2.19309  1.16948 -1.31719 0.126360 -4.92807 -2.97956 -5.27819  1.67111 -9.88829e-06 -5.81186 0.439040
 79:     2124.5838:  1.61373  1.81515  1.49894  2.34097  2.26637  2.28916  2.90338  2.45828 -0.737462 0.130853 -0.921176 -0.595956 -0.604004 -1.92309 -1.95937 -2.14401 -1.05261 -0.656557 -1.35297 -1.61102 -2.13253 -2.48249 0.143958 -3.11433  2.29537  1.51933 0.649850  1.57078  1.80245  1.82923  1.86310  1.02200 -1.51919 -0.0232123 0.769369  2.17477  1.20796 0.798282 -2.19091  1.17771 -1.31411 0.128898 -4.92542 -2.97600 -5.28147  1.67253 -5.68737e-05 -5.81035 0.439025
 80:     2124.5832:  1.61379  1.81552  1.49926  2.34093  2.26667  2.28919  2.90353  2.45831 -0.735903 0.130714 -0.921777 -0.597353 -0.602238 -1.92259 -1.95884 -2.14350 -1.05172 -0.656754 -1.35235 -1.61165 -2.13202 -2.77280 0.143662 -2.99566  2.29582  1.51940 0.649900  1.57148  1.80340  1.83010  1.86412  1.02288 -1.51717 -0.0230589 0.771589  2.17580  1.21167 0.798291 -2.19015  1.18228 -1.31240 0.134013 -4.92567 -2.97611 -5.27472  1.67187 0.000237537 -5.80991 0.438995
 81:     2124.5825:  1.61394  1.81581  1.49969  2.34090  2.26696  2.28935  2.90363  2.45832 -0.733378 0.130733 -0.921884 -0.601120 -0.599070 -1.92207 -1.95831 -2.14297 -1.05175 -0.657803 -1.35108 -1.61151 -2.13145 -2.98790 0.132563 -2.93755  2.29429  1.51872 0.648758  1.57086  1.80281  1.82902  1.86313  1.02182 -1.51588 -0.0240302 0.771464  2.17699  1.21373 0.797249 -2.19176  1.18027 -1.31243 0.134775 -4.92636 -2.97715 -5.26699  1.67006 0.000420152 -5.81005 0.439008
 82:     2124.5821:  1.61372  1.81568  1.49888  2.34117  2.26671  2.28888  2.90367  2.45842 -0.733389 0.131233 -0.920295 -0.601639 -0.598095 -1.92223 -1.95843 -2.14318 -1.05033 -0.657452 -1.35373 -1.61129 -2.13170 -3.38014 0.122978 -2.79552  2.29595  1.51931 0.649424  1.57082  1.80323  1.82975  1.86370  1.02264 -1.51795 -0.0241335 0.770109  2.17528  1.20919 0.796766 -2.19373  1.17596 -1.31445 0.129792 -4.92624 -2.97677 -5.28017  1.67238 -0.000297839 -5.81026 0.438945
 83:     2124.5818:  1.61361  1.81543  1.49869  2.34112  2.26653  2.28882  2.90364  2.45834 -0.735472 0.130920 -0.920548 -0.598355 -0.600952 -1.92318 -1.95941 -2.14411 -1.05050 -0.656821 -1.35419 -1.61200 -2.13266 -3.26990 0.122637 -2.84151  2.29602  1.51878 0.649178  1.57062  1.80281  1.82970  1.86362  1.02255 -1.51980 -0.0241827 0.769977  2.17346  1.20801 0.797870 -2.19276  1.17291 -1.31468 0.130918 -4.92671 -2.97685 -5.28324  1.67341 -0.000213908 -5.81051 0.438952
 84:     2124.5816:  1.61379  1.81549  1.49908  2.34109  2.26660  2.28893  2.90370  2.45829 -0.735835 0.130713 -0.921051 -0.597310 -0.601919 -1.92356 -1.95981 -2.14447 -1.05104 -0.656801 -1.35324 -1.61190 -2.13302 -3.40909 0.118110 -2.79757  2.29560  1.51871 0.649092  1.57091  1.80285  1.82966  1.86363  1.02246 -1.51924 -0.0238383 0.770794  2.17416  1.20999 0.799228 -2.19143  1.17158 -1.31374 0.133445 -4.92655 -2.97672 -5.27774  1.67265 0.000101849 -5.81082 0.438985
 85:     2124.5813:  1.61392  1.81565  1.49932  2.34104  2.26657  2.28884  2.90352  2.45819 -0.735617 0.130864 -0.920952 -0.598303 -0.601635 -1.92341 -1.95961 -2.14432 -1.05211 -0.657039 -1.35315 -1.61106 -2.13286 -3.68075 0.106396 -2.71885  2.29620  1.52026 0.650445  1.57192  1.80402  1.83045  1.86434  1.02323 -1.51672 -0.0225864 0.771438  2.17722  1.21109 0.803789 -2.19060  1.16924 -1.31278 0.131176 -4.92458 -2.97506 -5.27512  1.67117 -4.16554e-05 -5.81156 0.438995
 86:     2124.5812:  1.61392  1.81562  1.49930  2.34106  2.26656  2.28887  2.90358  2.45825 -0.735374 0.130878 -0.920969 -0.598679 -0.601309 -1.92324 -1.95945 -2.14414 -1.05196 -0.657124 -1.35279 -1.61141 -2.13268 -3.70049 0.103225 -2.71885  2.29627  1.52026 0.650445  1.57198  1.80397  1.83049  1.86443  1.02329 -1.51675 -0.0226217 0.771497  2.17704  1.21109 0.804691 -2.19062  1.16963 -1.31263 0.131862 -4.92467 -2.97509 -5.27523  1.67136 1.16981e-05 -5.81127 0.438997
 87:     2124.5812:  1.61382  1.81553  1.49906  2.34111  2.26656  2.28884  2.90369  2.45831 -0.735493 0.130849 -0.920884 -0.598149 -0.601349 -1.92326 -1.95948 -2.14416 -1.05111 -0.656930 -1.35336 -1.61184 -2.13271 -3.69996 0.102518 -2.71885  2.29630  1.51957 0.649891  1.57155  1.80353  1.83032  1.86428  1.02314 -1.51826 -0.0232233 0.771228  2.17511  1.21016 0.802960 -2.19113  1.17058 -1.31318 0.132966 -4.92567 -2.97581 -5.27815  1.67246 9.57695e-06 -5.81082 0.438981
 88:     2124.5812:  1.61384  1.81558  1.49911  2.34111  2.26660  2.28884  2.90367  2.45830 -0.735378 0.130879 -0.920870 -0.598240 -0.601207 -1.92322 -1.95943 -2.14413 -1.05109 -0.656923 -1.35335 -1.61161 -2.13267 -3.70016 0.102398 -2.71885  2.29620  1.51952 0.649836  1.57147  1.80353  1.83025  1.86420  1.02306 -1.51816 -0.0232663 0.771169  2.17528  1.21029 0.802135 -2.19118  1.17148 -1.31328 0.132620 -4.92572 -2.97595 -5.27778  1.67236 -1.27854e-05 -5.81082 0.438978
 89:     2124.5812:  1.61384  1.81558  1.49911  2.34111  2.26659  2.28885  2.90366  2.45830 -0.735366 0.130876 -0.920897 -0.598324 -0.601185 -1.92316 -1.95938 -2.14408 -1.05115 -0.656954 -1.35321 -1.61177 -2.13262 -3.70016 0.102180 -2.71885  2.29609  1.51947 0.649774  1.57139  1.80345  1.83015  1.86409  1.02296 -1.51812 -0.0233307 0.771042  2.17527  1.21017 0.801086 -2.19123  1.17250 -1.31337 0.132435 -4.92573 -2.97604 -5.27776  1.67228 -1.39623e-05 -5.81086 0.438979
 90:     2124.5812:  1.61385  1.81558  1.49912  2.34111  2.26659  2.28884  2.90366  2.45830 -0.735385 0.130875 -0.920897 -0.598280 -0.601221 -1.92319 -1.95941 -2.14410 -1.05115 -0.656943 -1.35334 -1.61158 -2.13264 -3.70021 0.102010 -2.71885  2.29607  1.51944 0.649749  1.57137  1.80342  1.83013  1.86407  1.02294 -1.51819 -0.0233458 0.771024  2.17524  1.21018 0.800785 -2.19122  1.17273 -1.31339 0.132397 -4.92576 -2.97607 -5.27782  1.67231 -7.41948e-06 -5.81086 0.438980
  0:     2124.5812:  1.61385  1.81558  1.49912  2.34111  2.26659  2.28884  2.90366  2.45830 -0.735385 0.130875 -0.920897 -0.598280 -0.601221 -1.92319 -1.95941 -2.14410 -1.05115 -0.656943 -1.35334 -1.61158 -2.13264 -3.70021 0.102010 -2.71885  2.29607  1.51944 0.649749  1.57137  1.80342  1.83013  1.86407  1.02294 -1.51819 -0.0233458 0.771024  2.17524  1.21018 0.800785 -2.19122  1.17273 -1.31339 0.132397 -4.92576 -2.97607 -5.27782  1.67231 -7.41948e-06 -5.81086 0.438980
  1:     2124.5812:  1.61385  1.81558  1.49912  2.34111  2.26659  2.28885  2.90366  2.45830 -0.735385 0.130875 -0.920897 -0.598279 -0.601222 -1.92319 -1.95941 -2.14410 -1.05115 -0.656943 -1.35334 -1.61158 -2.13264 -3.70021 0.101994 -2.71885  2.29608  1.51944 0.649750  1.57137  1.80342  1.83013  1.86407  1.02294 -1.51819 -0.0233449 0.771025  2.17524  1.21018 0.800787 -2.19122  1.17273 -1.31339 0.132399 -4.92576 -2.97607 -5.27782  1.67231 -4.71654e-06 -5.81086 0.438976
  2:     2124.5812:  1.61385  1.81559  1.49912  2.34110  2.26659  2.28885  2.90366  2.45830 -0.735386 0.130875 -0.920896 -0.598277 -0.601223 -1.92319 -1.95941 -2.14410 -1.05115 -0.656943 -1.35334 -1.61159 -2.13264 -3.70021 0.101979 -2.71885  2.29608  1.51944 0.649751  1.57137  1.80342  1.83013  1.86407  1.02295 -1.51819 -0.0233440 0.771026  2.17524  1.21018 0.800789 -2.19122  1.17273 -1.31339 0.132400 -4.92575 -2.97607 -5.27782  1.67232 -2.12967e-06 -5.81087 0.438981
  3:     2124.5812:  1.61386  1.81560  1.49912  2.34108  2.26658  2.28885  2.90365  2.45829 -0.735388 0.130876 -0.920893 -0.598270 -0.601226 -1.92318 -1.95941 -2.14410 -1.05115 -0.656940 -1.35332 -1.61160 -2.13264 -3.70019 0.101885 -2.71885  2.29608  1.51945 0.649756  1.57137  1.80343  1.83013  1.86406  1.02295 -1.51818 -0.0233384 0.771030  2.17524  1.21018 0.800801 -2.19122  1.17272 -1.31338 0.132409 -4.92575 -2.97606 -5.27781  1.67234 1.24474e-05 -5.81091 0.438977
  4:     2124.5812:  1.61387  1.81560  1.49913  2.34107  2.26658  2.28884  2.90367  2.45829 -0.735390 0.130875 -0.920890 -0.598264 -0.601230 -1.92318 -1.95940 -2.14410 -1.05114 -0.656939 -1.35331 -1.61162 -2.13264 -3.70017 0.101787 -2.71885  2.29608  1.51946 0.649761  1.57137  1.80343  1.83013  1.86407  1.02296 -1.51818 -0.0233330 0.771035  2.17524  1.21018 0.800814 -2.19121  1.17271 -1.31338 0.132417 -4.92575 -2.97606 -5.27781  1.67235 1.92503e-05 -5.81094 0.438983
  5:     2124.5812:  1.61387  1.81560  1.49913  2.34108  2.26658  2.28883  2.90366  2.45830 -0.735393 0.130874 -0.920888 -0.598259 -0.601233 -1.92318 -1.95940 -2.14410 -1.05114 -0.656938 -1.35329 -1.61163 -2.13264 -3.70016 0.101683 -2.71885  2.29608  1.51947 0.649765  1.57137  1.80344  1.83013  1.86409  1.02296 -1.51818 -0.0233278 0.771039  2.17524  1.21018 0.800827 -2.19121  1.17271 -1.31338 0.132425 -4.92574 -2.97605 -5.27781  1.67236 9.89449e-06 -5.81097 0.438974
  6:     2124.5812:  1.61386  1.81559  1.49912  2.34110  2.26659  2.28884  2.90366  2.45830 -0.735394 0.130873 -0.920887 -0.598256 -0.601236 -1.92318 -1.95940 -2.14409 -1.05114 -0.656937 -1.35328 -1.61164 -2.13263 -3.70014 0.101578 -2.71885  2.29608  1.51947 0.649769  1.57138  1.80344  1.83014  1.86410  1.02296 -1.51817 -0.0233228 0.771043  2.17523  1.21018 0.800840 -2.19121  1.17270 -1.31337 0.132433 -4.92574 -2.97604 -5.27780  1.67236 -4.67293e-06 -5.81098 0.438983
  7:     2124.5812:  1.61384  1.81558  1.49912  2.34113  2.26660  2.28887  2.90368  2.45828 -0.735395 0.130874 -0.920884 -0.598253 -0.601237 -1.92317 -1.95939 -2.14409 -1.05114 -0.656936 -1.35326 -1.61166 -2.13263 -3.70011 0.101327 -2.71885  2.29609  1.51948 0.649779  1.57140  1.80345  1.83017  1.86408  1.02297 -1.51816 -0.0233111 0.771054  2.17523  1.21018 0.800871 -2.19120  1.17269 -1.31336 0.132451 -4.92573 -2.97603 -5.27780  1.67233 -1.64825e-05 -5.81099 0.438979
  8:     2124.5812:  1.61383  1.81556  1.49912  2.34113  2.26663  2.28883  2.90368  2.45831 -0.735392 0.130888 -0.920877 -0.598247 -0.601235 -1.92316 -1.95938 -2.14407 -1.05113 -0.656932 -1.35321 -1.61171 -2.13261 -3.70001 0.100656 -2.71885  2.29612  1.51950 0.649806  1.57144  1.80347  1.83021  1.86407  1.02302 -1.51814 -0.0232815 0.771083  2.17524  1.21019 0.800951 -2.19119  1.17265 -1.31333 0.132495 -4.92571 -2.97598 -5.27777  1.67224 -1.87484e-06 -5.81100 0.438981
  9:     2124.5812:  1.61384  1.81556  1.49912  2.34111  2.26661  2.28884  2.90367  2.45831 -0.735386 0.130899 -0.920870 -0.598243 -0.601230 -1.92315 -1.95936 -2.14406 -1.05112 -0.656928 -1.35317 -1.61175 -2.13260 -3.69991 0.0999810 -2.71885  2.29614  1.51952 0.649831  1.57146  1.80348  1.83020  1.86415  1.02303 -1.51811 -0.0232547 0.771112  2.17524  1.21020 0.801031 -2.19117  1.17262 -1.31330 0.132536 -4.92568 -2.97594 -5.27775  1.67216 1.64142e-05 -5.81101 0.438966
 10:     2124.5812:  1.61385  1.81558  1.49913  2.34109  2.26659  2.28883  2.90367  2.45831 -0.735381 0.130905 -0.920865 -0.598240 -0.601224 -1.92313 -1.95935 -2.14405 -1.05111 -0.656924 -1.35314 -1.61177 -2.13259 -3.69982 0.0992985 -2.71885  2.29617  1.51954 0.649857  1.57149  1.80351  1.83022  1.86419  1.02306 -1.51808 -0.0232293 0.771141  2.17525  1.21021 0.801109 -2.19115  1.17259 -1.31327 0.132576 -4.92566 -2.97590 -5.27773  1.67211 1.80660e-05 -5.81102 0.438989
 11:     2124.5812:  1.61400  1.81578  1.49913  2.34117  2.26645  2.28870  2.90364  2.45838 -0.735341 0.130826 -0.920845 -0.598252 -0.601182 -1.92303 -1.95925 -2.14394 -1.05110 -0.656909 -1.35297 -1.61189 -2.13248 -3.69888 0.0921233 -2.71885  2.29640  1.51986 0.650121  1.57166  1.80383  1.83050  1.86449  1.02323 -1.51779 -0.0230036 0.771452  2.17544  1.21041 0.801886 -2.19096  1.17230 -1.31297 0.132953 -4.92539 -2.97549 -5.27748  1.67216 -0.000256177 -5.81132 0.438982
 12:     2124.5812:  1.61395  1.81573  1.49912  2.34114  2.26667  2.28878  2.90370  2.45848 -0.735316 0.130799 -0.920837 -0.598268 -0.601156 -1.92295 -1.95915 -2.14384 -1.05109 -0.656904 -1.35287 -1.61196 -2.13239 -3.69798 0.0849258 -2.71885  2.29662  1.52014 0.650377  1.57188  1.80411  1.83065  1.86481  1.02356 -1.51751 -0.0227783 0.771757  2.17565  1.21062 0.802639 -2.19076  1.17204 -1.31267 0.133305 -4.92512 -2.97509 -5.27724  1.67219 -3.92109e-05 -5.81152 0.438968
 13:     2124.5812:  1.61390  1.81551  1.49920  2.34115  2.26645  2.28872  2.90363  2.45833 -0.735283 0.131046 -0.920815 -0.598223 -0.601130 -1.92289 -1.95909 -2.14378 -1.05107 -0.656867 -1.35289 -1.61187 -2.13232 -3.69721 0.0777072 -2.71885  2.29688  1.52034 0.650620  1.57224  1.80417  1.83098  1.86508  1.02386 -1.51724 -0.0225369 0.772041  2.17593  1.21088 0.803307 -2.19055  1.17187 -1.31239 0.133579 -4.92485 -2.97474 -5.27699  1.67212 0.000217402 -5.81141 0.438960
 14:     2124.5812:  1.61386  1.81541  1.49921  2.34081  2.26652  2.28880  2.90363  2.45832 -0.735285 0.131199 -0.920807 -0.598173 -0.601144 -1.92287 -1.95907 -2.14376 -1.05107 -0.656845 -1.35302 -1.61170 -2.13230 -3.69656 0.0704625 -2.71885  2.29717  1.52054 0.650859  1.57258  1.80439  1.83123  1.86525  1.02410 -1.51698 -0.0222788 0.772305  2.17625  1.21118 0.803888 -2.19034  1.17179 -1.31213 0.133797 -4.92458 -2.97443 -5.27674  1.67202 2.68818e-05 -5.81113 0.438977
 15:     2124.5812:  1.61389  1.81559  1.49912  2.34102  2.26668  2.28880  2.90362  2.45819 -0.735318 0.131084 -0.920814 -0.598143 -0.601190 -1.92288 -1.95909 -2.14378 -1.05107 -0.656847 -1.35321 -1.61150 -2.13232 -3.69606 0.0631952 -2.71885  2.29745  1.52078 0.651099  1.57287  1.80478  1.83139  1.86542  1.02427 -1.51674 -0.0220138 0.772548  2.17660  1.21149 0.804370 -2.19011  1.17181 -1.31188 0.133970 -4.92432 -2.97416 -5.27649  1.67203 8.86479e-05 -5.81086 0.439015
 16:     2124.5812:  1.61389  1.81568  1.49905  2.34118  2.26651  2.28898  2.90378  2.45847 -0.735351 0.130914 -0.920822 -0.598137 -0.601234 -1.92290 -1.95911 -2.14380 -1.05108 -0.656861 -1.35333 -1.61138 -2.13234 -3.69559 0.0559231 -2.71901  2.29771  1.52103 0.651344  1.57305  1.80506  1.83174  1.86558  1.02455 -1.51651 -0.0217500 0.772782  2.17691  1.21179 0.804825 -2.18987  1.17186 -1.31165 0.134152 -4.92406 -2.97391 -5.27624  1.67210 0.000202084 -5.81071 0.439012
 17:     2124.5812:  1.61388  1.81554  1.49913  2.34121  2.26662  2.28890  2.90381  2.45844 -0.735340 0.130884 -0.920808 -0.598141 -0.601223 -1.92292 -1.95913 -2.14381 -1.05106 -0.656857 -1.35332 -1.61139 -2.13235 -3.69518 0.0486390 -2.71936  2.29792  1.52128 0.651601  1.57314  1.80520  1.83215  1.86595  1.02487 -1.51629 -0.0214930 0.773006  2.17717  1.21204 0.805235 -2.18964  1.17195 -1.31141 0.134357 -4.92381 -2.97368 -5.27598  1.67224 0.000129734 -5.81079 0.438900
 18:     2124.5811:  1.61384  1.81545  1.49918  2.34123  2.26662  2.28886  2.90381  2.45843 -0.735327 0.130915 -0.920804 -0.598157 -0.601207 -1.92293 -1.95914 -2.14383 -1.05106 -0.656858 -1.35330 -1.61141 -2.13236 -3.69499 0.0449926 -2.71950  2.29802  1.52143 0.651735  1.57324  1.80531  1.83224  1.86608  1.02505 -1.51618 -0.0213694 0.773118  2.17729  1.21217 0.805412 -2.18951  1.17203 -1.31129 0.134469 -4.92368 -2.97356 -5.27586  1.67234 7.56938e-05 -5.81087 0.438990
 19:     2124.5811:  1.61376  1.81551  1.49916  2.34116  2.26650  2.28884  2.90380  2.45841 -0.735299 0.131053 -0.920811 -0.598217 -0.601166 -1.92297 -1.95918 -2.14386 -1.05107 -0.656874 -1.35321 -1.61154 -2.13240 -3.69491 0.0413758 -2.71952  2.29816  1.52160 0.651874  1.57360  1.80557  1.83202  1.86605  1.02499 -1.51606 -0.0212540 0.773221  2.17738  1.21227 0.805424 -2.18937  1.17228 -1.31118 0.134602 -4.92357 -2.97350 -5.27573  1.67222 7.98549e-05 -5.81095 0.438989
 20:     2124.5811:  1.61380  1.81559  1.49910  2.34111  2.26655  2.28882  2.90378  2.45841 -0.735295 0.131051 -0.920827 -0.598264 -0.601154 -1.92301 -1.95923 -2.14391 -1.05108 -0.656896 -1.35316 -1.61163 -2.13245 -3.69487 0.0377236 -2.71944  2.29826  1.52169 0.651978  1.57376  1.80565  1.83221  1.86619  1.02496 -1.51595 -0.0211508 0.773310  2.17747  1.21238 0.805397 -2.18923  1.17257 -1.31108 0.134704 -4.92345 -2.97346 -5.27560  1.67213 0.000109809 -5.81095 0.438985
 21:     2124.5811:  1.61386  1.81562  1.49908  2.34111  2.26656  2.28881  2.90374  2.45836 -0.735297 0.131013 -0.920841 -0.598289 -0.601152 -1.92305 -1.95927 -2.14396 -1.05110 -0.656909 -1.35314 -1.61168 -2.13250 -3.69485 0.0340672 -2.71936  2.29835  1.52177 0.652078  1.57383  1.80570  1.83230  1.86632  1.02517 -1.51585 -0.0210504 0.773397  2.17756  1.21248 0.805352 -2.18909  1.17287 -1.31099 0.134799 -4.92335 -2.97343 -5.27548  1.67207 5.72145e-05 -5.81094 0.438964
 22:     2124.5811:  1.61376  1.81538  1.49926  2.34110  2.26655  2.28875  2.90370  2.45829 -0.735333 0.130942 -0.920850 -0.598198 -0.601212 -1.92317 -1.95939 -2.14409 -1.05111 -0.656883 -1.35319 -1.61166 -2.13262 -3.69511 0.0240777 -2.71913  2.29859  1.52201 0.652335  1.57376  1.80621  1.83264  1.86657  1.02533 -1.51559 -0.0207861 0.773632  2.17784  1.21276 0.805071 -2.18868  1.17382 -1.31076 0.135036 -4.92307 -2.97334 -5.27514  1.67224 5.26686e-06 -5.81098 0.438955
 23:     2124.5811:  1.61377  1.81552  1.49914  2.34109  2.26660  2.28873  2.90372  2.45824 -0.735374 0.130962 -0.920861 -0.598142 -0.601271 -1.92328 -1.95950 -2.14420 -1.05112 -0.656875 -1.35324 -1.61164 -2.13273 -3.69564 0.0140949 -2.71893  2.29880  1.52226 0.652536  1.57405  1.80619  1.83287  1.86682  1.02566 -1.51535 -0.0205601 0.773850  2.17807  1.21300 0.804643 -2.18828  1.17490 -1.31054 0.135259 -4.92282 -2.97328 -5.27481  1.67239 -6.01555e-05 -5.81100 0.438977
 24:     2124.5811:  1.61403  1.81540  1.49912  2.34116  2.26665  2.28878  2.90369  2.45828 -0.735351 0.130921 -0.920859 -0.598220 -0.601230 -1.92329 -1.95951 -2.14421 -1.05112 -0.656901 -1.35323 -1.61165 -2.13274 -3.69633 0.0106756 -2.71885  2.29883  1.52224 0.652562  1.57417  1.80624  1.83289  1.86686  1.02568 -1.51532 -0.0205339 0.773884  2.17806  1.21301 0.804246 -2.18815  1.17546 -1.31052 0.135297 -4.92280 -2.97330 -5.27473  1.67226 -7.50254e-05 -5.81090 0.438988
 25:     2124.5811:  1.61380  1.81561  1.49919  2.34117  2.26664  2.28878  2.90362  2.45829 -0.735296 0.130915 -0.920841 -0.598308 -0.601149 -1.92325 -1.95948 -2.14418 -1.05110 -0.656918 -1.35320 -1.61164 -2.13271 -3.69740 0.00737733 -2.71885  2.29879  1.52220 0.652558  1.57412  1.80624  1.83294  1.86690  1.02574 -1.51535 -0.0205411 0.773882  2.17801  1.21296 0.803740 -2.18805  1.17604 -1.31054 0.135290 -4.92282 -2.97331 -5.27468  1.67210 -6.13259e-05 -5.81077 0.438992
 26:     2124.5811:  1.61395  1.81567  1.49905  2.34108  2.26662  2.28874  2.90370  2.45825 -0.735307 0.130912 -0.920838 -0.598291 -0.601163 -1.92317 -1.95939 -2.14409 -1.05110 -0.656919 -1.35323 -1.61156 -2.13262 -3.69905 0.00435278 -2.71885  2.29877  1.52216 0.652489  1.57401  1.80606  1.83287  1.86678  1.02562 -1.51544 -0.0205919 0.773818  2.17792  1.21287 0.803109 -2.18802  1.17659 -1.31063 0.135180 -4.92292 -2.97334 -5.27470  1.67221 1.53338e-05 -5.81076 0.438978
 27:     2124.5811:  1.61391  1.81563  1.49913  2.34112  2.26664  2.28874  2.90370  2.45830 -0.735359 0.130930 -0.920860 -0.598236 -0.601234 -1.92315 -1.95937 -2.14407 -1.05112 -0.656918 -1.35325 -1.61158 -2.13260 -3.69928 0.00434767 -2.71885  2.29869  1.52212 0.652434  1.57411  1.80596  1.83282  1.86674  1.02556 -1.51548 -0.0206430 0.773775  2.17790  1.21285 0.803113 -2.18808  1.17647 -1.31067 0.135123 -4.92297 -2.97335 -5.27476  1.67231 -2.29989e-06 -5.81084 0.438973
 28:     2124.5811:  1.61390  1.81560  1.49912  2.34113  2.26660  2.28873  2.90371  2.45831 -0.735391 0.130963 -0.920882 -0.598199 -0.601279 -1.92313 -1.95935 -2.14405 -1.05114 -0.656914 -1.35324 -1.61165 -2.13258 -3.69939 0.00538931 -2.71885  2.29859  1.52202 0.652338  1.57400  1.80595  1.83272  1.86666  1.02552 -1.51555 -0.0207306 0.773687  2.17784  1.21279 0.803248 -2.18823  1.17610 -1.31075 0.135039 -4.92306 -2.97337 -5.27487  1.67227 -2.06769e-08 -5.81088 0.438979
 29:     2124.5811:  1.61388  1.81557  1.49919  2.34111  2.26657  2.28873  2.90370  2.45830 -0.735356 0.130856 -0.920874 -0.598236 -0.601232 -1.92312 -1.95934 -2.14404 -1.05113 -0.656916 -1.35325 -1.61167 -2.13257 -3.69953 0.00638570 -2.71885  2.29855  1.52196 0.652263  1.57388  1.80582  1.83258  1.86653  1.02540 -1.51564 -0.0208255 0.773592  2.17776  1.21271 0.803367 -2.18839  1.17571 -1.31084 0.134953 -4.92315 -2.97342 -5.27501  1.67226 4.74208e-06 -5.81090 0.438983
 30:     2124.5811:  1.61387  1.81555  1.49913  2.34115  2.26657  2.28875  2.90370  2.45831 -0.735316 0.130964 -0.920849 -0.598304 -0.601171 -1.92313 -1.95934 -2.14405 -1.05111 -0.656930 -1.35327 -1.61162 -2.13258 -3.69985 0.00711000 -2.71885  2.29840  1.52182 0.652119  1.57369  1.80574  1.83242  1.86637  1.02525 -1.51578 -0.0209858 0.773446  2.17761  1.21255 0.803476 -2.18863  1.17519 -1.31098 0.134819 -4.92331 -2.97353 -5.27522  1.67232 -8.85813e-07 -5.81093 0.438983
 31:     2124.5811:  1.61391  1.81560  1.49923  2.34114  2.26656  2.28876  2.90372  2.45830 -0.735361 0.130937 -0.920841 -0.598224 -0.601238 -1.92314 -1.95935 -2.14405 -1.05110 -0.656913 -1.35326 -1.61159 -2.13259 -3.70027 0.00679385 -2.71885  2.29812  1.52156 0.651906  1.57357  1.80567  1.83227  1.86622  1.02512 -1.51598 -0.0211869 0.773262  2.17740  1.21233 0.803566 -2.18891  1.17460 -1.31117 0.134647 -4.92350 -2.97369 -5.27547  1.67225 1.04237e-05 -5.81089 0.438985
 32:     2124.5811:  1.61388  1.81557  1.49916  2.34114  2.26656  2.28874  2.90370  2.45830 -0.735398 0.130928 -0.920860 -0.598143 -0.601297 -1.92314 -1.95935 -2.14405 -1.05112 -0.656891 -1.35324 -1.61162 -2.13259 -3.70043 0.00572662 -2.71885  2.29809  1.52151 0.651817  1.57343  1.80554  1.83216  1.86613  1.02501 -1.51606 -0.0212505 0.773181  2.17731  1.21224 0.803578 -2.18904  1.17437 -1.31124 0.134567 -4.92358 -2.97378 -5.27558  1.67218 4.18672e-06 -5.81089 0.438984
 33:     2124.5811:  1.61388  1.81558  1.49916  2.34113  2.26656  2.28871  2.90369  2.45830 -0.735380 0.130942 -0.920925 -0.598282 -0.601251 -1.92314 -1.95935 -2.14406 -1.05119 -0.656950 -1.35324 -1.61170 -2.13259 -3.70046 0.00343819 -2.71885  2.29799  1.52140 0.651699  1.57327  1.80535  1.83204  1.86601  1.02487 -1.51619 -0.0213857 0.773054  2.17722  1.21215 0.803468 -2.18918  1.17422 -1.31137 0.134412 -4.92370 -2.97394 -5.27572  1.67219 -3.61929e-07 -5.81093 0.438983
 34:     2124.5811:  1.61385  1.81555  1.49903  2.34108  2.26655  2.28869  2.90365  2.45826 -0.735329 0.130840 -0.920892 -0.598293 -0.601189 -1.92316 -1.95937 -2.14408 -1.05115 -0.656932 -1.35326 -1.61173 -2.13261 -3.70041 0.00138641 -2.71885  2.29772  1.52114 0.651445  1.57307  1.80508  1.83183  1.86576  1.02463 -1.51644 -0.0216602 0.772794  2.17698  1.21192 0.803156 -2.18943  1.17403 -1.31163 0.134137 -4.92395 -2.97426 -5.27598  1.67227 -2.06769e-06 -5.81098 0.438980
 35:     2124.5811:  1.61390  1.81563  1.49911  2.34111  2.26661  2.28874  2.90367  2.45827 -0.735355 0.130923 -0.920843 -0.598261 -0.601224 -1.92320 -1.95941 -2.14411 -1.05110 -0.656930 -1.35330 -1.61171 -2.13265 -3.70026 -0.000292822 -2.71885  2.29744  1.52084 0.651120  1.57268  1.80466  1.83147  1.86539  1.02425 -1.51679 -0.0219911 0.772430  2.17662  1.21156 0.802708 -2.18980  1.17376 -1.31199 0.133787 -4.92430 -2.97469 -5.27636  1.67230 -9.15360e-07 -5.81100 0.438978
 36:     2124.5811:  1.61389  1.81560  1.49914  2.34114  2.26661  2.28873  2.90371  2.45829 -0.735318 0.130935 -0.920874 -0.598325 -0.601170 -1.92319 -1.95941 -2.14411 -1.05114 -0.656939 -1.35323 -1.61156 -2.13265 -3.69988 -0.00158651 -2.71885  2.29702  1.52039 0.650693  1.57231  1.80428  1.83107  1.86503  1.02386 -1.51723 -0.0223640 0.772000  2.17614  1.21107 0.802219 -2.19024  1.17336 -1.31242 0.133399 -4.92475 -2.97512 -5.27681  1.67226 -2.11959e-05 -5.81092 0.438978
 37:     2124.5811:  1.61389  1.81559  1.49915  2.34112  2.26658  2.28873  2.90369  2.45829 -0.735380 0.130922 -0.920917 -0.598259 -0.601255 -1.92315 -1.95936 -2.14407 -1.05118 -0.656943 -1.35324 -1.61162 -2.13260 -3.69974 -0.000343950 -2.71885  2.29675  1.52017 0.650489  1.57208  1.80413  1.83084  1.86479  1.02366 -1.51746 -0.0226786 0.771776  2.17594  1.21088 0.801855 -2.19046  1.17324 -1.31265 0.133155 -4.92500 -2.97530 -5.27704  1.67230 1.32296e-06 -5.81092 0.438981
```

Table output
```
Coefficient_name
<chr>
Number_of_coefficients
<dbl>
Type
<chr>
beta1_ft	21	Fixed		
beta2_ft	21	Fixed		
L_epsilon1_z	1	Fixed		
L_epsilon2_z	1	Fixed		
L_omega1_z	1	Fixed		
L_omega2_z	1	Fixed		
logkappa1	1	Fixed		
logkappa2	1	Fixed		
logSigmaM	1	Fixed		
Epsiloninput1_sff	6627	Random	
```

```
Description:df [1  6]
 
 
Param
<chr>
starting_value
<dbl>
Lower
<dbl>
MLE
<dbl>
Upper
<dbl>
final_gradient
<dbl>
24	logkappa1	-0.1053605	-6.359621	-2.718847	-2.718847	-0.00380568

```
```
 
 
Param
<chr>
starting_value
<dbl>
Lower
<dbl>
MLE
<dbl>
Upper
<dbl>
final_gradient
<dbl>
47	L_epsilon2_z	1	-Inf	1.322964e-06	Inf	2.809993e-05
```



Crashes with error: 
Error: Please change model structure to avoid problems with parameter estimates and then re-try; see details in `?check_fit`

There is no file output. May need to run as script to work properly