---
title: "VAST take 1"
author: "Sarah Gaichas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_fold: hide
link-citations: yes
csl: ices-journal-of-marine-science.csl
bibliography: FishDiet_EcoIndicators.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

library(tidyverse)
library(here)
#library(DT)
#library(pdftools)
#library(patchwork)
#library(ggiraph)

#library(ecodata)
library(VAST)
```

Having built an initial dataset of haul-specific mean bluefish prey weight per stomach for piscivores, now we'll try to get a forage biomass index using VAST.

The approach here is to use exactly what @ng_predator_2021 for herring, but combining all bluefish prey (defined [here](https://sgaichas.github.io/bluefishdiet/PreyAggs.html)) as sampled by all piscivore predators at each station.

In @ng_predator_2021, seasons were modeled separately, so we will start that way as well. They used 100 knots, estimated by k-means clustering of the data, to define the spatial dimensions of each seasonal model. They used a a Poisson-link delta model to estimate expected prey mass per predator stomach.  

Read in data, separate spring and fall, and rename columns for VAST:

```{r, eval=FALSE}
bluepyagg_stn <- readRDS(here("fhdat/bluepyagg_stn.rds"))

bluepyagg_stn_fall <- bluepyagg_stn %>%
  ungroup() %>%
  filter(season_ng == "FALL") %>%
  mutate(Vessel = "NEFSC",
         AreaSwept_km2 = 0.0384) %>%
  select(Catch_KG = meanbluepywt,
         Year = year,
         Vessel,
         AreaSwept_km2,
         Lat = declat,
         Lon = declon) %>%
  as.data.frame()

bluepyagg_stn_spring <- bluepyagg_stn %>%
  filter(season_ng == "SPRING")%>%
  mutate(Vessel = "NEFSC",
         AreaSwept_km2 = 0.0384) %>%
  select(Catch_KG = meanbluepywt,
         Year = year,
         Vessel,
         AreaSwept_km2,
         Lat = declat,
         Lon = declon)%>%
  as.data.frame()
```

Try the simplest possible index standardization model, fall (run from script `VASTunivariate_bluefishprey.R`, *not* in rmd):

```{r, code = readLines(here("VASTunivariate_bluefishprey.R")), eval=F}
```

R console output of full script (TMB Warning gone after updating Matrix package to current; no longer advised to update TMB so I'm leaving it alone):
```
Loading required package: TMB
###########################################################################################
Loading package VAST version 3.8.2
For information and examples, please see http://github.com/james-thorson/VAST/
###########################################################################################
Loading package `FishStatsUtils` version 2.10.2
Loading required package: units
udunits database from /Library/Frameworks/R.framework/Versions/4.0/Resources/library/units/share/udunits/udunits2.xml

[...code in script...]

### Writing output from `fit_model` in directory: /Users/sarah.gaichas/Documents/0_Data/bluefishdiet/pyindex/allagg_fall//

### Making extrapolation-grid
Using strata 1:100000
For the UTM conversion, automatically detected zone 19.
# Reducing extrapolation-grid from 31311 to 2000 cells for Region(s): northwest_atlantic
Using 100 iterations to find optimal extrapolation grid placement because no saved file found...
Iter=1: Current=821480
Iter=10: Current=809392 Proposed=813597
Iter=20: Current=809392 Proposed=818043
Iter=30: Current=809392 Proposed=813552
Iter=40: Current=807909 Proposed=807927
Iter=50: Current=807817 Proposed=814752
Iter=60: Current=807817 Proposed=819982
Iter=70: Current=807817 Proposed=813120
Iter=80: Current=807817 Proposed=818292
Iter=90: Current=807817 Proposed=811000
Iter=100: Final=807817 after 47 iterations
Results saved to /Users/sarah.gaichas/Documents/0_Data/bluefishdiet/pyindex/allagg_fall//Kmeans_extrapolation-2000.RData
 for subsequent runs by default (delete it to override)

### Making spatial information
Using 100 iterations to find optimal spatial knot placement because no saved file found...
Iter=1: Current=1155548
Iter=10: Current=1118027 Proposed=1126877
Iter=20: Current=1105240 Proposed=1138444
Iter=30: Current=1105240 Proposed=1176444
Iter=40: Current=1105240 Proposed=1125060
Iter=50: Current=1104305 Proposed=1144182
Iter=60: Current=1104305 Proposed=1140426
Iter=70: Current=1104305 Proposed=1116826
Iter=80: Current=1104305 Proposed=1150607
Iter=90: Current=1104305 Proposed=1149081
Iter=100: Final=1104305 after 45 iterations
Results saved to /Users/sarah.gaichas/Documents/0_Data/bluefishdiet/pyindex/allagg_fall//Kmeans_knots-100.RData
 for subsequent runs by default (delete it to override)

### Making data object
Coercing `b_i` to have units `kg`; I recommend using explicit units, e.g., `as_units(b_i,'kg')`, `as_units(b_i,'count') or `as_units(b_i,unitless)`
Coercing `a_i` to have units `km^2`; I recommend using explicit units, e.g., `as_units(a_i,'km^2')` or `as_units(a_i,unitless)`
FieldConfig_input is:
             Component_1 Component_2
Omega                 -2          -2
Epsilon               -2          -2
Beta                  -2          -2
Epsilon_time          -3          -3
OverdispersionConfig_input is:
Eta1 Eta2 
  -1   -1 
Calculating range shift for stratum #1:

### Making TMB object
Note: Using Makevars in /Users/sarah.gaichas/.R/Makevars 
make: Nothing to be done for `all'.
Constructing atomic logspace_sub
Constructing atomic D_lgamma
Constructing atomic D_incpl_gamma_shape
Constructing atomic logspace_sub
Constructing atomic D_lgamma
Constructing atomic D_incpl_gamma_shape
List of estimated fixed and random effects:
    Coefficient_name Number_of_coefficients   Type
1           beta1_ft                     21  Fixed
2           beta2_ft                     21  Fixed
3       L_epsilon1_z                      1  Fixed
4       L_epsilon2_z                      1  Fixed
5         L_omega1_z                      1  Fixed
6         L_omega2_z                      1  Fixed
7         ln_H_input                      2  Fixed
8          logkappa1                      1  Fixed
9          logkappa2                      1  Fixed
10         logSigmaM                      1  Fixed
11 Epsiloninput1_sff                   6627 Random
12 Epsiloninput2_sff                   6627 Random
13    Omegainput1_sf                    141 Random
14    Omegainput2_sf                    141 Random

### Testing model at initial values
No problem detected: All fixed effects have a nonzero gradient

### Estimating parameters
Note that `getReportCovariance=FALSE` causes an error in `TMB::sdreport` when no ADREPORTed variables are present
  0:     3407.4426:  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  1.00000  1.00000 -2.71885  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  0.00000  1.00000  1.00000 -2.71885  1.60944
  1:     2988.5057: 0.000768207 0.000577006 0.0287776 0.0279307 0.0169915 0.0530422 0.0708692 0.165965 0.329559 0.127660 -0.0176126 -0.00226152 -0.0169023 -0.0135198 -0.0138058 -0.0199080 -0.0209304 -0.0255203 -0.0196997 -0.0146035 -0.0200739 -0.0270282 -0.0250568  1.16823  1.07727 -2.96382 0.0490667 0.0242394 0.00565546 0.0463988 0.0419860 0.125744 0.308510 0.0446797 1.00017e-05 0.00235638 0.00297993 0.0127676 0.00436147 0.000628474 -6.59582e-05 0.000247511 -0.000110302 0.00151567 -0.000209251 -0.000172832 -0.000106104  1.34391  1.09188 -3.15321  1.05881
  2:     2501.1418: 0.00334379 0.00258901 0.0591370 0.0581012 0.0344217 0.111083 0.147628 0.339933 0.679370 0.265111 -0.0442651 -0.0117235 -0.0416804 -0.0344091 -0.0353186 -0.0473452 -0.0494601 -0.0602018 -0.0475993 -0.0368652 -0.0486083 -0.0641179 -0.0592673  1.38409  1.21110 -3.35889 0.106151 0.0507886 0.0106329 0.0893613 0.0944899 0.248203 0.525927 0.0868394 -0.00100489 0.00293530 0.00537341 0.0276333 0.00888093 0.00134508 -0.000390376 0.000764832 -0.000865304 0.00235487 -0.000945219 -0.000862590 -0.000475531  1.93966  1.19570 -4.06184 0.429601
  3:     2331.6240: 0.00961339 0.00731568 0.111321 0.113546 0.0641580 0.219296 0.286509 0.622806  1.21973 0.507948 -0.112330 -0.0487902 -0.105373 -0.0900331 -0.0916373 -0.114688 -0.119091 -0.143024 -0.118345 -0.0960820 -0.119780 -0.154070 -0.141643  1.64949  1.61922 -4.21575 0.159569 0.0660778 0.00333819 0.107817 0.147809 0.322049 0.574386 0.0826694 -0.0109736 -0.0124852 0.00346763 0.0447369 0.0100455 0.000636420 -0.00301573 0.000770571 -0.00825836 -0.00413379 -0.00637831 -0.00620985 -0.00319446  2.21111  1.25391 -4.64657 0.801675
  4:     2262.2833: 0.0106043 0.00787075 0.117904 0.122108 0.0686263 0.233950 0.301802 0.644154  1.24423 0.530342 -0.119701 -0.0532570 -0.112815 -0.0963833 -0.0975163 -0.123031 -0.127858 -0.152588 -0.126612 -0.102802 -0.128061 -0.164117 -0.151254  1.65295  1.68928 -4.33260 0.163393 0.0671540 0.00271179 0.108984 0.151705 0.326273 0.575263 0.0820022 -0.0119137 -0.0138359 0.00333224 0.0463457 0.0102230 0.000583917 -0.00326551 0.000794880 -0.00895773 -0.00471684 -0.00689791 -0.00672029 -0.00345454  2.22154  1.25277 -4.66814 0.421220
  5:     2237.7671: 0.0141006 0.00972319 0.134248 0.144148 0.0800097 0.269918 0.338939 0.692780  1.29792 0.582286 -0.137272 -0.0639917 -0.130623 -0.111407 -0.111280 -0.143338 -0.149243 -0.175658 -0.146351 -0.118667 -0.148007 -0.188120 -0.174468  1.65779  1.86153 -4.62580 0.177453 0.0698175 -0.000532102 0.111098 0.167955 0.341867 0.577024 0.0795918 -0.0173977 -0.0205372 0.00245558 0.0539894 0.0111759 0.000271021 -0.00474296 0.00103175 -0.0130733 -0.00803979 -0.00998850 -0.00975272 -0.00500170  2.24845  1.26472 -4.74050 0.588557
  6:     2234.0538: 0.0139155 0.00906184 0.148910 0.161943 0.0899183 0.298999 0.373757 0.755952  1.40812 0.637087 -0.148844 -0.0688092 -0.142207 -0.120823 -0.120097 -0.157192 -0.163866 -0.192032 -0.159463 -0.128553 -0.161510 -0.205049 -0.190789  1.68981  1.94443 -4.79002 0.193561 0.0756067 -0.00144055 0.122475 0.182483 0.376246 0.664090 0.0856566 -0.0202022 -0.0238346 0.00264950 0.0602349 0.0123919 0.000158937 -0.00550846 0.00109231 -0.0152263 -0.00950304 -0.0116003 -0.0113303 -0.00580884  2.24557  1.27963 -4.71356 0.292213
  7:     2212.4925: 0.0118565 0.00705874 0.166279 0.180939 0.101156 0.331055 0.416570 0.846393  1.58484 0.709074 -0.159900 -0.0713013 -0.153074 -0.129365 -0.128408 -0.170615 -0.178043 -0.208579 -0.172064 -0.137543 -0.174620 -0.222206 -0.207142  1.74826  1.99042 -4.90806 0.216727 0.0842511 -0.00192644 0.141494 0.202844 0.433304 0.825889 0.0987662 -0.0239337 -0.0274123 0.00326929 0.0691352 0.0145057 7.47117e-05 -0.00655487 0.00125901 -0.0181367 -0.0112141 -0.0138233 -0.0134984 -0.00692242  2.21721  1.31389 -4.62425 0.507374
  8:     2205.6081: -0.00497313 -0.00752829 0.194413 0.219365 0.122648 0.383511 0.482074 0.944012  1.75907 0.797799 -0.180656 -0.0810929 -0.173690 -0.145358 -0.142767 -0.198034 -0.207101 -0.239968 -0.195058 -0.153216 -0.200071 -0.252978 -0.238487  1.77278  2.06864 -5.11564 0.265412 0.0980971 -0.00837214 0.161583 0.252064 0.507445 0.949499 0.103385 -0.0383145 -0.0441528 0.00266389 0.0945236 0.0196862 -0.000358342 -0.0104824 0.00241230 -0.0289583 -0.0189485 -0.0220873 -0.0215818 -0.0110605  2.16711  1.34800 -4.56675 0.422415
  9:     2199.7408: -0.0465124 -0.0428508 0.188404 0.233060 0.127239 0.375611 0.455716 0.775484  1.37179 0.696426 -0.186993 -0.0981481 -0.180654 -0.150804 -0.144814 -0.211009 -0.220996 -0.249032 -0.200572 -0.156019 -0.209373 -0.257882 -0.248395  1.55319  2.10332 -5.18924 0.287893 0.0928837 -0.0244449 0.120997 0.291447 0.431985 0.483911 0.0547187 -0.0631183 -0.0748662 -0.00234254 0.124466 0.0248921 -0.00110064 -0.0171767 0.00539862 -0.0471296 -0.0334728 -0.0361005 -0.0353048 -0.0180758  2.20884  1.29633 -4.93868 0.491361
 10:     2197.4413: -0.311106 -0.276965 0.226978 0.307495 0.169428 0.440010 0.519476 0.706222  1.14199 0.699905 -0.227953 -0.136586 -0.221497 -0.182472 -0.170602 -0.276272 -0.289956 -0.314801 -0.244112 -0.181441 -0.263941 -0.314170 -0.314602  1.23415  1.94943 -5.30492 0.402146 0.0982479 -0.0626428 0.0898178 0.420629 0.459751 0.180600 0.0102195 -0.145080 -0.158458 -0.0113043 0.227312 0.0483010 -0.00274811 -0.0399783 0.0151703 -0.108507 -0.0768669 -0.0842828 -0.0823275 -0.0422073  2.18188  1.20373 -5.20042 0.364155
 11:     2184.6381: -0.569284 -0.516972 0.293857 0.396368 0.224327 0.550433 0.658039 0.880819  1.43739 0.871626 -0.277503 -0.163362 -0.270313 -0.220254 -0.205048 -0.349789 -0.367201 -0.395715 -0.299132 -0.215278 -0.328350 -0.388640 -0.394852  1.14822  1.77534 -5.47169 0.534843 0.121943 -0.0885255 0.119917 0.546391 0.623817 0.459703 0.0241170 -0.217841 -0.225409 -0.0151195 0.323632 0.0727509 -0.00364893 -0.0606139 0.0238805 -0.163490 -0.112647 -0.128081 -0.124977 -0.0641488  2.10349  1.19175 -5.07398 0.446192
 12:     2177.6448: -1.01895 -1.02604 0.448199 0.587103 0.357703 0.781108 0.935290  1.20767  1.96628  1.19837 -0.376876 -0.192135 -0.372908 -0.299293 -0.279942 -0.515578 -0.536579 -0.577564 -0.417968 -0.290699 -0.468236 -0.550408 -0.573704 0.931963  1.43773 -5.84640 0.844401 0.217168 -0.138623 0.242004 0.763331 0.913858  1.01132 0.0696611 -0.405137 -0.391839 -0.0183655 0.557543 0.136256 -0.00470664 -0.114020 0.0446240 -0.304304 -0.197631 -0.241191 -0.235022 -0.120816  2.06555  1.09275 -4.79332 0.433764
 13:     2169.9550: -0.773808 -0.845437 0.655742 0.838779 0.556800  1.07685  1.24786  1.45410  2.22661  1.49944 -0.495801 -0.190662 -0.506587 -0.397755 -0.375736 -0.751631 -0.773708 -0.833532 -0.574746 -0.394229 -0.656199 -0.766470 -0.826354 0.684506  1.20376 -6.02251  1.26696 0.461274 -0.177955 0.547490 0.913545  1.06920  1.24624 0.206992 -0.712935 -0.641707 -0.00588596 0.910267 0.245138 -0.00209189 -0.203465 0.0754986 -0.535431 -0.317484 -0.430506 -0.418729 -0.215687  2.50383 0.821054 -4.41657 0.494074
 14:     2160.1515: -0.669687 -0.878486 0.876489  1.11488 0.769389  1.41965  1.59443  1.72657  2.45884  1.84289 -0.639951 -0.200366 -0.671743 -0.520615 -0.492977 -1.02901 -1.05515 -1.13543 -0.765074 -0.527166 -0.878782 -1.02430 -1.12618 0.551741 0.696988 -6.00033  1.52757 0.742827 -0.116214 0.862713  1.04306  1.22783  1.14082 0.532975 -1.05743 -0.776687 0.0174471  1.18498 0.371668 0.00976556 -0.309987 0.129590 -0.793717 -0.415627 -0.657916 -0.637955 -0.329718  2.54735 0.440729 -4.42721 0.503879
 15:     2158.1288: -0.147831 -0.794417  1.83161  2.28664  1.67024  2.93961  3.11539  2.96886  3.52498  3.36273 -1.25244 -0.232315 -1.37625 -1.04655 -0.996421 -2.17561 -2.22236 -2.38906 -1.57125 -1.09554 -1.81160 -2.10916 -2.37173 0.0959937 -1.18087 -5.66488  2.54339  1.79726 0.143356  1.98330  1.69207  1.82983  1.42755  1.39265 -2.39293 -1.23259 0.119179  2.24353 0.865449 0.0591665 -0.728345 0.345523 -1.79797 -0.777368 -1.55190 -1.49885 -0.778045  2.44566 -0.824261 -4.49402 0.444410
 16:     2155.5945: -0.151042 -0.975009  1.87184  2.34695  1.74413  2.95848  3.10900  2.78155  3.10670  3.23184 -1.29501 -0.222945 -1.43885 -1.08297 -1.02639 -2.34666 -2.39456 -2.56951 -1.64484 -1.13323 -1.92041 -2.22998 -2.55085 -0.0177720 -0.966859 -5.47084  2.53041  1.81573 0.299985  1.83855  1.63603  1.66410  1.46087  1.08246 -2.49765 -0.961882 0.202376  2.39740 0.988702 0.0994993 -0.833165 0.422913 -1.92495 -0.684019 -1.78389 -1.71097 -0.895091  2.57154 -1.63518 -4.94387 0.513187
 17:     2148.6246: -0.133344 -1.01709  1.68200  2.09280  1.60977  2.59685  2.69360  2.35042  2.61130  2.70252 -1.19423 -0.162740 -1.35735 -0.993075 -0.933613 -2.33537 -2.38503 -2.55459 -1.55129 -1.03508 -1.85909 -2.15872 -2.53685 -0.136476 -0.794614 -5.58186  2.38270  1.61731 0.397015  1.49613  1.62303  1.57076  1.47624 0.758838 -2.37892 -0.682090 0.273264  2.38361  1.04016 0.143096 -0.883484 0.481235 -1.87964 -0.530706 -1.90971 -1.80853 -0.959917  2.77214 -1.40726 -5.13758 0.366860
 18:     2135.1273: -0.189657 -1.13575  1.50128  1.81731  1.45621  2.27259  2.32932  2.20083  2.66645  2.37822 -1.06331 -0.0639060 -1.25017 -0.878455 -0.820786 -2.29607 -2.34761 -2.51532 -1.42871 -0.914666 -1.76836 -2.06136 -2.49822 -0.433195 -0.252887 -5.34487  2.27781  1.41649 0.454479  1.24226  1.72277  1.70997  1.51543 0.709684 -2.20383 -0.492742 0.330698  2.31472  1.06093 0.188657 -0.921728 0.537492 -1.77865 -0.388827 -2.02005 -1.87799 -1.01827  2.95393 -0.716202 -5.08253 0.402104
 19:     2133.5860: -0.170461 -1.12559  1.45757  1.72063  1.40650  2.18347  2.15999  2.15745  2.82012  2.29465 -1.02280 -0.0350360 -1.21851 -0.845387 -0.791798 -2.28553 -2.33754 -2.50483 -1.39200 -0.881605 -1.74107 -2.03189 -2.48796 -0.608358 -0.133610 -5.29524  2.24434  1.36421 0.470990  1.19255  1.72006  1.71566  1.53737 0.709700 -2.14450 -0.419947 0.351217  2.29270  1.06522 0.202929 -0.937275 0.555079 -1.74974 -0.342196 -2.06142 -1.90701 -1.03987  2.96613 -0.575754 -5.08917 0.502361
 20:     2132.6831: -0.161176 -1.12866  1.42524  1.62535  1.35332  2.11755  2.00096  2.14040  2.90105  2.27212 -0.975475 -0.00737708 -1.18017 -0.807969 -0.761843 -2.26783 -2.31994 -2.48665 -1.34719 -0.845112 -1.70540 -1.99272 -2.46999 -0.798934 0.0350731 -5.22383  2.20162  1.30970 0.482373  1.16595  1.69500  1.70574  1.56713 0.752910 -2.07628 -0.343996 0.372433  2.26198  1.06538 0.218192 -0.955411 0.573782 -1.71731 -0.293941 -2.10928 -1.94078 -1.06486  2.97500 -0.425082 -5.10382 0.414018
 21:     2131.8623: -0.143244 -1.12537  1.45308  1.59243  1.32935  2.17159  1.97419  2.18642  2.62677  2.40197 -0.938263 0.00696932 -1.15006 -0.783300 -0.751163 -2.24868 -2.29969 -2.46676 -1.31040 -0.824779 -1.67283 -1.95587 -2.45003 -0.953321 0.0489850 -5.24177  2.14377  1.28473 0.475657  1.23583  1.60577  1.61195  1.62435 0.865348 -2.02114 -0.295052 0.386944  2.21564  1.05253 0.229038 -0.974626 0.586723 -1.69546 -0.265584 -2.15737 -1.97687 -1.08979  2.98124 -0.377771 -5.14901 0.428668
 22:     2131.5765: -0.142518 -1.12529  1.45288  1.59398  1.32935  2.17126  1.98096  2.17466  2.64817  2.38666 -0.938150 0.00561010 -1.14981 -0.783357 -0.751468 -2.24842 -2.29939 -2.46651 -1.31000 -0.824934 -1.67234 -1.95529 -2.44978 -0.950134 0.0506898 -5.24000  2.14339  1.28500 0.475539  1.23762  1.60626  1.61236  1.62552 0.863046 -2.01992 -0.294376 0.387478  2.21493  1.05243 0.229427 -0.975286 0.587170 -1.69495 -0.264861 -2.15903 -1.97809 -1.09066  2.98124 -0.375492 -5.14732 0.466465
 23:     2131.0195: -0.140810 -1.12615  1.45634  1.59893  1.32932  2.17871  2.00273  2.15780  2.65243  2.36941 -0.936190 0.00256397 -1.14779 -0.782482 -0.752101 -2.24689 -2.29772 -2.46495 -1.30725 -0.824587 -1.66953 -1.95203 -2.44824 -0.949752 0.0506936 -5.24086  2.14010  1.28551 0.474416  1.24892  1.60173  1.60695  1.62822 0.866780 -2.01406 -0.290557 0.389536  2.21099  1.05133 0.230911 -0.978059 0.588893 -1.69276 -0.261847 -2.16592 -1.98327 -1.09424  2.97991 -0.370331 -5.14823 0.439875
 24:     2130.5707: -0.134567 -1.12798  1.46256  1.61353  1.32947  2.18970  2.05259  2.13208  2.67024  2.32668 -0.932305 -0.00834815 -1.14315 -0.781305 -0.754873 -2.24320 -2.29361 -2.46124 -1.30061 -0.824819 -1.66238 -1.94366 -2.44456 -0.941003 0.0446953 -5.24314  2.13338  1.28809 0.471957  1.27751  1.59244  1.60141  1.63187 0.868152 -1.99729 -0.278985 0.396003  2.20131  1.04894 0.235455 -0.986436 0.594111 -1.68654 -0.252568 -2.18672 -1.99890 -1.10504  2.97597 -0.357338 -5.14762 0.460510
 25:     2130.0027: -0.113092 -1.13423  1.46231  1.65311  1.33199  2.16806  2.09107  2.17822  2.69317  2.31937 -0.929071 -0.0460238 -1.13457 -0.783622 -0.766413 -2.23504 -2.28427 -2.45311 -1.28676 -0.830528 -1.64517 -1.92308 -2.43665 -0.875979 0.0130271 -5.25306  2.13020  1.30125 0.468571  1.33771  1.58413  1.63381  1.61996 0.837514 -1.94792 -0.242896 0.417779  2.18209  1.04579 0.250356 -1.01335 0.610871 -1.66820 -0.222126 -2.25360 -2.04892 -1.13981  2.95947 -0.329032 -5.13427 0.445586
 26:     2129.9808: -0.101301 -1.13459  1.46320  1.66140  1.33536  2.17035  2.09997  2.09833  2.77826  2.30471 -0.926354 -0.0496097 -1.13016 -0.782616 -0.767981 -2.23082 -2.27958 -2.44891 -1.28046 -0.830587 -1.63735 -1.91397 -2.43255 -0.841222 0.00666231 -5.24078  2.12891  1.30492 0.468328  1.35144  1.59028  1.63442  1.63276 0.831661 -1.92998 -0.232964 0.426118  2.17303  1.04470 0.256720 -1.02471 0.618113 -1.66061 -0.210968 -2.28237 -2.06978 -1.15484  2.95686 -0.301552 -5.12385 0.421662
 27:     2129.5644: -0.0925745 -1.13901  1.46527  1.66719  1.33924  2.17284  2.09255  2.09981  2.77615  2.31755 -0.923912 -0.0510613 -1.12597 -0.781615 -0.769344 -2.22683 -2.27513 -2.44491 -1.27454 -0.830519 -1.62988 -1.90519 -2.42864 -0.816948 0.00276899 -5.24257  2.13044  1.30995 0.468484  1.36399  1.59537  1.64129  1.63263 0.831357 -1.91218 -0.222302 0.434621  2.16551  1.04392 0.263159 -1.03654 0.625394 -1.65333 -0.199717 -2.31216 -2.09147 -1.17040  2.94942 -0.286062 -5.12122 0.447382
 28:     2129.1295: -0.0449213 -1.16232  1.48998  1.65281  1.36056  2.24257  2.07171  2.09231  2.73440  2.28307 -0.902698 -0.00815346 -1.09976 -0.766085 -0.761989 -2.20295 -2.24893 -2.42066 -1.24103 -0.818446 -1.58880 -1.85765 -2.40480 -0.760904 0.0146128 -5.25267  2.13836  1.33315 0.472793  1.40445  1.63130  1.62385  1.66860 0.898163 -1.83212 -0.183914 0.474614  2.12491  1.04000 0.296207 -1.09909 0.663258 -1.61857 -0.149805 -2.47088 -2.20519 -1.25355  2.90515 -0.211899 -5.13589 0.443679
 29:     2128.2376: 0.0941253 -1.19288  1.47733  1.62249  1.37222  2.16789  2.12790  2.13467  2.74425  2.37240 -0.866061 0.0409078 -1.04854 -0.736774 -0.743821 -2.14884 -2.18979 -2.36548 -1.17647 -0.794138 -1.50266 -1.75781 -2.35069 -0.643845 0.0203367 -5.24545  2.17705  1.39548 0.496993  1.45605  1.71722  1.71792  1.74817 0.981659 -1.66530 -0.105969 0.566555  2.05324  1.04244 0.374715 -1.24645 0.752633 -1.54129 -0.0401326 -2.84744 -2.46968 -1.45157  2.79883 -0.0759973 -5.14738 0.443180
 30:     2128.0917: 0.258290 -1.21701  1.46178  1.62768  1.36888  2.19076  2.09638  2.26679  2.84513  2.26565 -0.835164 0.0753798 -1.00760 -0.702961 -0.705029 -2.09750 -2.13443 -2.31315 -1.13075 -0.759385 -1.43338 -1.67932 -2.29932 -0.617669 0.0167714 -5.20054  2.24678  1.46560 0.556732  1.47252  1.81523  1.85162  1.86150 0.999189 -1.54602 -0.0610655 0.652200  2.02005  1.06941 0.456190 -1.39630 0.846035 -1.46981 0.0501646 -3.23827 -2.72706 -1.65968  2.72004 0.0405441 -5.17077 0.454657
 31:     2127.4336: 0.335223 -1.24801  1.47271  1.70894  1.36684  2.24599  2.12124  2.25696  2.84813  2.30384 -0.827223 0.0342011 -0.996300 -0.691170 -0.688005 -2.07569 -2.11114 -2.29139 -1.12053 -0.745735 -1.41157 -1.65590 -2.27787 -0.619533 -0.0128480 -5.18703  2.28997  1.50480 0.606756  1.52094  1.84671  1.91758  1.87770 0.967243 -1.50100 -0.0328514 0.695307  2.02643  1.09860 0.499933 -1.47212 0.896012 -1.43151 0.0930672 -3.44117 -2.84669 -1.77005  2.70006 0.0773322 -5.17269 0.437662
 32:     2126.8559: 0.409545 -1.29134  1.50964  1.76281  1.38296  2.23153  2.20581  2.27251  2.85210  2.32606 -0.826572 0.00550567 -0.997139 -0.683099 -0.670504 -2.06016 -2.09534 -2.27651 -1.12713 -0.734025 -1.40985 -1.65694 -2.26319 -0.652740 -0.0124909 -5.15397  2.34440  1.53020 0.672772  1.55096  1.87512  1.83869  1.90624  1.02748 -1.48655 -0.00807199 0.731802  2.07111  1.14749 0.544805 -1.54454 0.947389 -1.39357 0.124186 -3.64526 -2.93876 -1.88657  2.68061 0.109546 -5.18651 0.444853
 33:     2126.1756: 0.576302 -1.37915  1.63539  1.75282  1.49551  2.29544  2.24017  2.30639  2.88930  2.42095 -0.819502 0.0714542 -1.00150 -0.673529 -0.663426 -2.03930 -2.07473 -2.25971 -1.13866 -0.726447 -1.41921 -1.67530 -2.24659 -0.567476 0.0267171 -5.08307  2.39946  1.55330 0.757023  1.66263  1.84306  1.93713  1.92963  1.11752 -1.44901 0.0707898 0.803668  2.16775  1.23976 0.639901 -1.69525  1.05413 -1.31319 0.183859 -4.08085 -3.09387 -2.14740  2.60155 0.134699 -5.18509 0.449751
 34:     2125.6330: 0.793272 -1.45610  1.57008  1.76606  1.54360  2.30337  2.26229  2.29365  2.87083  2.45279 -0.767728 0.212227 -0.971459 -0.631656 -0.636416 -2.01274 -2.04890 -2.23754 -1.10927 -0.691991 -1.40929 -1.67318 -2.22456 -0.606775 0.0209859 -5.05809  2.40017  1.60719 0.795966  1.73973  1.94337  1.98853  1.98635  1.15725 -1.40255 0.148451 0.871673  2.25275  1.32141 0.740082 -1.84893  1.16540 -1.23197 0.240438 -4.53561 -3.20007 -2.44430  2.53814 0.135364 -5.21922 0.436953
 35:     2125.2774:  1.05432 -1.54337  1.60891  1.84320  1.46080  2.33992  2.22777  2.28393  2.88413  2.49123 -0.716182 0.117178 -0.924335 -0.590333 -0.607315 -1.97823 -2.01509 -2.20672 -1.05645 -0.655959 -1.38000 -1.64702 -2.19390 -0.530919 -0.00253915 -5.03877  2.44165  1.68857 0.801650  1.76024  2.06453  2.01488  2.02848  1.17624 -1.34218 0.197671 0.930813  2.32169  1.38291 0.841932 -1.99024  1.27536 -1.14961 0.291574 -4.95307 -3.21670 -2.77753  2.45916 0.114697 -5.24256 0.435452
 36:     2125.2314:  1.39545 -1.63261  1.65407  1.78456  1.43328  2.37846  2.32771  2.21835  2.85317  2.45260 -0.698188 0.0279950 -0.889824 -0.571866 -0.581954 -1.94591 -1.98462 -2.17784 -1.01807 -0.633995 -1.35424 -1.62362 -2.16478 -0.613878 -0.0220902 -5.02026  2.49422  1.72033 0.831570  1.72373  2.02964  2.12559  2.06902  1.16972 -1.30943 0.217941 0.967213  2.37876  1.43036 0.943703 -2.10321  1.38170 -1.07691 0.321846 -5.26090 -3.09828 -3.16203  2.37761 0.0434155 -5.30758 0.440552
 37:     2124.6664:  1.58026 -1.69924  1.61125  1.80252  1.47629  2.35341  2.28810  2.24687  2.90020  2.43548 -0.723223 0.0193529 -0.893514 -0.590168 -0.589879 -1.93261 -1.97227 -2.16514 -1.02108 -0.647174 -1.34702 -1.61550 -2.15196 -0.598159 0.00265935 -4.99577  2.51854  1.71081 0.858057  1.75914  1.98172  2.05632  2.05283  1.17864 -1.29776 0.215359 0.973844  2.39502  1.44111 0.989083 -2.13499  1.42645 -1.04612 0.332215 -5.30662 -2.98572 -3.36344  2.32530 0.0183188 -5.35079 0.429374
 38:     2124.2574:  1.79144 -1.77474  1.59153  1.84327  1.47026  2.32523  2.25457  2.24379  2.90375  2.42473 -0.745936 0.0901363 -0.909368 -0.607827 -0.602710 -1.92120 -1.96076 -2.15238 -1.03908 -0.663010 -1.34435 -1.61015 -2.13917 -0.588392 0.00168002 -4.99196  2.49336  1.69499 0.866530  1.79870  2.02369  2.03383  2.02553  1.14615 -1.30404 0.199566 0.968430  2.39504  1.43517  1.02441 -2.15041  1.45767 -1.03731 0.331199 -5.26737 -2.89446 -3.56291  2.26109 -0.0170181 -5.39973 0.443028
 39:     2123.6045:  2.70763 -2.11856  1.59890  1.72913  1.33980  2.28830  2.20925  2.26023  2.87742  2.40878 -0.781490 0.0857297 -0.954709 -0.636171 -0.630217 -1.87767 -1.91622 -2.09929 -1.09057 -0.691444 -1.33991 -1.59343 -2.08703 -0.546108 0.0423863 -4.94808  2.41027  1.63372 0.839062  1.75581  2.10710  1.99784  2.04173  1.30282 -1.34237 0.153721 0.940209  2.42112  1.41053  1.16476 -2.21490  1.57900 -1.02400 0.323477 -5.12748 -2.61783 -4.40315  1.93361 -0.0952101 -5.60841 0.447365
 40:     2123.3362:  2.90582 -2.21353  1.60211  1.72656  1.37524  2.25789  2.16560  2.23725  2.85819  2.40242 -0.772807 0.0503655 -0.954495 -0.633515 -0.634227 -1.87126 -1.90908 -2.08926 -1.08808 -0.691658 -1.34019 -1.59057 -2.07752 -0.602573 0.0348434 -4.93543  2.39476  1.63868 0.839007  1.78651  2.05073  1.97624  2.03985  1.26357 -1.33605 0.188292 0.938501  2.41941  1.40380  1.19803 -2.22558  1.60375 -1.02320 0.338956 -5.09028 -2.58657 -4.62267  1.90171 -0.0153487 -5.65887 0.444977
 41:     2123.1162:  3.13431 -2.37735  1.48062  1.76280  1.51199  2.39779  2.26586  2.27336  2.90911  2.45803 -0.792364 0.0207727 -0.992359 -0.665245 -0.679926 -1.92238 -1.95948 -2.13207 -1.12068 -0.731095 -1.41517 -1.66788 -2.12236 -0.647602 -0.0565164 -4.85260  2.40243  1.63543 0.807259  1.84255  1.99525  1.93849  1.98742  1.15751 -1.38186 0.221727 0.897938  2.41294  1.36386  1.21678 -2.15937  1.58197 -1.09934 0.344623 -4.80543 -2.56917 -5.03494  2.06005 -0.0224465 -5.62708 0.433769
 42:     2122.8603:  3.12178 -2.39192  1.55926  1.84832  1.53113  2.35241  2.26742  2.27020  2.89944  2.44370 -0.797369 0.0680274 -1.00167 -0.670245 -0.684435 -1.95320 -1.99041 -2.16162 -1.12971 -0.736821 -1.44301 -1.69906 -2.15255 -0.690007 -0.0740003 -4.82201  2.40711  1.62187 0.794912  1.84012  1.96584  1.95741  2.00446  1.15267 -1.40599 0.200865 0.876641  2.39209  1.34048  1.20000 -2.11432  1.54761 -1.14146 0.334021 -4.68244 -2.59969 -5.10535  2.16251 -0.0441766 -5.60122 0.430601
 43:     2122.6927:  3.05947 -2.38048  1.59898  1.80551  1.45707  2.34524  2.25249  2.29336  2.89926  2.45840 -0.786533 0.0974035 -0.979838 -0.648478 -0.648442 -1.97264 -2.00930 -2.18276 -1.11092 -0.709189 -1.43210 -1.69124 -2.17368 -0.760801 -0.0221723 -4.77446  2.40712  1.59513 0.833162  1.84665  1.97360  1.95425  2.00149  1.13137 -1.39207 0.182806 0.871078  2.34223  1.32344  1.16933 -2.06694  1.49499 -1.15940 0.334950 -4.62537 -2.69192 -5.11866  2.27184 0.00585679 -5.56735 0.436615
 44:     2122.5830:  3.18293 -2.41656  1.57765  1.82558  1.52167  2.32189  2.24100  2.28557  2.88167  2.44800 -0.773356 0.0825905 -0.951638 -0.623357 -0.609069 -1.98115 -2.01807 -2.19660 -1.08771 -0.677968 -1.40565 -1.66939 -2.18695 -0.759601 0.00832715 -4.73645  2.43054  1.60147 0.873835  1.79941  1.98173  1.98891  2.02466  1.16112 -1.38128 0.152547 0.874197  2.32302  1.32968  1.16409 -2.05309  1.46642 -1.14681 0.328735 -4.68783 -2.75781 -5.25763  2.30079 0.00585546 -5.56707 0.444075
 45:     2122.5255:  3.34708 -2.47690  1.63482  1.78895  1.51533  2.29421  2.25242  2.27340  2.87822  2.43448 -0.767995 0.115257 -0.942661 -0.619595 -0.607989 -1.98368 -2.02157 -2.20455 -1.08115 -0.674959 -1.38672 -1.65350 -2.19407 -0.746351 0.0184397 -4.70570  2.42707  1.61226 0.872739  1.80635  2.00999  1.97184  2.00447  1.12769 -1.38470 0.157194 0.874109  2.33304  1.34635  1.16132 -2.03629  1.43990 -1.12541 0.320432 -4.74325 -2.77090 -5.40375  2.33037 -0.00408215 -5.56917 0.442575
 46:     2122.4583:  3.45818 -2.51282  1.61766  1.80795  1.44933  2.29662  2.25183  2.25587  2.87393  2.42677 -0.765185 0.135583 -0.945972 -0.626765 -0.628107 -1.98252 -2.02153 -2.20743 -1.08312 -0.687041 -1.37265 -1.63904 -2.19626 -0.760608 0.0408776 -4.66705  2.38380  1.60050 0.831098  1.80638  1.97007  1.97671  2.00959  1.14768 -1.39242 0.173255 0.869054  2.34430  1.35391  1.14598 -2.00966  1.40186 -1.11226 0.313261 -4.76990 -2.77834 -5.48123  2.37874 0.00303498 -5.56381 0.441712
 47:     2122.4156:  3.53004 -2.51602  1.60170  1.76166  1.48789  2.29078  2.20229  2.22516  2.85781  2.41615 -0.760594 0.0634906 -0.972179 -0.645698 -0.676724 -1.97849 -2.01921 -2.20910 -1.09887 -0.718540 -1.36357 -1.62184 -2.19666 -0.842631 0.0488066 -4.59350  2.29167  1.54355 0.711783  1.75113  2.00873  1.95984  2.00424  1.16489 -1.41906 0.176669 0.844991  2.33369  1.32977  1.06433 -1.91756  1.26971 -1.12469 0.295833 -4.74318 -2.81677 -5.42112  2.60379 -0.0201852 -5.49516 0.435195
 48:     2122.3247:  3.68342 -2.57144  1.56171  1.77420  1.45226  2.32409  2.22170  2.25156  2.86657  2.43722 -0.776583 0.119594 -0.978691 -0.635992 -0.635070 -1.95928 -1.99888 -2.18785 -1.10020 -0.696939 -1.39042 -1.63910 -2.17557 -0.851197 0.0268306 -4.51257  2.46531  1.57641 0.746481  1.68003  1.92774  1.92950  1.98242  1.11486 -1.42680 0.0954545 0.831644  2.29740  1.28380 0.999959 -1.88234  1.16981 -1.15328 0.293698 -4.80903 -2.88035 -5.35899  2.76108 -0.00620045 -5.43357 0.430083
 49:     2122.2297:  3.91373 -2.64953  1.58027  1.83158  1.46194  2.33817  2.27662  2.29431  2.89434  2.44882 -0.769897 0.0942522 -0.944500 -0.605910 -0.570627 -1.94716 -1.98523 -2.16917 -1.07932 -0.651079 -1.42126 -1.67583 -2.15803 -0.890885 0.0564026 -4.41693  2.36748  1.54571 0.850006  1.80511  1.92818  1.94756  1.97078  1.10852 -1.46077 0.0439604 0.808112  2.26872  1.24992 0.967052 -1.90139  1.12587 -1.19802 0.273910 -4.90717 -2.90375 -5.35052  2.85670 -0.00395017 -5.39874 0.433598
 50:     2122.1998:  4.08068 -2.69069  1.63726  1.83268  1.48773  2.34212  2.28032  2.29357  2.90620  2.45114 -0.742513 0.128565 -0.921000 -0.630711 -0.670938 -1.95840 -1.99642 -2.17751 -1.06366 -0.706697 -1.39511 -1.66795 -2.16744 -0.967739 0.0218434 -4.35980  2.30353  1.57004 0.751447  1.67744  1.89718  1.89051  1.89631  1.08526 -1.49506 0.170198 0.783523  2.28534  1.27297 0.934772 -1.92113  1.10040 -1.22576 0.240838 -4.91085 -2.86855 -5.28730  3.03004 0.0100428 -5.34864 0.444951
 51:     2122.1302:  4.12757 -2.70742  1.62091  1.79033  1.48214  2.32206  2.25850  2.26903  2.88702  2.44215 -0.746399 0.113244 -0.927891 -0.632293 -0.670130 -1.95843 -1.99696 -2.17774 -1.06681 -0.707856 -1.37459 -1.64826 -2.16804 -0.982198 0.0110523 -4.33562  2.32831  1.53785 0.698067  1.71662  1.87959  1.87435  1.92025  1.06302 -1.51166 0.128751 0.770380  2.29161  1.27578 0.921899 -1.92736  1.08948 -1.23308 0.219154 -4.90352 -2.85825 -5.28198  3.09476 -0.00967957 -5.33543 0.446359
 52:     2122.0511:  4.25121 -2.71057  1.59230  1.79383  1.47552  2.31817  2.23095  2.25115  2.87589  2.43354 -0.793461 0.101687 -0.982290 -0.630238 -0.593380 -1.95205 -1.99043 -2.17530 -1.10392 -0.675460 -1.35054 -1.60770 -2.16488 -1.04858 0.0251800 -4.26185  2.31477  1.44202 0.729571  1.68355  1.90612  1.87751  1.90701  1.05469 -1.49990 0.0256715 0.758775  2.24133  1.24485 0.894986 -1.94507  1.06076 -1.23126 0.220335 -4.89765 -2.88141 -5.30430  3.24271 -0.00160606 -5.29582 0.435584
 53:     2122.0367:  4.33399 -2.73147  1.58349  1.78964  1.48840  2.32016  2.24793  2.27241  2.88159  2.44275 -0.730942 0.101558 -0.941772 -0.604610 -0.627328 -1.94506 -1.98330 -2.16788 -1.07631 -0.673133 -1.38077 -1.63283 -2.15753 -1.10530 0.0558504 -4.17017  2.27803  1.58485 0.699502  1.69622  1.87398  1.86856  1.91026  1.03802 -1.53559 -0.0308293 0.735299  2.21122  1.20244 0.869277 -1.98193  1.04565 -1.25770 0.196302 -4.91137 -2.91853 -5.28427  3.40039 -0.00746485 -5.23545 0.433694
 54:     2121.9770:  4.48915 -2.76218  1.59580  1.81016  1.48963  2.32837  2.26347  2.28605  2.89219  2.45071 -0.715330 0.107632 -0.899305 -0.602530 -0.640656 -1.93937 -1.97746 -2.16054 -1.03940 -0.678125 -1.39707 -1.65500 -2.15056 -1.17999 0.0442728 -4.09155  2.32649  1.48884 0.671689  1.70308  1.86120  1.85768  1.89240  1.03414 -1.55911 0.0428974 0.721482  2.20556  1.18467 0.863530 -2.03992  1.05656 -1.27972 0.182514 -4.96611 -2.93788 -5.30721  3.55408 -0.0125852 -5.18232 0.437014
 55:     2121.9448:  4.61266 -2.77074  1.61206  1.79753  1.47969  2.33030  2.25812  2.27160  2.88921  2.44542 -0.795405 0.114698 -0.945304 -0.630634 -0.594110 -1.93896 -1.97695 -2.15857 -1.07231 -0.675815 -1.37336 -1.63987 -2.14887 -1.25494 0.00192966 -4.03465  2.25830  1.44755 0.699569  1.64863  1.82322  1.82076  1.86139  1.00644 -1.56525 0.0259540 0.711182  2.22426  1.19988 0.858462 -2.09273  1.07317 -1.29448 0.171915 -4.97930 -2.93332 -5.29938  3.74023 -0.0101983 -5.13098 0.441113
 56:     2121.9124:  4.74066 -2.77244  1.60550  1.80227  1.48079  2.32479  2.24980  2.26748  2.88611  2.43898 -0.740791 0.111492 -0.971366 -0.617764 -0.641020 -1.93998 -1.97748 -2.16025 -1.10284 -0.686494 -1.35543 -1.61860 -2.15008 -1.34740 0.00878047 -3.94887  2.25278  1.41121 0.661241  1.62662  1.82954  1.81250  1.84255 0.989300 -1.57383 -0.0355712 0.694034  2.18343  1.18629 0.847325 -2.13358  1.07611 -1.30597 0.157189 -4.96893 -2.95078 -5.30913  3.91364 -0.00248735 -5.08247 0.439336
 57:     2121.8894:  4.85540 -2.76017  1.59367  1.80348  1.48507  2.32036  2.24692  2.26946  2.88472  2.43874 -0.760575 0.108444 -0.932151 -0.618168 -0.610515 -1.94436 -1.98182 -2.16600 -1.06637 -0.675783 -1.36777 -1.62483 -2.15540 -1.45272 0.0180557 -3.85682  2.24376  1.41914 0.606219  1.61715  1.82267  1.80176  1.82718 0.975078 -1.60477 -0.0401549 0.668913  2.14238  1.15118 0.835135 -2.17691  1.07864 -1.32501 0.128528 -4.96389 -2.97104 -5.32155  4.12032 -0.00309720 -5.01806 0.436566
 58:     2121.8732:  4.97114 -2.74832  1.59439  1.80052  1.48372  2.32472  2.25005  2.27299  2.88780  2.44444 -0.733629 0.112287 -0.920797 -0.606741 -0.625723 -1.94210 -1.97961 -2.16324 -1.04785 -0.672690 -1.37731 -1.63238 -2.15282 -1.56257 -0.000408069 -3.77786  2.21893  1.40563 0.642829  1.60030  1.79309  1.78081  1.81425 0.957867 -1.62635 -0.0554612 0.650605  2.13952  1.12380 0.831322 -2.22005  1.08824 -1.34547 0.110955 -4.99155 -2.98802 -5.35457  4.33934 -0.00876345 -4.95508 0.436330
 59:     2121.8627:  5.00000 -2.68802  1.60883  1.80741  1.49119  2.33239  2.26301  2.28209  2.89445  2.44868 -0.750807 0.119159 -0.961708 -0.612569 -0.609909 -1.93104 -1.96795 -2.15015 -1.09866 -0.673176 -1.36490 -1.62576 -2.13991 -1.67322 -0.0216427 -3.72623  2.21074  1.40988 0.602476  1.59705  1.78069  1.77452  1.81037 0.952588 -1.62339 -0.0650910 0.647752  2.14621  1.12649 0.839022 -2.24245  1.10577 -1.35490 0.115717 -5.03379 -3.00638 -5.37497  4.49484 -0.000302300 -4.91987 0.438757
 60:     2121.8527:  5.00000 -2.66477  1.60133  1.80244  1.48075  2.32394  2.25111  2.26968  2.88537  2.43950 -0.767319 0.108914 -0.940280 -0.626108 -0.627404 -1.93869 -1.97576 -2.15900 -1.07178 -0.685238 -1.37155 -1.63493 -2.14854 -1.68779 -0.0212933 -3.73799  2.20798  1.39696 0.611908  1.58965  1.78404  1.77232  1.80356 0.948188 -1.62661 -0.0759281 0.647516  2.13948  1.13799 0.835085 -2.20941  1.09085 -1.34981 0.110235 -5.00577 -2.99309 -5.37625  4.48674 -0.00165808 -4.93809 0.438636
 61:     2121.8504:  5.00000 -2.64450  1.59684  1.80017  1.48062  2.32064  2.24796  2.26821  2.88550  2.43844 -0.742096 0.109228 -0.945940 -0.608263 -0.606236 -1.94803 -1.98524 -2.16899 -1.07205 -0.669550 -1.37840 -1.63550 -2.15867 -1.68986 -0.0218967 -3.74856  2.21590  1.39950 0.619018  1.59412  1.79060  1.77716  1.80703 0.953604 -1.63382 -0.0514754 0.645164  2.14279  1.13193 0.827278 -2.17268  1.06751 -1.35017 0.102654 -4.98715 -2.98745 -5.38070  4.46929 -0.00281398 -4.95638 0.437739
 62:     2121.8470:  5.00000 -2.62345  1.60149  1.80429  1.48800  2.32527  2.25263  2.27284  2.88855  2.44308 -0.755803 0.114031 -0.934344 -0.615770 -0.620490 -1.94324 -1.98032 -2.16354 -1.06526 -0.675456 -1.36869 -1.62368 -2.15349 -1.70164 -0.0221284 -3.74373  2.22720  1.40760 0.625420  1.60478  1.80117  1.78755  1.81903 0.962682 -1.62492 -0.0552967 0.650247  2.15153  1.13094 0.826220 -2.16011  1.05830 -1.34634 0.110687 -5.00661 -2.99064 -5.38761  4.46617 0.00159130 -4.96568 0.437342
 63:     2121.8449:  5.00000 -2.58278  1.60221  1.80573  1.48753  2.32538  2.25668  2.27225  2.88721  2.44265 -0.753320 0.110271 -0.935663 -0.618661 -0.619288 -1.93756 -1.97474 -2.15806 -1.06971 -0.681271 -1.36923 -1.63225 -2.14794 -1.72389 -0.0211556 -3.72951  2.22836  1.40870 0.620673  1.60773  1.79501  1.78675  1.81581 0.961918 -1.61299 -0.0622658 0.657076  2.15358  1.14341 0.824538 -2.15839  1.05583 -1.33885 0.122647 -5.01239 -2.98357 -5.36602  4.50037 0.00268288 -4.96183 0.437776
 64:     2121.8426:  5.00000 -2.54183  1.60191  1.80480  1.48514  2.32494  2.25488  2.27208  2.88710  2.44140 -0.757547 0.110199 -0.943314 -0.614885 -0.623979 -1.93602 -1.97316 -2.15630 -1.07296 -0.672911 -1.37284 -1.63463 -2.14620 -1.73287 -0.0245225 -3.72326  2.23476  1.41766 0.628163  1.61402  1.80354  1.79368  1.82316 0.969016 -1.61165 -0.0503543 0.663122  2.15836  1.15114 0.826050 -2.15283  1.05559 -1.33475 0.126514 -5.00232 -2.97994 -5.35004  4.51208 0.00382676 -4.96612 0.438102
 65:     2121.8386:  5.00000 -2.38812  1.60341  1.80359  1.48231  2.32630  2.25068  2.27402  2.88953  2.44205 -0.743785 0.113925 -0.947255 -0.620096 -0.603152 -1.93423 -1.97132 -2.15382 -1.07793 -0.688156 -1.37454 -1.62913 -2.14388 -1.75011 -0.0338616 -3.70471  2.26482  1.45218 0.664646  1.64221  1.84078  1.82499  1.85632  1.00123 -1.59191 -0.00932436 0.690811  2.18776  1.17808 0.841029 -2.12902  1.06430 -1.31044 0.149301 -4.96186 -2.95626 -5.30365  4.52953 0.00531830 -4.98759 0.438541
 66:     2121.8331:  5.00000 -2.24258  1.60554  1.80539  1.48653  2.32869  2.25391  2.27652  2.89232  2.44673 -0.748163 0.116088 -0.939178 -0.601451 -0.611547 -1.93492 -1.97224 -2.15481 -1.07349 -0.656631 -1.36533 -1.62081 -2.14487 -1.75109 -0.0349064 -3.68870  2.29649  1.47925 0.692825  1.67243  1.86822  1.85383  1.88357  1.03151 -1.55119 0.0211586 0.722835  2.22310  1.20592 0.867670 -2.10811  1.08999 -1.27438 0.186150 -4.92719 -2.91669 -5.26794  4.53355 0.00192658 -5.00208 0.438111
 67:     2121.8275:  5.00000 -2.13629  1.60281  1.80371  1.48723  2.32691  2.25530  2.27496  2.88955  2.44485 -0.753027 0.114028 -0.947619 -0.606975 -0.619482 -1.93126 -1.96858 -2.15139 -1.06173 -0.662129 -1.36497 -1.62556 -2.14131 -1.73448 -0.0383227 -3.68491  2.32441  1.50488 0.721326  1.70168  1.89384  1.88138  1.91048  1.05888 -1.52412 0.0464613 0.749714  2.24506  1.23315 0.903549 -2.09618  1.13381 -1.24660 0.214315 -4.90655 -2.88897 -5.24667  4.52543 -6.74897e-07 -5.00307 0.437764
 68:     2121.8193:  5.00000 -1.92257  1.60099  1.80259  1.48676  2.32653  2.25670  2.27392  2.88845  2.44366 -0.756627 0.113871 -0.924784 -0.612315 -0.623880 -1.92761 -1.96486 -2.14769 -1.07146 -0.670416 -1.36921 -1.63075 -2.13742 -1.69731 -0.0531753 -3.69152  2.37675  1.55642 0.775582  1.75542  1.94646  1.93576  1.96433  1.11261 -1.46668 0.0915585 0.806222  2.29693  1.29231 0.979701 -2.05760  1.22512 -1.18943 0.273304 -4.85128 -2.83229 -5.20324  4.49599 -0.00509999 -5.00528 0.437567
 69:     2121.8126:  5.00000 -1.70514  1.60202  1.80450  1.48710  2.32782  2.25807  2.27499  2.88981  2.44510 -0.753285 0.114840 -0.933141 -0.616728 -0.619843 -1.92770 -1.96494 -2.14764 -1.05347 -0.675854 -1.36460 -1.62564 -2.13729 -1.66563 -0.0702194 -3.70769  2.42923  1.61036 0.826174  1.80783  1.99911  1.98903  2.01652  1.16501 -1.40902 0.138676 0.861224  2.35290  1.34720  1.05126 -2.00201  1.30599 -1.13243 0.328608 -4.79373 -2.77539 -5.15769  4.46114 -0.0102517 -5.00787 0.437615
 70:     2121.8065:  5.00000 -1.47711  1.60026  1.80364  1.48611  2.32597  2.25709  2.27345  2.88803  2.44325 -0.753955 0.112777 -0.932360 -0.617249 -0.619461 -1.92886 -1.96607 -2.14881 -1.06076 -0.682938 -1.36084 -1.62403 -2.13848 -1.63949 -0.0907119 -3.73054  2.48167  1.66448 0.880777  1.86064  2.05159  2.04180  2.06869  1.21753 -1.35918 0.194916 0.913042  2.40627  1.39695  1.11409 -1.93354  1.37195 -1.08111 0.376623 -4.74050 -2.72233 -5.10538  4.43196 -0.0114850 -5.00738 0.437571
 71:     2121.7999:  5.00000 -1.07531  1.60188  1.80435  1.48677  2.32590  2.25576  2.27367  2.88913  2.44293 -0.744985 0.113563 -0.935836 -0.630343 -0.614021 -1.93250 -1.96952 -2.15191 -1.06244 -0.671794 -1.37595 -1.63252 -2.14185 -1.59849 -0.127204 -3.78285  2.56514  1.75144 0.960040  1.94447  2.13848  2.12749  2.15497  1.30413 -1.27389 0.275107  1.00156  2.49827  1.48845  1.20624 -1.80066  1.45827 -0.996650 0.463558 -4.65039 -2.63632 -5.01387  4.36706 -0.00714827 -5.01014 0.437773
 72:     2121.7983:  5.00000 -0.924993  1.60135  1.80617  1.48502  2.32504  2.25389  2.27344  2.88833  2.44284 -0.759704 0.109633 -0.942554 -0.587985 -0.613186 -1.93580 -1.97289 -2.15535 -1.06891 -0.695475 -1.36889 -1.62586 -2.14545 -1.59320 -0.127905 -3.80501  2.58907  1.77853 0.984242  1.96784  2.15996  2.14915  2.17607  1.32453 -1.25474 0.304307  1.02401  2.52272  1.50907  1.21918 -1.75482  1.46035 -0.974263 0.480158 -4.62749 -2.61230 -4.98304  4.34240 -0.00360062 -5.01065 0.437920
 73:     2121.7929:  5.00000 -0.943958  1.59930  1.80596  1.48322  2.32338  2.25249  2.27223  2.88617  2.44192 -0.753446 0.105934 -0.942351 -0.614920 -0.617422 -1.93737 -1.97461 -2.15735 -1.08059 -0.677911 -1.35521 -1.61784 -2.14747 -1.60452 -0.107886 -3.80266  2.57365  1.76406 0.972098  1.95180  2.14096  2.13075  2.15737  1.30505 -1.27602 0.296604  1.00432  2.50311  1.48423  1.18751 -1.77405  1.42017 -0.992928 0.455728 -4.64761 -2.62939 -4.99368  4.34608 -0.000571431 -5.00953 0.437914
 74:     2121.7859:  5.00000 -0.933157  1.60049  1.80311  1.48530  2.32350  2.25295  2.27177  2.88711  2.44133 -0.748189 0.110304 -0.939943 -0.625875 -0.617901 -1.93835 -1.97553 -2.15827 -1.07686 -0.664130 -1.37025 -1.63136 -2.14842 -1.60456 -0.0806955 -3.80068  2.54741  1.73518 0.944895  1.92661  2.11864  2.10737  2.13606  1.28419 -1.29471 0.267515 0.982936  2.48115  1.46216  1.15139 -1.80802  1.37663 -1.01738 0.440458 -4.66903 -2.65307 -5.01052  4.33412 0.00763496 -5.01192 0.437893
 75:     2121.7708:  5.00000 -0.606107  1.60170  1.80166  1.48520  2.32413  2.25139  2.27092  2.88756  2.44187 -0.745948 0.111766 -0.940351 -0.634838 -0.619624 -1.94084 -1.97811 -2.16107 -1.07656 -0.651673 -1.38330 -1.63794 -2.15131 -1.58383 -0.0129846 -3.82216  2.53873  1.72607 0.937060  1.91819  2.11081  2.09933  2.13021  1.27735 -1.29689 0.257317 0.980620  2.47062  1.46299  1.12630 -1.83135  1.33704 -1.02177 0.441642 -4.67571 -2.65606 -5.01334  4.26052 0.0179934 -5.02100 0.437952
 76:     2121.7453:  5.00000 0.305393  1.60191  1.79861  1.48482  2.32351  2.25050  2.27014  2.88741  2.44079 -0.746557 0.114426 -0.940444 -0.637436 -0.621747 -1.94590 -1.98323 -2.16663 -1.07366 -0.647616 -1.38909 -1.64883 -2.15694 -1.53533 0.107059 -3.86524  2.55493  1.74118 0.957444  1.93544  2.13036  2.11913  2.15288  1.29770 -1.26926 0.275245  1.00861  2.49807  1.48698  1.13243 -1.83757  1.32952 -0.996990 0.471008 -4.64571 -2.62991 -4.97840  4.12005 0.0331752 -5.04180 0.438019
 77:     2121.7243:  5.00000  1.21937  1.60220  1.79771  1.48347  2.32388  2.24932  2.27129  2.88653  2.44133 -0.750368 0.114558 -0.942772 -0.634060 -0.622189 -1.94940 -1.98693 -2.17079 -1.07346 -0.653974 -1.39800 -1.64766 -2.16110 -1.49902 0.193400 -3.89202  2.58770  1.77335 0.992446  1.96694  2.16224  2.15150  2.18620  1.33041 -1.23246 0.306105  1.04480  2.52478  1.52617  1.17199 -1.82696  1.37174 -0.960060 0.509548 -4.61267 -2.59330 -4.94812  4.01547 0.0345129 -5.06581 0.438051
 78:     2121.6858:  5.00000  3.25132  1.60077  1.79782  1.48227  2.32369  2.25144  2.27911  2.88513  2.44175 -0.759016 0.115533 -0.944125 -0.618625 -0.620897 -1.95600 -1.99373 -2.17832 -1.06990 -0.676971 -1.38359 -1.65250 -2.16857 -1.43637 0.326978 -3.92136  2.65255  1.83439  1.06044  2.02807  2.22749  2.21802  2.25310  1.39356 -1.16788 0.370022  1.11202  2.59754  1.59487  1.26939 -1.78755  1.49322 -0.890362 0.574786 -4.54072 -2.52974 -4.88050  3.85177 0.0286140 -5.12298 0.437977
 79:     2121.6505:  5.00000  4.81780  1.60084  1.80096  1.48101  2.32509  2.25238  2.28467  2.88327  2.44380 -0.766813 0.111685 -0.948958 -0.608897 -0.619075 -1.95860 -1.99682 -2.18192 -1.07428 -0.697831 -1.39232 -1.63458 -2.17205 -1.39107 0.388969 -3.93093  2.68319  1.86189  1.08580  2.05088  2.25072  2.24131  2.27358  1.41558 -1.14894 0.390173  1.12613  2.60046  1.60753  1.32695 -1.76218  1.58099 -0.868602 0.593366 -4.53289 -2.50916 -4.88304  3.73367 0.00747113 -5.18177 0.437960
 80:     2121.6076:  5.00000  5.00000  1.59894  1.80457  1.48241  2.32494  2.25571  2.28912  2.88309  2.44411 -0.768957 0.109730 -0.947210 -0.601674 -0.616904 -1.95585 -1.99399 -2.17866 -1.07445 -0.713016 -1.36356 -1.63114 -2.16873 -1.37651 0.328249 -3.92351  2.59162  1.76785 0.988436  1.95610  2.15792  2.14872  2.17772  1.31859 -1.25651 0.297164  1.02062  2.50501  1.50772  1.25623 -1.81597  1.53853 -0.972310 0.485291 -4.64108 -2.61793 -5.00336  3.72536 -0.0105639 -5.20834 0.437717
 81:     2121.5480:  5.00000  5.00000  1.59977  1.80807  1.48575  2.32521  2.25804  2.27744  2.88337  2.44133 -0.764826 0.106089 -0.946214 -0.606554 -0.616918 -1.94927 -1.98739 -2.17118 -1.08215 -0.715776 -1.35651 -1.61028 -2.16110 -1.29469 0.175437 -3.98783  2.40902  1.58259 0.794225  1.76798  1.96979  1.95999  1.98229  1.12713 -1.46403 0.107966 0.808653  2.29648  1.27995  1.07631 -1.91053  1.38695 -1.18190 0.273627 -4.85946 -2.82260 -5.21979  3.62918 -0.0259044 -5.22817 0.437674
 82:     2121.5347:  4.96764  5.00000  1.59493  1.80718  1.48489  2.32459  2.25535  2.26884  2.88750  2.43975 -0.763627 0.102733 -0.947636 -0.611468 -0.619495 -1.94381 -1.98402 -2.16821 -1.08564 -0.716845 -1.36031 -1.60458 -2.15692 -1.26121 0.109305 -4.02248  2.31949  1.49561 0.705531  1.68006  1.88155  1.87056  1.89315  1.03862 -1.55962 0.0196825 0.712203  2.20121  1.17938 0.993870 -1.96436  1.31099 -1.28022 0.179157 -4.96076 -2.91762 -5.32210  3.58659 -0.0352005 -5.23209 0.436440
 83:     2121.5260:  4.99473  5.00000  1.60153  1.80637  1.48673  2.32336  2.25568  2.26797  2.88830  2.44038 -0.759195 0.107314 -0.944429 -0.612941 -0.617253 -1.94561 -1.98277 -2.16610 -1.08461 -0.704753 -1.35122 -1.60654 -2.15438 -1.21464 0.0178223 -4.06442  2.27198  1.44518 0.651311  1.63177  1.83425  1.82321  1.84656 0.991615 -1.60603 -0.0287207 0.667275  2.16245  1.14238 0.932913 -1.98577  1.25151 -1.32453 0.132591 -5.00729 -2.97045 -5.36635  3.52682 -0.0217336 -5.24376 0.437132
 84:     2121.5141:  4.92180  5.00000  1.59829  1.79833  1.48445  2.32262  2.25017  2.27039  2.89125  2.44057 -0.750787 0.115405 -0.944243 -0.620154 -0.619143 -1.94281 -1.97635 -2.13596 -1.06927 -0.670908 -1.37208 -1.64086 -2.18981 -1.22974 -0.0872111 -4.09424  2.26309  1.44063 0.654108  1.63407  1.84161  1.82974  1.86013  1.00385 -1.58444 -0.0246094 0.693028  2.21402  1.20459 0.849353 -2.02569  1.15631 -1.31004 0.162317 -4.94038 -2.92146 -5.29692  3.56815 0.00632147 -5.22904 0.436888
 85:     2121.5005:  4.89758  5.00000  1.59432  1.80170  1.48248  2.32399  2.25151  2.27229  2.88259  2.43872 -0.753702 0.107978 -0.947336 -0.622162 -0.621246 -1.93913 -1.97573 -2.14075 -1.07469 -0.677520 -1.37919 -1.64218 -2.18143 -1.20026 -0.0615201 -4.11035  2.22117  1.40117 0.611024  1.59083  1.79597  1.78542  1.80889 0.955948 -1.63331 -0.0729779 0.642435  2.15473  1.13967 0.799583 -2.08824  1.10059 -1.36082 0.114444 -5.00157 -2.97125 -5.36900  3.50289 -0.0109348 -5.24257 0.437793
 86:     2121.4892:  4.91150  5.00000  1.59872  1.80434  1.48098  2.32612  2.24874  2.27064  2.88849  2.44395 -0.757339 0.103928 -0.947593 -0.619730 -0.619954 -1.94269 -1.98075 -2.15941 -1.07806 -0.676425 -1.37845 -1.65339 -2.16452 -1.18329 0.0665107 -4.10152  2.27522  1.45293 0.658006  1.63854  1.83736  1.82546  1.85359 0.999133 -1.58382 -0.0357757 0.690983  2.18068  1.16909 0.827893 -2.12763  1.10424 -1.30792 0.162661 -4.97178 -2.93277 -5.35861  3.39761 -0.00842293 -5.26266 0.437032
 87:     2121.4750:  4.85843  5.00000  1.59582  1.80375  1.48267  2.32482  2.25138  2.26983  2.88473  2.44048 -0.758030 0.103228 -0.946801 -0.622334 -0.623027 -1.94212 -1.98173 -2.16330 -1.07808 -0.680876 -1.38632 -1.63400 -2.15994 -1.13059 0.0253804 -4.15183  2.23243  1.41049 0.617797  1.59788  1.79685  1.78637  1.81116 0.957773 -1.62744 -0.0745443 0.649661  2.13595  1.12785 0.777837 -2.17475  1.04016 -1.35134 0.118966 -5.01663 -2.97832 -5.40610  3.28921 -0.0128288 -5.29167 0.437335
 88:     2121.4380:  4.66027  5.00000  1.59070  1.80300  1.48457  2.32286  2.25382  2.26727  2.87779  2.43461 -0.760677 0.101134 -0.947543 -0.628678 -0.628928 -1.94030 -1.98247 -2.16757 -1.07930 -0.689884 -1.38615 -1.62678 -2.15320 -0.964464 -0.0554076 -4.31986  2.14957  1.32958 0.537161  1.51744  1.71894  1.70995  1.72844 0.877719 -1.70848 -0.155138 0.570783  2.05395  1.04683 0.674003 -2.29570 0.886063 -1.43486 0.0379624 -5.09818 -3.05856 -5.51108  2.86707 -0.0223568 -5.41467 0.437833
 89:     2121.3921:  4.40544  5.00000  1.58602  1.80270  1.48797  2.32020  2.25809  2.26662  2.87143  2.42876 -0.763352 0.0999496 -0.946855 -0.633472 -0.634888 -1.93969 -1.98396 -2.17350 -1.07851 -0.700531 -1.39483 -1.60106 -2.14566 -0.779558 -0.0933282 -4.51251  2.07074  1.25094 0.459742  1.44041  1.64443  1.63800  1.65018 0.801150 -1.78640 -0.231064 0.498842  1.98042 0.976423 0.575118 -2.42654 0.727193 -1.51234 -0.0401144 -5.17232 -3.13545 -5.60606  2.32572 -0.0243674 -5.58577 0.438214
 90:     2121.3503:  4.12983  5.00000  1.58413  1.80353  1.49285  2.31825  2.26267  2.26682  2.86536  2.42370 -0.765639 0.100688 -0.945027 -0.636888 -0.639684 -1.93939 -1.98522 -2.18034 -1.07643 -0.711557 -1.39697 -1.57834 -2.13564 -0.630697 -0.113530 -4.69916  1.99807  1.17735 0.386868  1.36745  1.57556  1.57130  1.57683 0.730011 -1.85734 -0.302828 0.433544  1.90978 0.911886 0.482898 -2.55211 0.571037 -1.58264 -0.111748 -5.24331 -3.20870 -5.69566  1.77380 -0.0206577 -5.78475 0.438631
 91:     2121.2959:  3.84758  5.00000  1.58998  1.80449  1.50307  2.31569  2.27099  2.27127  2.86121  2.41982 -0.764087 0.112032 -0.936309 -0.632013 -0.640425 -1.94085 -1.98549 -2.19044 -1.06606 -0.720772 -1.39600 -1.53338 -2.11530 -0.602725 -0.109091 -4.81653  1.99549  1.16959 0.385242  1.36081  1.57843  1.57778  1.57895 0.730652 -1.85200 -0.297867 0.452092  1.92557 0.943380 0.487465 -2.60820 0.506335 -1.56963 -0.108224 -5.23477 -3.22209 -5.66999  1.33537 0.00548072 -6.02877 0.439429
 92:     2121.1304:  3.84277  5.00000  1.58835  1.79608  1.49212  2.31522  2.26300  2.27641  2.86802  2.42588 -0.757742 0.117598 -0.934952 -0.617441 -0.629572 -1.93216 -1.97505 -2.17600 -1.06241 -0.704751 -1.38549 -1.57129 -2.10981 -0.608259 -0.0629786 -4.74776  2.13368  1.31898 0.536262  1.49558  1.71098  1.71573  1.73082 0.874541 -1.69323 -0.151794 0.611865  2.07586  1.11095 0.727639 -2.41466 0.801286 -1.41513 0.0562214 -5.07443 -3.08521 -5.48427  1.35658 -0.0139633 -6.13843 0.438267
 93:     2121.0805:  3.81601  5.00000  1.59066  1.79540  1.47885  2.32029  2.25114  2.27366  2.88035  2.43626 -0.755299 0.111421 -0.944767 -0.608862 -0.617405 -1.92660 -1.96723 -2.15655 -1.07501 -0.687632 -1.37050 -1.65243 -2.12519 -0.521243 -0.0113023 -4.78806  2.19289  1.39093 0.591271  1.53813  1.74873  1.75773  1.78755 0.928318 -1.63336 -0.113937 0.658729  2.11213  1.12059 0.859159 -2.24175  1.01707 -1.37770 0.110792 -5.01569 -3.02920 -5.40917  1.05967 0.0264437 -6.35962 0.436635
 94:     2121.0662:  3.78710  5.00000  1.60969  1.81163  1.47843  2.33356  2.24428  2.26631  2.89409  2.45147 -0.752838 0.106148 -0.944286 -0.611316 -0.609768 -1.93494 -1.97177 -2.15303 -1.07471 -0.672599 -1.34448 -1.69252 -2.15135 -0.584923 -0.0304976 -4.79363  2.11878  1.29954 0.485010  1.43781  1.65042  1.65011  1.67602 0.827039 -1.74863 -0.237064 0.527341  1.98017 0.987796 0.755465 -2.28131 0.980414 -1.48632 -0.0130740 -5.14800 -3.11927 -5.54099  1.10221 -0.0386832 -6.35962 0.436837
 95:     2120.9972:  3.75390  5.00000  1.61037  1.81125  1.48414  2.33219  2.25004  2.27010  2.89014  2.44744 -0.751432 0.111076 -0.942428 -0.609943 -0.610869 -1.93814 -1.97438 -2.15527 -1.07247 -0.672374 -1.34957 -1.67548 -2.15521 -0.593469 -0.0395666 -4.77808  2.10288  1.27920 0.469357  1.42140  1.63872  1.63877  1.66007 0.811822 -1.76887 -0.245772 0.512635  1.97237 0.979256 0.721667 -2.30142 0.953134 -1.50157 -0.0320637 -5.16005 -3.13711 -5.52066  1.16055 0.00623264 -6.35962 0.438210
 96:     2120.9743:  3.73226  5.00000  1.60257  1.80732  1.48569  2.32728  2.25359  2.27404  2.88545  2.44258 -0.750968 0.112003 -0.939379 -0.611683 -0.615110 -1.93662 -1.97401 -2.15543 -1.06834 -0.676292 -1.36665 -1.63722 -2.15190 -0.547152 0.00360834 -4.80255  2.09881  1.27779 0.474433  1.42724  1.64368  1.64655  1.66700 0.815298 -1.76290 -0.231037 0.523727  1.99201  1.00421 0.705981 -2.32602 0.930617 -1.49503 -0.0216103 -5.14985 -3.13428 -5.51368  1.10064 0.00439481 -6.35962 0.437971
 97:     2120.9668:  3.78117  5.00000  1.60147  1.80463  1.48552  2.32405  2.25215  2.27314  2.88535  2.44167 -0.751314 0.112305 -0.938763 -0.613927 -0.616978 -1.93789 -1.97471 -2.15681 -1.06815 -0.677452 -1.37830 -1.61400 -2.14942 -0.555958 0.00328543 -4.81472  2.11670  1.29514 0.493744  1.44967  1.66533  1.66793  1.69140 0.836917 -1.73667 -0.205654 0.548647  2.01818  1.03068 0.706871 -2.29413 0.947851 -1.47087 0.00690150 -5.13443 -3.11714 -5.49949  1.11937 0.00364819 -6.35962 0.437262
 98:     2120.9593:  3.76404  5.00000  1.60005  1.80261  1.48503  2.32385  2.25055  2.27033  2.88677  2.44139 -0.751969 0.112311 -0.940827 -0.616053 -0.618266 -1.93826 -1.97560 -2.15665 -1.07131 -0.676320 -1.37415 -1.62816 -2.15152 -0.525082 -0.0210989 -4.85350  2.12483  1.30517 0.502877  1.45805  1.67529  1.67652  1.70315 0.847611 -1.72738 -0.196686 0.557532  2.02160  1.03409 0.687338 -2.28148 0.957228 -1.46309 0.0152590 -5.12636 -3.10755 -5.48558  1.11233 -0.00358019 -6.35962 0.436355
 99:     2120.9518:  3.75386  5.00000  1.60111  1.80425  1.48610  2.32497  2.25161  2.26933  2.88674  2.44125 -0.753202 0.111802 -0.941207 -0.617300 -0.619092 -1.94036 -1.97784 -2.15868 -1.07182 -0.677988 -1.36375 -1.64072 -2.15442 -0.513816 0.00112069 -4.89029  2.10716  1.28734 0.482489  1.43792  1.65648  1.65738  1.68389 0.828024 -1.74971 -0.219482 0.536191  1.99999  1.01152 0.642280 -2.31101 0.934504 -1.48438 -0.0104931 -5.14236 -3.12385 -5.50182  1.11114 -0.00399470 -6.35962 0.436531
100:     2120.9407:  3.74115  5.00000  1.60199  1.80561  1.48633  2.32527  2.25171  2.26914  2.88504  2.44054 -0.755619 0.110412 -0.943415 -0.620259 -0.620901 -1.94345 -1.98090 -2.16186 -1.07363 -0.679815 -1.36558 -1.64624 -2.15820 -0.476605 0.00353359 -4.98557  2.10308  1.28235 0.473942  1.43153  1.65103  1.65190  1.67769 0.821175 -1.75627 -0.229891 0.529713  1.99481  1.00564 0.600015 -2.33545 0.930625 -1.48951 -0.0169138 -5.14726 -3.12657 -5.51119  1.10315 -0.00116716 -6.35962 0.437094
101:     2120.9345:  3.73968  5.00000  1.60180  1.80515  1.48580  2.32395  2.25112  2.26810  2.88444  2.43997 -0.756485 0.109303 -0.944792 -0.620003 -0.621960 -1.94649 -1.98388 -2.16599 -1.07504 -0.681770 -1.37551 -1.63522 -2.16013 -0.436935 0.00285880 -5.09324  2.10408  1.28084 0.472657  1.43129  1.65083  1.65214  1.67584 0.820505 -1.75806 -0.229625 0.527808  1.99787  1.00835 0.594746 -2.34561 0.945890 -1.48913 -0.0180448 -5.15209 -3.13051 -5.51509  1.11099 -4.88680e-05 -6.35962 0.437128
102:     2120.9340:  3.73979  5.00000  1.60095  1.80418  1.48446  2.32315  2.25017  2.26837  2.88362  2.43960 -0.756534 0.108520 -0.945263 -0.619396 -0.621992 -1.94548 -1.98299 -2.16546 -1.07576 -0.681892 -1.37612 -1.63574 -2.15816 -0.437403 -0.00422173 -5.10698  2.11121  1.28801 0.479840  1.43892  1.65809  1.65947  1.68216 0.828447 -1.75047 -0.222519 0.534099  2.00542  1.01509 0.628387 -2.34220 0.952898 -1.48205 -0.00979220 -5.14765 -3.12742 -5.51439  1.10822 0.000344594 -6.35962 0.437129
103:     2120.9336:  3.74081  5.00000  1.60046  1.80354  1.48368  2.32304  2.24989  2.26800  2.88382  2.43971 -0.756165 0.108364 -0.945175 -0.618485 -0.621576 -1.94434 -1.98201 -2.16465 -1.07579 -0.681351 -1.37600 -1.63576 -2.15639 -0.434151 0.00140035 -5.10999  2.11352  1.29105 0.483007  1.44156  1.66018  1.66184  1.68444 0.831260 -1.74887 -0.220032 0.536122  2.00765  1.01652 0.651787 -2.33988 0.953815 -1.47987 -0.00784537 -5.14579 -3.12706 -5.51138  1.10775 0.000264777 -6.35962 0.437067
104:     2120.9336:  3.74028  5.00000  1.60077  1.80387  1.48401  2.32327  2.25017  2.26813  2.88412  2.43993 -0.756065 0.108579 -0.944843 -0.618442 -0.621481 -1.94426 -1.98186 -2.16460 -1.07523 -0.681068 -1.37611 -1.63487 -2.15601 -0.434802 -8.50980e-05 -5.10614  2.11275  1.29021 0.482197  1.44091  1.65943  1.66113  1.68415 0.830310 -1.74997 -0.220926 0.535819  2.00816  1.01765 0.655419 -2.34089 0.948446 -1.48054 -0.00933671 -5.14538 -3.12776 -5.50987  1.10895 -6.95478e-06 -6.35962 0.437072
105:     2120.9336:  3.74033  5.00000  1.60078  1.80382  1.48408  2.32320  2.25004  2.26808  2.88403  2.43984 -0.756186 0.108611 -0.945009 -0.618640 -0.621615 -1.94449 -1.98208 -2.16485 -1.07541 -0.681237 -1.37594 -1.63546 -2.15627 -0.435328 2.18983e-05 -5.10572  2.11233  1.28980 0.481744  1.44059  1.65915  1.66076  1.68383 0.830047 -1.74984 -0.221168 0.535553  2.00740  1.01684 0.656634 -2.34209 0.944867 -1.48092 -0.00899736 -5.14593 -3.12815 -5.51026  1.10892 -4.14018e-05 -6.35962 0.437071
106:     2120.9336:  3.74031  5.00000  1.60078  1.80386  1.48408  2.32322  2.25006  2.26809  2.88403  2.43984 -0.756212 0.108578 -0.945044 -0.618724 -0.621646 -1.94457 -1.98217 -2.16493 -1.07548 -0.681241 -1.37587 -1.63580 -2.15638 -0.434990 -7.84302e-05 -5.10648  2.11210  1.28955 0.481456  1.44028  1.65891  1.66049  1.68356 0.829775 -1.75010 -0.221484 0.535326  2.00700  1.01653 0.656971 -2.34255 0.943328 -1.48118 -0.00941544 -5.14611 -3.12823 -5.51041  1.10870 2.38422e-06 -6.35962 0.437071
107:     2120.9336:  3.74033  5.00000  1.60078  1.80387  1.48409  2.32322  2.25007  2.26809  2.88404  2.43985 -0.756209 0.108572 -0.945033 -0.618733 -0.621652 -1.94459 -1.98219 -2.16495 -1.07546 -0.681230 -1.37603 -1.63556 -2.15642 -0.435066 2.22502e-05 -5.10642  2.11197  1.28940 0.481313  1.44014  1.65877  1.66037  1.68343 0.829616 -1.75029 -0.221611 0.535181  2.00696  1.01644 0.656818 -2.34267 0.943145 -1.48131 -0.00953321 -5.14626 -3.12832 -5.51046  1.10880 1.45576e-06 -6.35962 0.437069
  0:     2120.9336:  3.74033  5.00000  1.60078  1.80387  1.48409  2.32322  2.25007  2.26809  2.88404  2.43985 -0.756209 0.108572 -0.945033 -0.618733 -0.621652 -1.94459 -1.98219 -2.16495 -1.07546 -0.681230 -1.37603 -1.63556 -2.15642 -0.435066 2.22502e-05 -5.10642  2.11197  1.28940 0.481313  1.44014  1.65877  1.66037  1.68343 0.829616 -1.75029 -0.221611 0.535181  2.00696  1.01644 0.656818 -2.34267 0.943145 -1.48131 -0.00953321 -5.14626 -3.12832 -5.51046  1.10880 1.45576e-06 -6.35962 0.437069
  1:     2120.9336:  3.74033  5.00000  1.60078  1.80387  1.48409  2.32322  2.25007  2.26809  2.88404  2.43985 -0.756209 0.108572 -0.945033 -0.618733 -0.621652 -1.94459 -1.98219 -2.16495 -1.07546 -0.681230 -1.37603 -1.63556 -2.15642 -0.435066 2.22260e-05 -5.10642  2.11197  1.28940 0.481313  1.44014  1.65877  1.66037  1.68343 0.829616 -1.75029 -0.221611 0.535181  2.00696  1.01644 0.656818 -2.34267 0.943145 -1.48131 -0.00953320 -5.14626 -3.12832 -5.51046  1.10880 1.44275e-06 -6.35962 0.437069
  2:     2120.9336:  3.74033  5.00000  1.60078  1.80387  1.48409  2.32322  2.25007  2.26809  2.88404  2.43985 -0.756209 0.108572 -0.945033 -0.618733 -0.621652 -1.94459 -1.98219 -2.16495 -1.07546 -0.681230 -1.37603 -1.63556 -2.15642 -0.435066 2.22260e-05 -5.10642  2.11197  1.28940 0.481313  1.44014  1.65877  1.66037  1.68343 0.829616 -1.75029 -0.221611 0.535181  2.00696  1.01644 0.656818 -2.34267 0.943145 -1.48131 -0.00953320 -5.14626 -3.12832 -5.51046  1.10880 1.44275e-06 -6.35962 0.437069
  3:     2120.9336:  3.74033  5.00000  1.60078  1.80387  1.48409  2.32322  2.25007  2.26809  2.88404  2.43985 -0.756209 0.108572 -0.945033 -0.618733 -0.621652 -1.94459 -1.98219 -2.16495 -1.07546 -0.681230 -1.37603 -1.63556 -2.15642 -0.435066 2.22260e-05 -5.10642  2.11197  1.28940 0.481313  1.44014  1.65877  1.66037  1.68343 0.829616 -1.75029 -0.221611 0.535181  2.00696  1.01644 0.656818 -2.34267 0.943145 -1.48131 -0.00953320 -5.14626 -3.12832 -5.51046  1.10880 1.44275e-06 -6.35962 0.437069

Check bounds for the following parameters:
        Param starting_value     Lower       MLE     Upper final_gradient
2  ln_H_input      0.0000000 -5.000000  5.000000  5.000000    -0.06354718
50  logkappa2     -0.1053605 -6.359621 -6.359621 -2.718847     0.42225521

The following parameters appear to be approaching zero:
          Param starting_value Lower          MLE Upper final_gradient
25 L_epsilon1_z              1  -Inf 2.222603e-05   Inf   0.0002381819
49 L_epsilon2_z              1  -Inf 1.442753e-06   Inf   0.0001268970
Please turn off factor-model variance parameters `L_` that are approaching zero and re-run the model


Error: Please change model structure to avoid problems with parameter estimates and then re-try; see details in `?check_fit`
In addition: Warning messages:
1: In sparseMatrix(i = index.i, j = index.j, x = Aij, dims = c(mesh$n,  :
  'giveCsparse' has been deprecated; setting 'repr = "T"' for you
2: In sparseMatrix(i = index.i, j = index.j, x = Aij, dims = c(mesh$n,  :
  'giveCsparse' has been deprecated; setting 'repr = "T"' for you
3: In sparseMatrix(i = index.i, j = index.j, x = Aij, dims = c(mesh$n,  :
  'giveCsparse' has been deprecated; setting 'repr = "T"' for you

```



Crashes with error: 
Error: Please change model structure to avoid problems with parameter estimates and then re-try; see details in `?check_fit`

There is no file output. May need to run as script to work properly